### 2013-09-24 NeurounitFrontiers/Paper.tex
Initial commit

\documentclass[11pt,letterpaper]{article}
\pagestyle{plain}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage[utf8]{inputenc}
\usepackage{times}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage{listings}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage{setspace}
\usepackage{python_syntax}
\usepackage[sort&compress]{natbib}
\usepackage{bibentry}
\usepackage{todonotes}
\usepackage{url}
\usepackage[compact]{titlesec}
\titleformat{\subsection}[runin]
{\normalfont\large\bfseries}{\thesubsection}{1em}{}
\titleformat{\subsubsection}[runin]
{\normalfont\large\bfseries}{\thesubsubsection}{1em}{}
\usepackage{enumitem}
\usepackage[
top    = 1in,
bottom = 1in,
left   = 1in,
right  = 1in]{geometry}
\usepackage{caption}
\captionsetup{belowskip=0pt,aboveskip=0pt}
\linespread{0.92} % NSF allows up to 6 lines per inch.  
\def\UrlFont{\em} % Italicize all URLs.  
\frenchspacing
\setlist{nolistsep} % or \setlist{noitemsep} to leave space around whole list
\lstset{
	basicstyle=\small\ttfamily,
	breaklines=true,
	language=Python,
	}
\let\verbx\lstinline
\newcommand{\bfhead}[1]{\noindent \textbf{#1:}}

\begin{document}

\section{Abstract}
Rigorously validating a scientific model’s explanatory power requires comparing its predictions against empirical data -- both data available during model development and data gathered after publication. 
However, model validation remains an informal and incomplete process, especially in neuroscience.   
This makes it difficult to evaluate a model's strengths and weaknesses, or to adequately compare two models.

Here we describe a model-testing library that draws inspiration from ``unit tests'', a common form of software testing that validates a single component of a computer program against a single correctness criterion. 
This is realized by using the \textit{SciUnit} Python framework for analogous ``model validation tests'' -- 
executable functions validating models against an empirical observation by producing a score indicating model/data agreement. 
We applied this framework to neuroscience to produce \textit{NeuroUnit}, a library for test construction in neuroscience, and a repository of useful tests.

% Section 1.
\section{Introduction}
Neuroscientists construct quantitative models to explain observations about neurons, circuits, and brains in a coherent and rigorous manner. 
These models are characterized by their \textit{scope}: the set of observable quantities that the model can generate predictions about, and by their \textit{validity}, the extent to which these predictions agree with empirical observations of those quantities. 
As the quantity of models and empirical data in neuroscience proliferates, it is increasingly challenging to efficiently discover models whose scope is of interest and then assessing their validity against this mountain of data.

Neuroscience models are traditionally described in publications. 
Although authors may refer to some relevant experimental data and alternative models, these comparisons are incomplete and tend to serve the goals of authors rather than readers. 
However, making exhaustive comparisons to exisiting models and data would make such publications encyclopedic and obscure their main points. 
Thus, a strength of publication is its focused description of how a model works and its conceptual advances. 
A weakness, however, is that evaluating the scope and validity of a model is intractable using a publication alone. 
This problem is exacerbated post-pubication as new data is rarely compared against existing models, and the original publication -- a resource of first resort for new scientists and onlookers -- is cited ``as-is'' in perpetuity. 	
The validation of neuroscience models must be formalized to supplement the publication system and provide a straightforward way to determine how well models do what they claim to do.

There are related efforts in the machine learning community to develop models and validate them against standardized, publicly-available datasets according to well-specified metrics. 
Kaggle\cite{kaggle_url} drives model development by organizing competitions where training data is made public and competitors submit competing algorithms, compared automatically by cross-validated accuracy on an unrevealed test set. 
The success of Kaggle shows that open competitions are effective\cite{carpenter_may_2011}, and that a ``modeling as a competition'' paradigm attracts data scientists across traditional discipline boundaries.  
On the other hand, Kaggle focuses solely on a few general cases in machine learning: classification, regression, and clustering, where validation criteria are straightforward.

Discipline-specific competitions having a similar structure but with more sophisticated validation criteria within neuroscience have also resulted in important advances. 
For example, the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} addressed the complexity-accuracy tradeoff among reduced models of excitable membranes; 
the ``Hopfield'' challenge\cite{hopfield_what_2000} asked for neuronal network form, given function; 
the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity\cite{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction\cite{diadem_url}; 
examples from other subfields of biology abound\cite{dream_url}.

Recognizing that neuroscience contains a wide variety of models that aim to explain phenomena at multiple levels, we leveraged a discipline-agnostic Python framework called \textit{SciUnit}\cite{sciunit_url} to create tools for testing neuroscience models and associated tests.  The result is \textit{NeuroUnit}, which extends \textit{SciUnit} into neuroscience by supporting the testing of models described using \textit{NeuroML}, the construction of test logic using \textit{NeuroTools} \cite{neurotools_url}, and employing a test ``answer key" using electrophysiology data from the \textit{NeuroElectro Project} \cite{neuroelectro_url}.  In addition to this open testing framework we also provide a library of tests for models of spiking single neurons.

% Section 2.
\section{Fundamentals of Testing}
\vspace{-12px}
\begin{wrapfigure}{r}{0.6\textwidth}
\vspace{-38px}
\includegraphics[scale=0.75]{sciunit_overview.pdf}
\caption{Proposal overview. 
\small{i) The \textit{SciUnit} framework can generate discipline-specific libraries for tests generation and model interfacing.  
\textit{NeuronUnit} is proposed and described here.  Experimental data guides test development; model generation informs and is informed by these \textit{SciUnit} libraries.  
Each \text{SciUnit} test suite repository on GitHub is indexed by the \textit{SciDash} web application.  
Test suites for OSB and QSNMC (described in the text) are being built. 
\textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
\vspace{-10px}
\label{fig:sciunit_overview}
\end{wrapfigure}
\leavevmode
\vspace{-0px}

The \textit{SciUnit} framework is organized around simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.

\begin{figure}
\small
\begin{python}
class SpikeCountTest(sciunit.Test):
  """Tests models that generates spike counts from currents. Computes p-values based on a chi-squared test statistic, and pools them using Fisher's method.

  parameters:
    inputs: list of numpy arrays containing input currents (nA)
    means, stds: list of means and standard deviations of the 
      spike counts observed in response to the inputs
  """
  def __init__(self, inputs, means, stds):
    self.inputs, self.means, self.stds = inputs, means, stds

  required_capabilities = [SpikeCountFromCurrent]

  def run_test(self, model):
    inputs, means, stds = self.inputs, self.means, self.stds
    n = len(inputs)
    counts = numpy.empty((n,))
    for i in xrange(n):
      counts[i] = model.spike_count_from_current(inputs[i])
    chisquared = sum((counts-means)**2 / means) # An array of chi-squared values.  
    p = scipy.stats.chi2.cdf(chisquared,n-1) # An array of p-values.  
    pooled_p = sciunit.utils.fisherp(p_array) # A pooled p-value.  
    return sciunit.PValue(pooled_p, related_data={
      "inputs": input_current,
      "obs_means": means,
      "obs_stds": stds
    })
\end{python}
\vspace{-5px}
\caption{A single neuron spike count test family implemented in \textit{SciUnit}}
\label{fig:rate_test}
\vspace{-15px}
\end{figure}

\subsection{Example: Neural Membrane Potential Dynamics} To clarify the basic ideas, we begin by describing a test suite related to single-neuron neurophysiology. 
The tests in this suite are designed for experiments where stimuli are delivered to neurons of a particular type, as somatically injected current (in pA), while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.  
A model claiming to capture this cell type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.

One simple validation test would ask candidate models to predict the number of action potentials generated in response to a series of stimuli, and compare these \emph{spike count} predictions to the distribution observed in repeated experimental trials with the same stimuli. 
The test creator is responsible for specifying how to measure the goodness-of-fit; 
for example, a p-value derived from a chi-squared statistic could be calculated for each prediction and then these p-values could be combined using Fisher's method\cite{fisher_statistical_1925}.

Alongside this \emph{spike count test}, a number of other tests capturing different features of the data could be specified to produce a more comprehensive suite. 
For data of this sort, the QSNMC defined 17 other validation criteria in addition to one based on the overall spike count, capturing features like spike latencies (SL), mean subthreshold voltage (SV), interspike intervals (ISI) and interspike minima (ISM) that can be extracted from the data\cite{jolivet_quantitative_2008}. 
They then defined a combined metric favoring models that broadly succeeded at meeting these criteria, to produce an overall ranking. 
Such combined criteria are simply validation tests that invoke other tests to produce a result.

Importantly, the validation criteria in each case are made explicit by the specification of a test suite, so modelers need not guess which criteria are being used to validate or invalidate their model. 
Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and scientists who wish to promote different criteria need only derive alternative test suites. 
In many cases, models require no modifications to take the new tests because the same type of model output is being requested.

Fig. \ref{fig:rate_test} shows how a scientist would implement the spike count test described in the preceding section using \textit{SciUnit}. 
A \textit{SciUnit} validation test is an {instance} of a Python class implementing the \verbx{sciunit.Test} interface. 
Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor (in Python, the constructor is always named \verbx{__init__}; the parameters' meaning is documented on lines 5-8). 
For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
For example, given observations from hippocampal CA1 cells (not shown), we can instantiate a test as follows:
\begin{python}
  CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
\end{python}
We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test. 
As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their field so that test generation for a particular system of interest will often consist simply of instantiating a previously-developed family with particular experimental parameters and data. 
For single-neuron tests like the \verbx{SpikeCountTest}, we have developed a library to facilitate development (Sec. \ref{sec:neuronunit}).

Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{run_test} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
To specify the interface between the test and the model (that is, to constrain the test's scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig. \ref{fig:rate_test}. 
Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java \cite{java_interfaces_url}. 
In Python, they are written as classes with unimplemented members. 
The capability required by the test in Fig. \ref{fig:rate_test} (used on line 19) is shown in Fig. \ref{fig:capability}. 
In \textit{SciUnit}, classes defining capabilities be tagged by inheriting from \verbx{sciunit.Capability}, and discovered automatically (Figs. \ref{fig:capability},\ref{fig:training}).

\begin{figure}
\begin{python}
class SpikeCountFromCurrent(sciunit.Capability):
  def spike_count_from_current(self, input): 
    """Takes a numpy array containing current stimulus (in nA) and
    produces an integer spike count. Can be called multiple times."""
    raise NotImplementedError("Model does not implement capability.")
\end{python}
\caption{An example capability specifying a single required method (used by the test in Figure \ref{fig:rate_test}).}
\label{fig:capability}
\vspace{-10px}
\end{figure}

\begin{figure}
\begin{python}
class TrainSpikeCountFromCurrent(sciunit.Capability):
  def train_with_currents(self, currents, counts):
    """Takes a list of numpy arrays containing current stimulus (in nA) and
    observed spike counts. Model parameters should be adjusted based on this
    training data."""
    raise NotImplementedError("Model does not implement capability.")
\end{python}
\caption{Another capability specifying a training protocol (not used by the test in Figure \ref{fig:rate_test}).}
\label{fig:training}
\vspace{-15px}
\end{figure}

Capabilities are \emph{implemented} by models. 
A simple \emph{family} of models implementing this capability is shown in Fig. \ref{fig:simple_model}. 
Models in this family produce a spike count by applying a linear transformation to the mean of the provided input current. 
The family is parameterized by a scale factor and offset, both scalars. 
To create a \emph{particular} model, the modeler may choose particular parameter values, just as with test families:
\begin{python}
CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
\end{python}
Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
An alternative test design to the one in Fig. \ref{fig:rate_test} would add a second required capability (Fig. \ref{fig:training}) and a corresponding training phase to the \verb|run_test| method. 
This design would be relevant only for those models for which parameters can be adjusted without human involvement. 
Whether to build a training phase into the test protocol is a choice left to each modeler. 
Although Fig. \ref{fig:rate_test} does not include a training phase, if training data is available then models that nevertheless implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
\begin{python}
CA1_linear_model_fit = LinearModel()
CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
\end{python}
\begin{figure}
\begin{python}
class LinearModel(sciunit.Model, SpikeCountFromCurrent, 
    TrainSpikeCountFromCurrent):
  def __init__(self, scale=None, offset=None): 
    self.scale, self.offset = scale, offset

  def spike_count_from_current(self, input):
    return int(self.scale*numpy.mean(input) + self.offset)

  def train_with_currents(self, currents, counts):
    means = [numpy.mean(c) for c in currents]
    [self.offset, self.scale] = numpy.polyfit(means, counts, deg=1)    
\end{python}
\caption{A simple model that returns a spike count by scaling the mean of the input by a fixed parameter.}
\label{fig:simple_model}
\vspace{-15px}
\end{figure}

In the test in Fig. \ref{fig:rate_test}, the \verbx{run_test} method simply calls the \verbx{spike_count_from_current} capability method to produce spike count predictions for each input current on line 18. 
There are many possibly statistical choices for deriving a test score.  
In the figure, the resulting spike count is compared to the empirical mean to produce a chi-squared statistic, and ultimately a p-value. 
Alternatively, the array of standard deviations (line 10) could be used to derive a Z-score.  
In addition to the score itself, the returned score object also contains metadata of use to those wishing to examine the result in detail. 
In this test we saved the inputs and observed means and standard deviations alongside the score by using the \verbx{related_data} parameter. 
We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.

Finally, a test is executed against a model instance, using the \verbx{sciunit.judge} function:
\begin{python}
score = sciunit.judge(CA1_sc_test, CA1_linear_model_heuristic)
\end{python}

The \verbx{sciunit.judge} function operates in three phases: 
\textbf{(1) Capability Checking}: The model is verified as capable of taking the test by checking each capability in the test's \verbx{required_capabilities} attribute; 
\textbf{(2) Test Execution}: The test's \verbx{run_test} method is called to execute the model and the output is cached. 
\textbf{(3) Output Validation}: \verbx{run_test} returns an instance of a \verbx{sciunit.Score} subclass containing a goodness-of-fit metric between the model output and the data used to parameterize the test.  
Any errors that occur during this process are reported by raising an appropriate exception.

\subsection{\textit{SciUnit} Test Suites}
A test suite is a collection of tests designed to validate a model against several mutually coherent requirements, i.e. various summaries of the data.  
The following is a test suite that could be used for a simplified version of the QSNMC:  
\begin{python}
CA1_suite = sciunit.TestSuite([CA1_sc_test, CA1_sl_test, CA1_sv_test, CA1_isi_test, CA1_ism_test])
\end{python}
When a test suite is executed against a model, it produces summary data that can be shown on the console or visualized by other tools, such as the web application described in Sec. \ref{sec:scidash}.

\subsection{\textit{SciUnit} Design Considerations}
Each community can collaboratively specify capabilities capturing the high-level semantics of their preferred modeling formalisms. 
Existing modeling standards (e.g. NeuroML\cite{neuroml_url,gleeson_neuroml:_2010}) can be leveraged to simplify this process. \textbf{\textit{SciUnit}, written in Python, was designed to make test construction (from data) and test-driven model execution exceptionally easy and flexible.} 
All figures shown here containing code blocks make use of this framework.

\subsection{\textit{SciDash}: A community web application}\label{sec:scidash}
This framework is most effective when the current state of a research area is represented by a collection of tests and models. 
This requires coordination among research groups, so community-oriented cyberinfrastructure to support test suite creation and summarization, building upon \textit{SciUnit}, is essential.
We developed a service called \textit{SciDash}, utilizing existing infrastructure for coordinated development of software repositories, and focusing on GitHub\cite{github_url}\cite{ram_git_2013}. 
A suite of related tests will be contained in a GitHub repository with a stereotyped high-level structure allowing the \textit{SciDash} web application to discover, index and summarize it continuously (Fig. \ref{fig:scidash_repo}).

\begin{wrapfigure}[18]{r}{0.45\textwidth}
\center
\vspace{-10px}
\includegraphics[scale=0.72]{scidash_github.png}
\caption{A \textit{SciDash} repository on GitHub}
\label{fig:scidash_repo}
\end{wrapfigure}
\vspace{-10px}
\leavevmode

Test results can be visualized as a ``record matrix'' composed of large numbers of model/test combinations (Fig. \ref{fig:scidash_matrix}).  
Each row in this matrix contains results for all tests taken by one model and serve as clear evidence of that model's scope and validity.  
Models, tests, and records will be stored on GitHub, pointed to by hyperlinks in the record matrix. 
\textit{SciDash} serves as a public record of competition among models, facilitating and encouraging data-driven development among modelers.
\textbf{Thus, the second product of this proposal is a web application called \textit{SciDash}, whose back-end can index test suite repositories collaboratively developed on GitHub, and whose front-end offers users a simple environment for discovery and evaluation of models, tests, and records.}

\subsection{\textit{NeuronUnit}: A Suite of Tests for Neurophysiology}\label{sec:neuronunit}
By using machine-readable models from Open Source Brain (OSB), and machine-readable data from resources like The NeuroElectro Project\cite{neuroelectro_url}, we have produced a suite of data-driven validation tests in \textit{NeuronUnit}, as well as tools for capability implementation, and model interfaces for a representative set of canonical neurophysiology models, all publicly available.

% Section 3.
\section{Results}

\subsection{\textit{SciDash} Activities}\label{sec:scidash_activities}
The \textit{SciDash} web application points to test suite repositories and aggregates test results for scientific communities \cite{scidash_url}. 
It is populated with models and tests from the educational illustration in Table \ref{table:record_matrix} (section~\ref{sec:education}). 
\textit{SciDash} exists in three layers.
The \textbf{first layer} is completely under the control of individual developer communities, and consists of git repositories. 
Git is the most popular implementation of ``version control'' among developers today\cite{ram_git_2013}, and is increasingly used for open science projects (e.g. OSB\cite{osb_url}). 
The GitHub website\cite{github_url} is the most popular location for collaborative code development using git. 
\textit{SciDash} identifies all similarly structured repositories (by tracking the lineage of the repository above using the GitHub API).
This list of repositories will be indexed by \textit{SciDash} to form the \textbf{second layer}, an overview of the state of all \textit{SciDash} repositories on GitHub.  
This index is searchable and filterable on the \textit{SciDash} website to identify repositories of interest to a particular research community.  
The \textbf{third layer} is a ``dashboard'' view of the state of a field, visible through a matrix of records for model/test combinations in a GitHub repository (Fig. \ref{fig:scidash_repo}). 
Each record links to test records (stored in the repository), displaying line-by-line the executed code and intermediate output statements, as well as the underlying models and tests.

\begin{figure}%[18]{r}{1\textwidth}
\includegraphics[scale=0.65]{table.png}
\caption{A \textit{SciDash} record matrix}
\label{fig:scidash_matrix}
\vspace{-15px}
\end{figure}
\vspace{-10px}
\leavevmode

\subsection{\textit{NeuronUnit} Activities}
\label{sec:neuronunit_acitivities}
Here we describe standard neuroinformatics tools we have adopted to develop \textit{NeuronUnit}\cite{neurounit_url}.

\subsubsection{Models from NeuroML}\label{sec:neuroml_models}
NeuroML is a standardized model description language for neuroscience \cite{gleeson_neuroml:_2010}. 
It permits many neurophysiological/neuroanatomical models to be described in a simulator-independent fashion, and executed across many popular simulators due to inter-conversion capabilities of the NeuroML API. 
Because NeuroML is an XML specification, model descriptions can be validated for correctness and queried for model properties and components, exposing potential capabilities. 
It is ideal for model sharing, curation, and for answering both \textit{what} and \textit{how} programatically.

NeuroConstruct\cite{neuroconstruct_url,gleeson_neuroconstruct:_2007} is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
\textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, instantiated with the path to a NeuroML model.  
Because NeuroML can describe such a wide range of models, \verbx{NeuroConstructModel} makes few assumptions about them: that each one is \verbx{TimeIntegrable}, and \verbx{HasMembranePotential}.  
It is subclassed to test \textit{specific} NeuroML models (Fig. \ref{fig:ca1_model}).

The Open Source Brain project (OSB,\cite{osb_url}) curates many models described in NeuroML. 
OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators\cite{neuron_url,genesis_url,nest_url,moose_url}. 
Concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files) is reported for each model. 
Thus, OSB is an excellent source of models that, in addition to being open source, are sufficiently described to enable validation. 
The hippocampal CA1 pyramidal cell is commonly modeled, and we implement one such model hosted on OSB\cite{osb_ca1_url} by simply declaring a \verbx{CA1PyramidalCellModel} class, inheriting from \verbx{NeuroConstructModel}.  
This basic implementation simply ``wraps'' the components of the existing model, with simulator interaction taken care of by \verbx{NeuroConstructModel} methods; 
thus, only the code shown in Fig. \ref{fig:ca1_model} is required. 
All OSB models, and indeed any NeuroML model, can be tested similarly. 
Working together with OSB is part of our \textbf{first collaboration}, and our integration efforts can be publicly tracked\cite{neuroconstruct_rgerkin_url}.

Spanning a range of scales and original development environments, all OSB models are formally described using NeuroML, as are all model components and sub-components, such as cells, ion channels, calcium stores, etc. 
These models are regularly executed on OSB servers to ensure that their output remains consistent as they are updated. 
Therefore, OSB can confirm that they \textit{do} work, while linked journal articles, on-site wiki, and code inspection can establish \textit{how} they work. 
However, there is no mechanism for establishing \textit{how well} they work, i.e. how well the models accord with data. 
\textit{NeuroUnit} fills this gap by helping OSB (and the larger biology community) assess models using data-driven tests. 
\textit{SciUnit} can be applied similarly to other neuroscience (or biology) sub-disciplines using \textit{NeuronUnit} analogues written by the corresponding communities.

\begin{figure}
\begin{python}
class CA1PyramidalCellModel(NeuroConstructModel):
	"""CA1 Pyramidal Cell model from Open Source Brain."""
	def __init__(self,**kwargs):
		project_path = neuroconstruct.get_path("hippocampus","CA1_pyramidal_neuron","CA1PyramidalCell","neuroConstruct")
		models.NeuroConstructModel.__init__(self,project_path,**kwargs)
\end{python}
\vspace{-5px}
\caption{A model class corresponding to a CA1 Pyramidal Cell model from Open Source Brain}
\label{fig:ca1_model}
\vspace{-15px}
\end{figure}

\subsubsection{Capabilities from NeuroTools}
NeuroTools\cite{neuralensemble_url} is a Python library supporting tasks associated with analysis of neural data (or model output), such as membrane potential time series, spike trains, etc. 
It is an open source and actively developed project, containing reliable algorithms on which to base neurophysiology tests.

We use NeuroTools to implement \textit{SciUnit} capabilities in \textit{NeuronUnit}. 
For example, an \verbx{AnalogSignal} object (e.g. a membrane potential time series) from NeuroTools has a threshold detection method that returns a NeuroTools \verbx{SpikeTrain} object. 
A \textit{NeuronUnit} \verbx{HasSpikeTrain} Capability requires that the method \verbx{getSpikeTrain} be implemented. 
\verbx{NeuroConstructModel} does so by placing the object method \verbx{AnalogSignal.threshold_detection} inside \verbx{getSpikeTrain}. 
Many such NeuroTools objects are similarly exchanged between \verbx{NeuroConstructModel} methods. 
This simplifies test writing, since basic model output properties are obtained trivially using NeuroTools object methods, and these NeuroTools objects are easily extracted from model output using candidate models subclassing \verbx{NeuroConstructModel}.

\subsubsection{Reference Data for Tests from NeuroElectro}
Answering \textit{how well} requires validation testing against data. 
The NeuroElectro project\cite{neuroelectro_url} is an effort to curate all published single cell neurophysiology data\cite{tripathy_neuroelectro:_2012}.  
Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning $>$ 2000 single pieces of published data extracted from article tables. 
We have made it easy to construct \textit{NeuronUnit} tests using the NeuroElectro API to get reference data. 
Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
The former is illustrated in Figure \ref{fig:neuronunit_example}. 
Associated statistics of that data (e.g mean, standard error, and sample size) are attached and enable judgement of model output according to a chosen scoring mechanism. 
While NeuroElectro alone cannot judge all model aspects, it can serve to validate basic features of many neurophysiology models, such as resting membrane potential, action potential width, after-hyperpolarization amplitude, etc. 
As NeuroElectro is the only publicly curated source of such data, it represents a key component for \textit{NeuronUnit} test constuction.  
Continued development of the NeuroElectro API, through which data are systematically exposed to test authors, represents our \textbf{second collaboration}\cite{neuroelectro_dev_url}.

% Section 4.
\section{Research and Development Plan}

\subsection{A Complete Pipeline}
Although the tools described in Sec. \ref{sec:neuronunit_acitivities} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal. 
In the \textit{NeuronUnit} repository\cite{neurounit_url} is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
It (1) selects an OSB model; 
(2) simulates it using NeuroConstruct; 
(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTestDynamic}; 
and (4) computes and prints a test score (Figure~\ref{fig:neuronunit_example}).

\begin{figure}
\begin{python}
# Interface with neuroelectro.org to search for spike widths of CA1 Pyramidal cells. 
reference_data = NeuroElectroSummary(neuron={'id':85}, ephysprop={'id':23})
reference_data.get_values()  # Get summary data for the above. 
model = CA1PyramidalCellModel(population_name="CG_CML_0") # Initialize the model with some parameters.
test = SpikeWidthTestDynamic( # Initialize the test.    
	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics from the reference data
	model_args = {'current':40.0}, # Somatic current injection in pA.  
	comparator = ZComparator), # A comparison class that implements a Z-score.  
result = sciunit.judge(test,model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
result.summarize() # Summarize the result.  
\end{python}
\caption{Working example of a testing in \textit{NeuronUnit}}
\label{fig:neuronunit_example}
\vspace{-15px}
\end{figure}

\subsection{Creating New Models, Capabilities, and Tests}
\textit{NeuronUnit} provides base classes to enable rapid generation of models, capabilities, and tests for neurophysiology data. 
However these objects can also be created from scratch, requiring only adherence to the \textit{SciUnit} interface. 
For example, a Model could implement an \verbx{integrate} capability method by wrapping execution of a MATLAB script and a \verbx{get_spikes} capability method by parsing a .csv file on disk; 
a Test could be initialized using empirical spike rates collected in the lab.  
While this does not meet our idealized vision of development and testing, in practice this may be a common scenario. 
As part of our outreach efforts (Sec. \ref{sec:broader_impacts}) we will train modelers in the use of this framework, and encourage them to use it as part of their workflow of choice. 
Adoption of \textit{SciUnit} into traditional, custom workflows would be reflected in the Methods sections of articles.

\subsubsection{Visualization}
\label{sec:scidash_visualization}
There are many possibilities for visualization of specific test results though \textit{SciDash}. 
When a test record is selected from the record matrix (Fig. \ref{fig:scidash_matrix}), it can point to a Sage notebook\cite{sagenb_url}, whose ``worksheets'' facilitate visualization and storage of executed code. 
While Sage was written for Python, the notebook also supports the execution of code and visualization of outputs from other programming languages, making possible worksheets based on MATLAB, Mathematica, and other popular environments for modeling. 
Even with \textit{SciUnit} written in Python, calls to other languages can still be issued, and their results visualized using these worksheets.

\subsubsection{Collaboration}
Community-moderated comments on GitHub will allow test-makers and test-takers to discuss issues associated with test suites. 
On GitHub, these takes the form of ``issues,'' commit messages, and comments surrounding merge requests from forked repositories. 
Thus, disagreements about the appropriateness of a test can be openly aired and in many cases resolved. 
The \textit{SciDash} website itself can also support public comment to extend the features of GitHub. 
More importantly, we will enable sorting and filtering of \textit{SciDash} results by repository statistics, e.g. the volume of activity and the number of followers, via the GitHub API. 
This will allow the most important test suites, as judged by each community, to be featured prominently on \textit{SciDash}. 
Simple tagging should enable filtering by subject matter. 
We also will support open authentication via existing web applications (Google, Twitter, etc.), lowering the barrier to participation.

\subsubsection{Population}
\textit{SciDash} will regularly run scripts that (1) read the GitHub repositories, (2) run any outstanding tests on new or existing models, and (3) format the results. 
In order to quickly populate \textit{SciDash} with repositories that are both useful and illustrative, we will use \textit{SciUnit} to recapitulate the results of some ``settled'' competitions as \textit{SciDash} repositories, i.e. we will encode the competition rules as tests and \textit{SciDash} will then index the results. 
There are several examples of settled competitions which have publicly available rules, entries, and results against which to check\cite{jolivet_quantitative_2008,hopfield_what_2000,neural_prediction_url}.

\subsection{Challenges}
Here we describe theoretical and practical challenges to implementation, and how they can be overcome.

\subsubsection{Participation from Modeling Communities}
Modelers may not want to expose model capabilities, a requirement of test-taking.  
We anticipate four solutions: \textbf{First}, interfacing a model to \textit{SciUnit} requires only implementing selected model capabilities. 
Often this means identifying native model procedures that satisfy a capability, and wrapping their functionality. 
This can require as little as one line of code. 
Importantly, the modeler is not required to expose or rewrite any model flow control. 
\textbf{Second}, we support multiple environments automatically by using NeuroML\cite{gleeson_neuroml:_2010}, and other simulator-independent model descriptions are possible for other domains. 
Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator\cite{neuron_url}, this functionality is already mature and in use. 
This minimizes modeler effort for a large and growing number of models. 
\textbf{Third}, modelers have an incentive to demonstrate publicly their models' validity. 
Participation in public modeling competitions (Sec. \ref{sec:existing_efforts}) demonstrates this incentive. 
\textbf{Fourth}, modelers have an incentive to use \textit{SciUnit} during development (see TDD, above) to ensure that ongoing development preserves correspondence between model and data. 
A popular test suite can represent a ``gold standard'' by which progress during development is judged.

\subsubsection{Participation from Experimental Communities}
Experimentalists may not want to write tests derived from their data.  We anticipate four solutions: \textbf{First}, tests require no special data formatting; only a list of required  capabilities (for selecting eligible models), optional metadata (as run-time arguments), and a statistical data summary (for scoring tests) are required.  A unit test is focused and does not require arbitrary computations on data.  For example, suppose intracellular current injection evokes 100 action potentials, the width of which is of interest.  Writing the test consists of selecting \verbx{ReceivesCurrent} and \verbx{ProducesActionPotentialShape} capabilities (one line of code each), computing the mean and variance of action potential widths (one line of code), specifying current injection parameters, e.g. amplitude and duration (two lines of code), and selecting a scoring mechanism from \verbx{sciunit.scores}, e.g. (colloquially) ``Must be $<$ 1 standard deviation of the mean'' (one line of code).  This example can be found in \verbx{NeuronUnit.tests.SpikeWidthTest}; heavy-lifting is done by the interface.
\textbf{Second}, data-sharing is becoming accepted, and test-writing can be distributed across scientists, including non-experimentalists with other aims such as analysis or modeling. 
\textbf{Third}, many tests can be automatically generated using the NeuroElectro API, and the continued emergence of such data-aggregation initiatives will expand these possibilities. 
\textbf{Fourth}, an incentive to write tests for one's data exists: the ability to identify models that give the data clear context and impact.

\subsubsection{Diversity of Levels and Kinds of Models and Data}
The diversity of topics in biology is vast. 
\textbf{First}, we address this by providing an interface allowing modelers to express specific capabilities.  
This capability set determines the range of eligible tests.  Scale hierarchies are embedded in capability inheritance.  =
For example, \verbx{HasActionPotentials} inherits from \verbx{HasNeurons}, and \verbx{HodgkinHuxley} inherits from \verbx{VoltageGated}. 
Thus, incompatibility of a test-requiring-action-potentials for a model-lacking-neurons is known without explicit tagging. 
\textbf{Second}, NeuroML naturally addresses diversity of scales because it is organized hierarchically, in ``levels.''  
Models can be sub- or supersets of other models; similarly for SBML\cite{sbml_url,hucka_systems_2003}, a general systems biology markup language. 
\textbf{Third}, cross-level testing can use ``Representional Similarity Analysis'' (RSA)\cite{kriegeskorte_representational_2008}, requiring only that a model respond to defined inputs (e.g. stimuli). 
A ``similarity matrix'' for input responses defines a unique model signature, and can serve as intermediate test output. 
Goodness-of-fit between similarity matrices for model and experiment determines test scores; 
these matrices are independent of model scale because their size depends only on test inputs, not system detail.

\subsubsection{Arbitrary Scoring Criteria for Tests}
A test first assesses goodness-of-fit, and applies a normalization (e.g. pass/fail, 0.0-1.0) to generate a score. 
Arbitrary choices at both stages may benefit some models over others.  \textbf{First}, however, rank-ordering is constant across many goodness-of-fit metrics, meaning that choice of metric will rarely cause an otherwise passing model to fail and vice versa. 
For example, given a data mean and variance, ordering model output by Z-score or p-value will yield the same relative ranking of models. 
Indeed, rank ordering of models may prove more valuable than test scores themselves. 
\textbf{Second}, suite repositories are open (e.g. Fig. \ref{fig:scidash_repo}), so tests can be cloned and new statistical choices implemented. 
Statistics as applied to neuroscience have been notoriously ``fast and loose''; 
identification and correction of flawed methodology is becoming increasingly common\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010,fish_fmri_url}, and is accelerated by an open framework. 
The community can judge which test version is most appropriate, i.e. what a model \textit{should} do -- this process documented via standard moderation techiniques used on GitHub -- and the \textit{SciUnit} framework determines whether the model \textit{does} it.

\subsubsection{Reliability of Data Underlying Tests}
Unreliable data can undermine model validation. 
\textbf{First}, the community must evaluate experimental design and methods, discounting data produced using questionable techniques. 
GitHub supports community moderation, permitting users to comment on tests, indicating their concerns. 
Suite repository popularity, by which \textit{SciDash} results can be filtered, can reflect consensus. 
Experimental metadata also constrains a test's relevance, so test writers should select data with metadata appropriate to the system being modeled, and attach the metadata to resulting test scores. 
Metadata can also be expressed as Capabilities, e.g. \verbx{At37Degrees} or \verbx{Calcium3mM}; and tests can require that models express them. 
Such capabilities require no implementation, so the model definition must only inherit them. 
\textbf{Second}, models cannot perfectly reproduce data that is itself a random draw from a ``true'' distribution. 
Uncertainty in data must be made explicit, by asking how well a data set validates its own experimental replications\cite{kriegeskorte_representational_2008}. 
The degree of such ``self-validation'' represents the upper limit of what a model can be expected to achieve, and should represent a ``perfect'' score.

\subsubsection{Occam's Razor}
All things being equal, simpler models are better. 
Model complexity has many definitions, so \textit{SciDash} will report several complexity metrics\cite{mccabe_complexity_1976}, including: 
1) model length; 2) memory use; 3) CPU load; 4) \# of capabilities. 
\textit{SciDash} will report the model validity vs complexity tradeoff in tabular form (e.g. Table \ref{table:record_matrix}), and in a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot. 
The set of models which \textit{dominate} all others, i.e. that have the highest validity for a given complexity, can be represented as a ``frontier'' in such a scatter plot, a visualization familiar from the symbolic regression package Eureqa\cite{schmidt_distilling_2009}.

\subsubsection{Expansion Into Other Areas of Biology}
After covering neurophysiology, we would like \textit{SciUnit} to be applied across neuroscience and in other biological sciences. 
The framework is discipline-agnostic, so community participation and model description are the only obstacles. 
Community participation begins with enumerating the capabilities relevant to a sub-discipline, and then writing tests. 
Model description can expand within NeuroML (which already covers multiple levels within neuroscience) and tools for capability implementation can incorporate libraries for neuroimaging (NiBabel\cite{nibabel_url}), neuroanatomy (NeuroHDF,\cite{neurohdf_url}) and other sub-disciplines. 
SBML\cite{hucka_systems_2003,sbml_url} will enable expansion beyond neuroscience, facilitated by parallel efforts among NeuroML developers to interface with it (Crook, unpublished). 
One intriguing possiblity is applying \textit{SciUnit} to the OpenWorm project\cite{open_worm_url}, which through open, collaborative development seeks to model the entire organism C. elegans.

% Section 5.
\section{Broader Impacts}
\label{sec:broader_impacts}
\subsection{Education}
\label{sec:education}
The scientific method is a cornerstone of basic science education. 
However, its application in professional science is often informal and therefore of limited pedagogical value. 
\textit{SciDash} will provide a window to the scientific method in practice, illustrating which hypotheses (models) withstand the scrutiny of evidence (pass tests). 
Hypothesis (model) revision will be transparent through version control and repository lineage on GitHub. 
The ability to visualize the scientific method in practice from any computer in the world will represent a major step forward in science education.

\begin{wraptable}[10]{r}{0.7\columnwidth}
\vspace{-7px}
\caption{A record matrix illustrating models and data-driven tests from the history of cosmology. Each row is a model; each column is a test.}
\label{table:record_matrix}
\begin{tabular}{| c | c | c | c | c | c | c }
\hline
    & \textit{Complexity} & \textbf{Babylon} & \textbf{Brahe} & \textbf{Galileo} & \textbf{Le Verrier} \\ \hline
  \textbf{Ptolemy} & Medium & \textcolor{ForestGreen}{Pass} & \textcolor{Red}{Fail} & \textcolor{Red}{Fail} & \textcolor{Red}{Fail} \\ \hline
  \textbf{Copernicus} & Low & \textcolor{ForestGreen}{Pass} & \textcolor{Red}{Fail} & \textcolor{Red}{Fail} & \textcolor{Red}{Fail} \\ \hline
  \textbf{Kepler} & Medium & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{Red}{Fail} \\ \hline
  \textbf{Newton} & Low & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{Red}{Fail} \\ \hline
  \textbf{Einstein} & High & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} \\ \hline
\end{tabular}
\end{wraptable}
\leavevmode
\leavevmode
\leavevmode

As a pedagogical tool, we will provide \textit{SciDash} repositories for historical case studies. 
For example, Table \ref{table:record_matrix} summarizes 5 astronomical models and 4 validation tests derived from, and recapitulating, the history of cosmology. 
This shows the scientific method to be an on-going process. 
Ptolemy's geocentric model\cite{ptolemy_almagest_150} passes a test derived from Babylonian records of planetary motion. 
Ptolemy's model fails other tests shown here, including one constructed from Brahe's more meticulous measurements\cite{kepler_rudolphine_1627}, falsifying Ptolemy's hypothesis of circular orbits. 
The Copernican heliocentric model\cite{copernicus_revolutionibus_1543} also uses circular orbits and fails Brahe's test, but is simpler than Ptolemy's model, dispensing with ``epicycles.'' 
Kepler's laws of planetary motion permit elliptic orbits\cite{kepler_astronomia_1609}, as well as Galileo's discovery of elliptic orbits among Jupiter's moons\cite{galilei_siderius_1610}. 
Newton's model passes these tests and does so by unifying Kepler's laws under the principle of gravity\cite{newton_philosophiae_1687}. 
Newton's model cannot explain Mercury's perihelion precession\cite{le_verrier_lettre_1859}, solved only by General Relativity\cite{einstein_foundation_1916}. 
This account is simplistic compared with testing practice in modern biology, but it is appropriate for pre-baccalaureate teaching. 
\textit{SciDash} will index and highlight such case studies for teaching.

\bibliographystyle{unsrt}
\bibliography{references,references_crook,urls,references_ja}
%\listoftodos
\end{document}

### 2013-09-24 NeurounitFrontiers/Paper.tex
Condensed

@@
 Importantly, the validation criteria in each case are made explicit by the specification of a test suite, so modelers need not guess which criteria are being used to validate or invalidate their model.
-Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and scientists who wish to promote different criteria need only derive alternative test suites.
+Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative test suites.
 In many cases, models require no modifications to take the new tests because the same type of model output is being requested.
@@
 
-The \verbx{sciunit.judge} function operates in three phases: 
-\textbf{(1) Capability Checking}: The model is verified as capable of taking the test by checking each capability in the test's \verbx{required_capabilities} attribute; 
-\textbf{(2) Test Execution}: The test's \verbx{run_test} method is called to execute the model and the output is cached. 
-\textbf{(3) Output Validation}: \verbx{run_test} returns an instance of a \verbx{sciunit.Score} subclass containing a goodness-of-fit metric between the model output and the data used to parameterize the test.
-Any errors that occur during this process are reported by raising an appropriate exception.
-
-\subsection{\textit{SciUnit} Test Suites}
-A test suite is a collection of tests designed to validate a model against several mutually coherent requirements, i.e. various summaries of the data.  
+Collection of tests with mutually coherent requirments, i.e. various summaries of the available empirical data, can form test suites.
 The following is a test suite that could be used for a simplified version of the QSNMC:  
@@
 
-\subsection{\textit{SciUnit} Design Considerations}
-Each community can collaboratively specify capabilities capturing the high-level semantics of their preferred modeling formalisms. 
-Existing modeling standards (e.g.
-NeuroML\cite{neuroml_url,gleeson_neuroml:_2010}) can be leveraged to simplify this process.
-\textbf{\textit{SciUnit}, written in Python, was designed to make test construction (from data) and test-driven model execution exceptionally easy and flexible.}
-All figures shown here containing code blocks make use of this framework.
-
-\subsection{\textit{SciDash}: A community web application}\label{sec:scidash}
-This framework is most effective when the current state of a research area is represented by a collection of tests and models. 
-This requires coordination among research groups, so community-oriented cyberinfrastructure to support test suite creation and summarization, building upon \textit{SciUnit}, is essential.
-We developed a service called \textit{SciDash}, utilizing existing infrastructure for coordinated development of software repositories, and focusing on GitHub\cite{github_url}\cite{ram_git_2013}. 
-A suite of related tests will be contained in a GitHub repository with a stereotyped high-level structure allowing the \textit{SciDash} web application to discover, index and summarize it continuously (Fig.
-\ref{fig:scidash_repo}).
-
-\begin{wrapfigure}[18]{r}{0.45\textwidth}
-\center
-\vspace{-10px}
-\includegraphics[scale=0.72]{scidash_github.png}
-\caption{A \textit{SciDash} repository on GitHub}
-\label{fig:scidash_repo}
-\end{wrapfigure}
-\vspace{-10px}
-\leavevmode
-
-Test results can be visualized as a ``record matrix'' composed of large numbers of model/test combinations (Fig. \ref{fig:scidash_matrix}).  
-Each row in this matrix contains results for all tests taken by one model and serve as clear evidence of that model's scope and validity.  
-Models, tests, and records will be stored on GitHub, pointed to by hyperlinks in the record matrix. 
-\textit{SciDash} serves as a public record of competition among models, facilitating and encouraging data-driven development among modelers.
-\textbf{Thus, the second product of this proposal is a web application called \textit{SciDash}, whose back-end can index test suite repositories collaboratively developed on GitHub, and whose front-end offers users a simple environment for discovery and evaluation of models, tests, and records.}
+% Section 3.
+\section{Results}
 
@@
 
-% Section 3.
-\section{Results}
-
-\subsection{\textit{SciDash} Activities}\label{sec:scidash_activities}
-The \textit{SciDash} web application points to test suite repositories and aggregates test results for scientific communities \cite{scidash_url}. 
-It is populated with models and tests from the educational illustration in Table \ref{table:record_matrix} (section~\ref{sec:education}). 
-\textit{SciDash} exists in three layers.
-The \textbf{first layer} is completely under the control of individual developer communities, and consists of git repositories. 
-Git is the most popular implementation of ``version control'' among developers today\cite{ram_git_2013}, and is increasingly used for open science projects (e.g. OSB\cite{osb_url}). 
-The GitHub website\cite{github_url} is the most popular location for collaborative code development using git. 
-\textit{SciDash} identifies all similarly structured repositories (by tracking the lineage of the repository above using the GitHub API).
-This list of repositories will be indexed by \textit{SciDash} to form the \textbf{second layer}, an overview of the state of all \textit{SciDash} repositories on GitHub.  
-This index is searchable and filterable on the \textit{SciDash} website to identify repositories of interest to a particular research community.  
-The \textbf{third layer} is a ``dashboard'' view of the state of a field, visible through a matrix of records for model/test combinations in a GitHub repository (Fig. \ref{fig:scidash_repo}). 
-Each record links to test records (stored in the repository), displaying line-by-line the executed code and intermediate output statements, as well as the underlying models and tests.
-
-\begin{figure}%[18]{r}{1\textwidth}
-\includegraphics[scale=0.65]{table.png}
-\caption{A \textit{SciDash} record matrix}
-\label{fig:scidash_matrix}
-\vspace{-15px}
-\end{figure}
-\vspace{-10px}
-\leavevmode
-
-\subsection{\textit{NeuronUnit} Activities}
 \label{sec:neuronunit_acitivities}
@@
 
+\subsection{\textit{SciDash}: A community web application}\label{sec:scidash}
+A collection of tests, models, and test records can summarize the current state of modeling in a research area.  
+Community-oriented cyberinfrastructure to support the creation and summarization of such collections is essential.
+We used a service called \textit{SciDash} \cite{scidash_url} for coordinated development of software repositories.
+
+\begin{wrapfigure}[18]{r}{0.45\textwidth}
+\center
+\vspace{-10px}
+\includegraphics[scale=0.72]{scidash_github.png}
+\caption{A \textit{SciDash} repository on GitHub}
+\label{fig:scidash_repo}
+\end{wrapfigure}
+\vspace{-10px}
+\leavevmode
+
+\textit{SciDash} exists in three layers.
+The \textbf{first layer} is completely under the control of individual developer communities, and consists of git repositories \cite{ram_git_2013} stored on GitHub \cite{github_url}. 
+\textit{SciDash} identifies all similarly structured repositories (by tracking the lineage of a vanilla \textit{SciDash} repository above using the GitHub API).
+This list of repositories is indexed by \textit{SciDash} to form the \textbf{second layer}, an overview of the state of all \textit{SciDash} repositories on GitHub.  
+This index is searchable and filterable on the \textit{SciDash} website to identify repositories of interest to a particular research community.  
+The \textbf{third layer} is a ``dashboard'' view of the state of a field, visible through a matrix of records for model/test combinations in a GitHub repository (Fig. \ref{fig:scidash_repo}). 
+Test records are visualized as a ``record matrix'' composed of large numbers of model/test combinations (Fig. \ref{fig:scidash_matrix}).  
+Each row in this matrix contains results for all tests taken by one model and serve as clear evidence of that model's scope and validity.  
+Hyperlinks in the record matrix point to models, tests, and records available on GitHub. 
+Each record links to test records (stored in the repository), displaying line-by-line the executed code and intermediate output statements, as well as the underlying models and tests.
+
+\begin{figure}%[18]{r}{1\textwidth}
+\includegraphics[scale=0.65]{table.png}
+\caption{A \textit{SciDash} record matrix}
+\label{fig:scidash_matrix}
+\vspace{-15px}
+\end{figure}
+\vspace{-10px}
+\leavevmode
+
 % Section 4.
-\section{Research and Development Plan}
+\section{Discussion}
 
@@
 
-\subsubsection{Visualization}
-\label{sec:scidash_visualization}
-There are many possibilities for visualization of specific test results though \textit{SciDash}. 
-When a test record is selected from the record matrix (Fig.
-\ref{fig:scidash_matrix}), it can point to a Sage notebook\cite{sagenb_url}, whose ``worksheets'' facilitate visualization and storage of executed code.
-While Sage was written for Python, the notebook also supports the execution of code and visualization of outputs from other programming languages, making possible worksheets based on MATLAB, Mathematica, and other popular environments for modeling.
-Even with \textit{SciUnit} written in Python, calls to other languages can still be issued, and their results visualized using these worksheets.
-
 \subsubsection{Collaboration}
@@
 
-\subsubsection{Population}
-\textit{SciDash} will regularly run scripts that (1) read the GitHub repositories, (2) run any outstanding tests on new or existing models, and (3) format the results. 
-In order to quickly populate \textit{SciDash} with repositories that are both useful and illustrative, we will use \textit{SciUnit} to recapitulate the results of some ``settled'' competitions as \textit{SciDash} repositories, i.e.
-we will encode the competition rules as tests and \textit{SciDash} will then index the results.
-There are several examples of settled competitions which have publicly available rules, entries, and results against which to check\cite{jolivet_quantitative_2008,hopfield_what_2000,neural_prediction_url}.
-
-\subsection{Challenges}
-Here we describe theoretical and practical challenges to implementation, and how they can be overcome.
-
-\subsubsection{Participation from Modeling Communities}
+\subsection{Participation from Modeling Communities}
 Modelers may not want to expose model capabilities, a requirement of test-taking.  
@@
 
-\subsubsection{Participation from Experimental Communities}
+\subsection{Participation from Experimental Communities}
 Experimentalists may not want to write tests derived from their data.
@@
 
-\subsubsection{Diversity of Levels and Kinds of Models and Data}
+\subsection{Diversity of Levels and Kinds of Models and Data}
 The diversity of topics in biology is vast. 
@@
 
-\subsubsection{Arbitrary Scoring Criteria for Tests}
+\subsection{Arbitrary Scoring Criteria for Tests}
 A test first assesses goodness-of-fit, and applies a normalization (e.g. pass/fail, 0.0-1.0) to generate a score. 
@@
 
-\subsubsection{Reliability of Data Underlying Tests}
+\subsection{Reliability of Data Underlying Tests}
 Unreliable data can undermine model validation. 
@@
 
-\subsubsection{Occam's Razor}
+\subsection{Occam's Razor}
 All things being equal, simpler models are better. 
@@
 
-\subsubsection{Expansion Into Other Areas of Biology}
+\subsection{Expansion Into Other Areas of Biology}
 After covering neurophysiology, we would like \textit{SciUnit} to be applied across neuroscience and in other biological sciences. 
@@
 
-% Section 5.
-\section{Broader Impacts}
-\label{sec:broader_impacts}
-\subsection{Education}
-\label{sec:education}
-The scientific method is a cornerstone of basic science education. 
-However, its application in professional science is often informal and therefore of limited pedagogical value. 
-\textit{SciDash} will provide a window to the scientific method in practice, illustrating which hypotheses (models) withstand the scrutiny of evidence (pass tests). 
-Hypothesis (model) revision will be transparent through version control and repository lineage on GitHub. 
-The ability to visualize the scientific method in practice from any computer in the world will represent a major step forward in science education.
-
-\begin{wraptable}[10]{r}{0.7\columnwidth}
-\vspace{-7px}
-\caption{A record matrix illustrating models and data-driven tests from the history of cosmology. Each row is a model; each column is a test.}
-\label{table:record_matrix}
-\begin{tabular}{| c | c | c | c | c | c | c }
-\hline
-    & \textit{Complexity} & \textbf{Babylon} & \textbf{Brahe} & \textbf{Galileo} & \textbf{Le Verrier} \\ \hline
-  \textbf{Ptolemy} & Medium & \textcolor{ForestGreen}{Pass} & \textcolor{Red}{Fail} & \textcolor{Red}{Fail} & \textcolor{Red}{Fail} \\ \hline
-  \textbf{Copernicus} & Low & \textcolor{ForestGreen}{Pass} & \textcolor{Red}{Fail} & \textcolor{Red}{Fail} & \textcolor{Red}{Fail} \\ \hline
-  \textbf{Kepler} & Medium & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{Red}{Fail} \\ \hline
-  \textbf{Newton} & Low & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{Red}{Fail} \\ \hline
-  \textbf{Einstein} & High & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} & \textcolor{ForestGreen}{Pass} \\ \hline
-\end{tabular}
-\end{wraptable}
-\leavevmode
-\leavevmode
-\leavevmode
-
-As a pedagogical tool, we will provide \textit{SciDash} repositories for historical case studies. 
-For example, Table \ref{table:record_matrix} summarizes 5 astronomical models and 4 validation tests derived from, and recapitulating, the history of cosmology. 
-This shows the scientific method to be an on-going process. 
-Ptolemy's geocentric model\cite{ptolemy_almagest_150} passes a test derived from Babylonian records of planetary motion. 
-Ptolemy's model fails other tests shown here, including one constructed from Brahe's more meticulous measurements\cite{kepler_rudolphine_1627}, falsifying Ptolemy's hypothesis of circular orbits. 
-The Copernican heliocentric model\cite{copernicus_revolutionibus_1543} also uses circular orbits and fails Brahe's test, but is simpler than Ptolemy's model, dispensing with ``epicycles.'' 
-Kepler's laws of planetary motion permit elliptic orbits\cite{kepler_astronomia_1609}, as well as Galileo's discovery of elliptic orbits among Jupiter's moons\cite{galilei_siderius_1610}. 
-Newton's model passes these tests and does so by unifying Kepler's laws under the principle of gravity\cite{newton_philosophiae_1687}. 
-Newton's model cannot explain Mercury's perihelion precession\cite{le_verrier_lettre_1859}, solved only by General Relativity\cite{einstein_foundation_1916}. 
-This account is simplistic compared with testing practice in modern biology, but it is appropriate for pre-baccalaureate teaching. 
-\textit{SciDash} will index and highlight such case studies for teaching.
-
 \bibliographystyle{unsrt}

### 2013-09-25 NeurounitFrontiers/Paper.tex
Revisions

@@
 
-Here we describe a model-testing library that draws inspiration from ``unit tests'', a common form of software testing that validates a single component of a computer program against a single correctness criterion.
+Here we describe a model-testing library for neuroscience that draws inspiration from ``unit tests'', a common form of software testing that validates a single component of a computer program against a single correctness criterion.
 This is realized by using the \textit{SciUnit} Python framework for analogous ``model validation tests'' -- 
@@
 These models are characterized by their \textit{scope}: the set of observable quantities that the model can generate predictions about, and by their \textit{validity}, the extent to which these predictions agree with empirical observations of those quantities.
-As the quantity of models and empirical data in neuroscience proliferates, it is increasingly challenging to efficiently discover models whose scope is of interest and then assessing their validity against this mountain of data.
+As the quantity of models and empirical data in neuroscience proliferates, it is increasingly challenging to efficiently discover models whose scope is of interest and to then assess their validity against this mountain of data.
 
@@
 Although authors may refer to some relevant experimental data and alternative models, these comparisons are incomplete and tend to serve the goals of authors rather than readers. 
-However, making exhaustive comparisons to exisiting models and data would make such publications encyclopedic and obscure their main points. 
-Thus, a strength of publication is its focused description of how a model works and its conceptual advances. 
+However, making exhaustive comparisons to existing models and data would make such publications encyclopedic and obscure their main points. 
+Thus, a strength of publication is its focused description of \textit{how} a model works and its conceptual advances. 
 A weakness, however, is that evaluating the scope and validity of a model is intractable using a publication alone. 
@@
 
-There are related efforts in the machine learning community to develop models and validate them against standardized, publicly-available datasets according to well-specified metrics. 
-Kaggle\cite{kaggle_url} drives model development by organizing competitions where training data is made public and competitors submit competing algorithms, compared automatically by cross-validated accuracy on an unrevealed test set.
-The success of Kaggle shows that open competitions are effective\cite{carpenter_may_2011}, and that a ``modeling as a competition'' paradigm attracts data scientists across traditional discipline boundaries.
-On the other hand, Kaggle focuses solely on a few general cases in machine learning: classification, regression, and clustering, where validation criteria are straightforward.
-
-Discipline-specific competitions having a similar structure but with more sophisticated validation criteria within neuroscience have also resulted in important advances. 
+Modeling competitions in neuroscience have resulted in important advances. 
 For example, the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} addressed the complexity-accuracy tradeoff among reduced models of excitable membranes; 
@@
 
-Recognizing that neuroscience contains a wide variety of models that aim to explain phenomena at multiple levels, we leveraged a discipline-agnostic Python framework called \textit{SciUnit}\cite{sciunit_url} to create tools for testing neuroscience models and associated tests.
-The result is \textit{NeuroUnit}, which extends \textit{SciUnit} into neuroscience by supporting the testing of models described using \textit{NeuroML}, the construction of test logic using \textit{NeuroTools} \cite{neurotools_url}, and employing a test ``answer key" using electrophysiology data from the \textit{NeuroElectro Project} \cite{neuroelectro_url}.
-In addition to this open testing framework we also provide a library of tests for models of spiking single neurons.
-
-% Section 2.
-\section{Fundamentals of Testing}
-\vspace{-12px}
 \begin{wrapfigure}{r}{0.6\textwidth}
@@
 \vspace{-0px}
+Recognizing that neuroscience contains a wide variety of models that aim to explain phenomena at multiple levels, we leveraged a discipline-agnostic Python framework called \textit{SciUnit}\cite{sciunit_url} to create tools for testing neuroscience models and associated tests.
+The result is \textit{NeuroUnit}, which extends \textit{SciUnit} into neuroscience by supporting the testing of models described using \textit{NeuroML}, the construction of test logic using \textit{NeuroTools} \cite{neurotools_url}, and employing a test ``answer key" using electrophysiology data from the \textit{NeuroElectro Project} \cite{neuroelectro_url}.
+In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
 
-The \textit{SciUnit} framework is organized around simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.
+% Section 2.
+\section{Implementation of Testing}
 
@@
 
-\subsection{Example: Neural Membrane Potential Dynamics} To clarify the basic ideas, we begin by describing a test suite related to single-neuron neurophysiology. 
-The tests in this suite are designed for experiments where stimuli are delivered to neurons of a particular type, as somatically injected current (in pA), while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
+Simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.
+We begin by describing abstractly the outlines of a test suite related to single-neuron neurophysiology.
+Suppose that the tests in this suite are designed for experiments where stimuli are delivered to neurons as somatically injected current (in pA), while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
 A model claiming to capture this cell type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.
@@
 
-Fig. \ref{fig:rate_test} shows how a scientist would implement the spike count test described in the preceding section using \textit{SciUnit}. 
+Fig. \ref{fig:rate_test} shows how a scientist would implement the spike count test described above using \textit{SciUnit}. 
 A \textit{SciUnit} validation test is an {instance} of a Python class implementing the \verbx{sciunit.Test} interface. 
-Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor (in Python, the constructor is always named \verbx{__init__}; the parameters' meaning is documented on lines 5-8).
+Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor; the parameters' meaning is documented on lines 5-8). 
 For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
@@
 We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test.
-As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their field so that test generation for a particular system of interest will often consist simply of instantiating a previously-developed family with particular experimental parameters and data.
-For single-neuron tests like the \verbx{SpikeCountTest}, we have developed a library to facilitate development (Sec. \ref{sec:neuronunit}).
+As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often consist simply of instantiating a previously-developed family with particular experimental parameters and data.
+For single-neuron tests like the \verbx{SpikeCountTest}, we have developed a library \cite{neurounit_url} to facilitate development (Sec. \ref{sec:neuronunit}).
 

### 2013-09-26 NeurounitFrontiers/Paper.tex
Updated abstract

@@
 \section{Abstract}
-Rigorously validating a scientific model’s explanatory power requires comparing its predictions against empirical data -- both data available during model development and data gathered after publication.
-However, model validation remains an informal and incomplete process, especially in neuroscience.   
-This makes it difficult to evaluate a model's strengths and weaknesses, or to adequately compare two models.
+Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
+However, model validation remains an informal and incomplete process, especially in fields, like neuroscience, where the available data is growing rapidly.   
+This makes it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models to determine the state-of-the-art, and to precisely identify open modeling problems.
 
-Here we describe a model-testing library for neuroscience that draws inspiration from ``unit tests'', a common form of software testing that validates a single component of a computer program against a single correctness criterion.
-This is realized by using the \textit{SciUnit} Python framework for analogous ``model validation tests'' -- 
-executable functions validating models against an empirical observation by producing a score indicating model/data agreement. 
-We applied this framework to neuroscience to produce \textit{NeuroUnit}, a library for test construction in neuroscience, and a repository of useful tests.
+Software engineers validate software by developing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion.
+Suites of such unit tests that collectively capture the desired program behavior provide evidence for its validity and correctness.
+Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' --
+executable functions, here written in Python, that compare model predictions against single empirical observations to  produce a score indicating agreement between the model and the data.
+Suites of such validation tests are used as a summary of modeling progress within a scientific community.
+Using this framework, we develop \textit{NeuroUnit}, a library that aids validation testing in neuroscience\todo{neurophys specifically?}.
 

### 2013-09-27 databases/databases_chapter.tex
Book chapter

\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{bibentry}

\begin{document}

Computational neuroscience produces models that can help to explain empirical data. 
Empirical and theoretical researchers can benefit from resources that facilitate discovery of these models and the data that informs both these and future models.

First, there are databases of computational models and model parts.  
The BioModels database (\url{http://www.ebi.ac.uk/biomodels-main}) is a general repository of computational models of biological processes.  
The SenseLab database, ModelDB, (\cite{migliore_modeldb_2003},\url{http://senselab.med.yale.edu/modeldb}) compiles user-submitted computational models developed specifically for simulating the electrophysiological and neurochemical properties of single neurons and networks of neurons (e.g., multi-compartment Hodgkin-Huxley type conductance based models \cite{hodgkin_quantitative_1952}). 
The Physiome Model Repository \url{http://www.cellml.org/tools/pmr} is a software suite that facilitates storage and management of models, focusing on those described in CellML, a standard markup language for biological models. 
Similarly, OpenSourceBrain (\url{http://www.opensourcebrain.org/}) is a community platform for collaborative development of computational neuron and network models that utilizes open standards such as NeuroML \cite{gleeson_neuroml:_2010} to facilitate interoperability and visualization of neuroscience models developed by different researchers.

Second, there are databases containing structured information specific to neurons and their properties. 
For example, information on the detailed shapes of neurons (i.e., their morphology) is being compiled by NeuroMorpho \url{http://neuromorpho.org} which contains user-submitted neuron morphological reconstructions made using the NeuroLucida format \cite{glaser_neuron_1990}. 
Measured electrophysiological properties of neuron types, and the metadata associated with these measurements, is catalogued in the NeuroElectro Project \url{http://neuroelectro.org}.  
Similarly, other SenseLab databases, including NeuronDB and CellPropDB (\cite{crasto_senselab:_2007},\url{http://senselab.med.yale.edu/NeuronDB/}), contain information on the ionic currents and neurotransmitters expressed by each neuron and how these are distributed with respect to neuronal morphology. 
Detailed information on ion channel subtypes, including voltage and temporal dynamics, genetic homology, and corresponding literature references is being compiled by Channelpedia (\cite{ranjan_channelpedia:_2011},\url{http://channelpedia.net/‎}), a subproject within the Blue Brain Project \citep{markram_blue_2006}.

Third, there are databases focusing on the anatomical organization of the brain.  
BrainInfo (\url{http://braininfo.rprc.washington.edu}) provides general information about brain areas, including what they do, where they are located, and what they contain.  
The Allen Institute for Brain Sciences provides brain-wide gene expression atlases, where the expression of each of the genes in the mammalian genome has been systematically quantified throughout the brain for a number of animal species and across stages of neural development (\cite{lein_genome-wide_2007}, \url{http://brain-map.org}). 
Similarly, the Allen Institute also provides information on the anatomical connectivity of different brain regions.
Parallel to this effort is The Human Connectome Project (\url{http://www.humanconnectomeproject.org}), a large-scale effort to map complete structural and functional neural connections \textit{in vivo} in individual humans. 
BrainMap (\url{http://www.brainmap.org}) consists of a database and related software to search published functional and structural human neuroimaging experiments.  
CoCoMac (\url{http://cocomac.g-node.org}), in contrast, is focused on the primate brain, containing records of tracing studies in the macaque. 
The Brain Architecture Management System (BAMS, \cite{bota_brain_2005}, \url{http://brancusi1.usc.edu}) contains neural connectivity information across species that has been manually curated from the existing research literature.  
Finally, Cell Centered Database (\url{http://ccdb.ucsd.edu}) focuses on images from light and electron microscopy, ranging from whole brain areas to subcellular compartments.

In addition to these neuroscience domain-specific databases are uber-databases that provide linking facilities for cross-resource data integration. 
For example, NeuroLex (\cite{larson_neurolex.org:_2013},\url{http://neurolex.org}), provides a platform for community annotation of neuron types on the basis of morphological, neurochemical, or electrophysiological properties. 
Given this wealth of neuroscience resources, the Neuroscience Information Framework (NIF, \cite{gardner_neuroscience_2008},\url{http://www.neuinfo.org}), provides tools for semantically searching across these diverse databases through the development and incorporation of neuroscience domain-specific ontologies \cite{bug_nifstd_2008,larson_ontologies_2009,hamilton_ontological_2012,imam_development_2012}. 
For example, in NIF, the search query ``mitral cell" returns a number of database records including relevant research literature from PubMed, computational models from ModelDB, and connectivity information from BAMS.

The number and size of these database continues to grow with the collection and contribution of ever more models and data.  
These databases give computational neuroscientists a powerful tool for constraining data-driven models and serve as an alternative to conventional literature searches.

\bibliographystyle{plainnat}
\nobibliography{shreejoy}

\end{document}

### 2013-09-28 databases/neuroelectro_chapter.tex
Added NeuroElectro chapter

\documentclass[12pt]{article}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage{bibentry}

\begin{document}

Computational neuroscientists have argued that the electrophysiological properties of neurons determine their computational roles.  
Furthermore, models containing or concerning neurons can be constrained or validated in part using empirical data on single cell electrophysiology.  
However, compared with imaging or genetic data, these data are infrequently published in a format that permits them to be easily discovered in the literature.  
The NeuroElectro Project (\url{http://neuroelectro.org}, \cite{neuroelectro_2013}) solves this problem by providing a database on the electrophysiological diversity of mammalian neuron types.

This database is populated primarily using automated text extraction from tables of journal articles using Python.  
A subset of records have been manually validated against the primary literature.  
Neuron types are identified using the NeuroLex ontology (\cite{larson_neurolex.org:_2013}, \url{http://neurolex.org}); 
Electrophysiological property types are identified using a custom ontology in the absence of standards.

While NeuroElectro contains information about 27 distinct electrophysiological properties, those most heavily represented include resting membrane potential, input resistance, action potental height and width, etc.  
The list of journals containing the source information include those from the Elsevier, Highwire, Wiley, and Oxford family of journals, including The Journal of Neuroscience, The Journal of Physiology, and The Journal of Neurophysiology, among others.  
Neuroelectro also contains details on each study’s experimental conditions (like species or electrode type used), the so-called ``metadata", obtained using similar text extraction techniques applied to article methods sections.

The NeuroElectro web interface (\url{http://neuroelectro.org} also permits users to contribute to the database’s content. 
For example, users can suggest relevant articles on a specific neuron type as well as validate content that has been extracted via our automated algorithms. 
Furthermore, users can elect to become “content-experts” on a specific neuron type and can then modify the database’s content directly.

NeuroElectro also contains analyses of the resulting database yielding novel relationships on the electrophysiological similarity of different neuron types throughout the brain. 
Among these are hierarchical classifications of neuron types by similarity of electrophysiological properties.  
The project maintainers are also aiming to relate gene expression patterns in specific cell types to those cells' electrophysiological properties, using expression data obtained through the Allen Brain Atlas (\cite{lein_genome-wide_2007}, \url{http://brain-map.org}).

\bibliographystyle{plainnat}
\nobibliography{shreejoy}

\end{document}

### 2013-09-28 databases/databases_chapter.tex
Added new references

@@
 First, there are databases of computational models and model parts.  
-The BioModels database (\url{http://www.ebi.ac.uk/biomodels-main}) is a general repository of computational models of biological processes.  
-The SenseLab database, ModelDB, (\cite{migliore_modeldb_2003},\url{http://senselab.med.yale.edu/modeldb}) compiles user-submitted computational models developed specifically for simulating the electrophysiological and neurochemical properties of single neurons and networks of neurons (e.g., multi-compartment Hodgkin-Huxley type conductance based models \cite{hodgkin_quantitative_1952}).
-The Physiome Model Repository \url{http://www.cellml.org/tools/pmr} is a software suite that facilitates storage and management of models, focusing on those described in CellML, a standard markup language for biological models.
-Similarly, OpenSourceBrain (\url{http://www.opensourcebrain.org/}) is a community platform for collaborative development of computational neuron and network models that utilizes open standards such as NeuroML \cite{gleeson_neuroml:_2010} to facilitate interoperability and visualization of neuroscience models developed by different researchers.
+The BioModels database (\cite{BioModels2010,BioModels2013}, \url{http://www.ebi.ac.uk/biomodels-main}) is a general repository of computational models of biological processes.  
+The SenseLab database, ModelDB, (\cite{migliore_modeldb_2003}, \url{http://senselab.med.yale.edu/modeldb}) compiles user-submitted computational models developed specifically for simulating the electrophysiological and neurochemical properties of single neurons and networks of neurons (e.g., multi-compartment Hodgkin-Huxley type conductance based models \cite{hodgkin_quantitative_1952}).
+The Physiome Model Repository (\cite{physiomemodelrepository_2011}, \url{http://www.cellml.org/tools/pmr} is a software suite that facilitates storage and management of models, focusing on those described in CellML, a standard markup language for biological models.
+Similarly, OpenSourceBrain (\cite{OSB_2012}, \url{http://www.opensourcebrain.org}) is a community platform for collaborative development of computational neuron and network models that utilizes open standards such as NeuroML (\cite{gleeson_neuroml:_2010}) to facilitate interoperability and visualization of neuroscience models developed by different researchers.
 
 Second, there are databases containing structured information specific to neurons and their properties. 
-For example, information on the detailed shapes of neurons (i.e., their morphology) is being compiled by NeuroMorpho \url{http://neuromorpho.org} which contains user-submitted neuron morphological reconstructions made using the NeuroLucida format \cite{glaser_neuron_1990}.
-Measured electrophysiological properties of neuron types, and the metadata associated with these measurements, is catalogued in the NeuroElectro Project \url{http://neuroelectro.org}.  
-Similarly, other SenseLab databases, including NeuronDB and CellPropDB (\cite{crasto_senselab:_2007},\url{http://senselab.med.yale.edu/NeuronDB/}), contain information on the ionic currents and neurotransmitters expressed by each neuron and how these are distributed with respect to neuronal morphology.
-Detailed information on ion channel subtypes, including voltage and temporal dynamics, genetic homology, and corresponding literature references is being compiled by Channelpedia (\cite{ranjan_channelpedia:_2011},\url{http://channelpedia.net/‎}), a subproject within the Blue Brain Project \citep{markram_blue_2006}.
+For example, information on the detailed shapes of neurons (i.e., their morphology) is being compiled by NeuroMorpho (\cite{neuromorpho_2007}, \url{http://neuromorpho.org}) which contains user-submitted neuron morphological reconstructions made using the NeuroLucida format \cite{glaser_neuron_1990}.
+Measured electrophysiological properties of neuron types, and the metadata associated with these measurements, is catalogued in the NeuroElectro Project (\cite{neuroelectro_2013}, \url{http://neuroelectro.org}).
+Similarly, other SenseLab databases, including NeuronDB and CellPropDB (\cite{crasto_senselab:_2007}, \url{http://senselab.med.yale.edu/NeuronDB}), contain information on the ionic currents and neurotransmitters expressed by each neuron and how these are distributed with respect to neuronal morphology.
+Detailed information on ion channel subtypes, including voltage and temporal dynamics, genetic homology, and corresponding literature references is being compiled by Channelpedia (\cite{ranjan_channelpedia:_2011}, \url{http://channelpedia.net}), a subproject within the Blue Brain Project \citep{markram_blue_2006}.
 
@@
 Similarly, the Allen Institute also provides information on the anatomical connectivity of different brain regions.
-Parallel to this effort is The Human Connectome Project (\url{http://www.humanconnectomeproject.org}), a large-scale effort to map complete structural and functional neural connections \textit{in vivo} in individual humans.
-BrainMap (\url{http://www.brainmap.org}) consists of a database and related software to search published functional and structural human neuroimaging experiments.  
-CoCoMac (\url{http://cocomac.g-node.org}), in contrast, is focused on the primate brain, containing records of tracing studies in the macaque. 
+Parallel to this effort is The Human Connectome Project (\cite{humanconnectomeproject_2013}, \url{http://www.humanconnectomeproject.org}), a large-scale effort to map complete structural and functional neural connections \textit{in vivo} in individual humans.
+BrainMap (\cite{brainmap_2005}, \url{http://www.brainmap.org}) consists of a database and related software to search published functional and structural human neuroimaging experiments.  
+CoCoMac (\cite{cocomac_2001,cocomac_2012}, \url{http://cocomac.g-node.org}), in contrast, is focused on the primate brain, containing records of tracing studies in the macaque. 
 The Brain Architecture Management System (BAMS, \cite{bota_brain_2005}, \url{http://brancusi1.usc.edu}) contains neural connectivity information across species that has been manually curated from the existing research literature.
-Finally, Cell Centered Database (\url{http://ccdb.ucsd.edu}) focuses on images from light and electron microscopy, ranging from whole brain areas to subcellular compartments.
+Finally, Cell Centered Database (\cite{cellcentered_2003,cellcentered_2009}, \url{http://ccdb.ucsd.edu}) focuses on images from light and electron microscopy, ranging from whole brain areas to subcellular compartments.
 
 In addition to these neuroscience domain-specific databases are uber-databases that provide linking facilities for cross-resource data integration. 
-For example, NeuroLex (\cite{larson_neurolex.org:_2013},\url{http://neurolex.org}), provides a platform for community annotation of neuron types on the basis of morphological, neurochemical, or electrophysiological properties.
+For example, NeuroLex (\cite{larson_neurolex.org:_2013}, \url{http://neurolex.org}), provides a platform for community annotation of neuron types on the basis of morphological, neurochemical, or electrophysiological properties.
 Given this wealth of neuroscience resources, the Neuroscience Information Framework (NIF, \cite{gardner_neuroscience_2008},\url{http://www.neuinfo.org}), provides tools for semantically searching across these diverse databases through the development and incorporation of neuroscience domain-specific ontologies \cite{bug_nifstd_2008,larson_ontologies_2009,hamilton_ontological_2012,imam_development_2012}.

### 2013-09-29 databases/neuroelectro_chapter.tex
Shreejoy edits

@@
 A subset of records have been manually validated against the primary literature.
-Neuron types are identified using the NeuroLex ontology (\cite{larson_neurolex.org:_2013}, \url{http://neurolex.org}); 
-Electrophysiological property types are identified using a custom ontology in the absence of standards.
+Neuron types are identified using the listing of neuron types provided by NeuroLex (\cite{larson_neurolex.org:_2013,hamilton_ontological_2012}, \url{http://neurolex.org});
+Electrophysiological property types are identified using a custom ontology which formalizes existing community standards \cite{ascoli_petilla_2008}.
 
-While NeuroElectro contains information about 27 distinct electrophysiological properties, those most heavily represented include resting membrane potential, input resistance, action potental height and width, etc.
+While NeuroElectro contains information about 27 distinct electrophysiological properties, those most heavily represented include resting membrane potential, input resistance, action potential height and width, etc.
 The list of journals containing the source information include those from the Elsevier, Highwire, Wiley, and Oxford family of journals, including The Journal of Neuroscience, The Journal of Physiology, and The Journal of Neurophysiology, among others.
-Neuroelectro also contains details on each study’s experimental conditions (like species or electrode type used), the so-called ``metadata", obtained using similar text extraction techniques applied to article methods sections.
+NeuroElectro also contains details on each study’s experimental conditions (like species or electrode type used), the so-called ``metadata'', obtained using similar text extraction techniques applied to article methods sections.
 
-The NeuroElectro web interface (\url{http://neuroelectro.org} also permits users to contribute to the database’s content. 
-For example, users can suggest relevant articles on a specific neuron type as well as validate content that has been extracted via our automated algorithms. 
-Furthermore, users can elect to become “content-experts” on a specific neuron type and can then modify the database’s content directly.
+The NeuroElectro web interface (\url{http://neuroelectro.org} also invites users to contribute to the database’s content.
+For example, users can suggest relevant articles on a specific neuron type as well as validate content that has been extracted via the automated algorithms.
+Furthermore, users can elect to become ``content-experts” on a specific neuron type and can then modify the database’s content directly.
 
 NeuroElectro also contains analyses of the resulting database yielding novel relationships on the electrophysiological similarity of different neuron types throughout the brain.
-Among these are hierarchical classifications of neuron types by similarity of electrophysiological properties.  
+Among these are hierarchical classifications of neuron types based on similarity of electrophysiological properties.
 The project maintainers are also aiming to relate gene expression patterns in specific cell types to those cells' electrophysiological properties, using expression data obtained through the Allen Brain Atlas (\cite{lein_genome-wide_2007}, \url{http://brain-map.org}).
@@
 \nobibliography{shreejoy}
-
 \end{document}

### 2013-09-29 NeurounitFrontiers/Paper.tex

@@
 \section{Introduction}
-Neuroscientists construct quantitative models to explain observations about neurons, circuits, and brains in a coherent and rigorous manner. 
-These models are characterized by their \textit{scope}: the set of observable quantities that the model can generate predictions about, and by their \textit{validity}, the extent to which these predictions agree with empirical observations of those quantities.
-As the quantity of models and empirical data in neuroscience proliferates, it is increasingly challenging to efficiently discover models whose scope is of interest and to then assess their validity against this mountain of data.
+Neuroscientists construct quantitative models to explain observations about neurons, circuits, brain regions and behavior in a coherent and rigorous manner. 
+These models are characterized by their \textit{scope}: the set of observable quantities that the model can generate predictions about, and by their \textit{validity}: the extent to which these predictions agree with empirical observations of those quantities.
+As the number of models and the volume of empirical data in neuroscience increases, it has become a challenge to efficiently and exhaustively discover models that relate to a system of interest and to comparatively assess their  validity against  growing mountains of data.
+This is because today, modelers contribute their results to the community by publishing the technical details of a new model along with a few selected demonstrations that they predict some observable quantities better than previous models do.
+Unfortunately, these demonstrations are necessarily incomplete, they naturally tend to serve the goals of authors rather than readers, they quickly go out of date and there is no easy way to summarize and compare the claims being made across modeling papers in order to synthesize an understanding of a research area as a whole.
+%Indeed, requiring exhaustive comparisons to all existing models and data would make publications encyclopedic and obscure their main points.
+Similarly, it is unrealistic to expect that publications containing new data exhaustively evaluate how they affect the validity of previously-developed models.
+A strength of publications are their focused descriptions of new data and models. 
+A weakness, however, is that evaluating the scope and validity of models against known data is intractable using a body of publications alone.
 
-Neuroscience models are traditionally described in publications. 
-Although authors may refer to some relevant experimental data and alternative models, these comparisons are incomplete and tend to serve the goals of authors rather than readers. 
-However, making exhaustive comparisons to existing models and data would make such publications encyclopedic and obscure their main points. 
-Thus, a strength of publication is its focused description of \textit{how} a model works and its conceptual advances. 
-A weakness, however, is that evaluating the scope and validity of a model is intractable using a publication alone. 
-This problem is exacerbated post-pubication as new data is rarely compared against existing models, and the original publication -- a resource of first resort for new scientists and onlookers -- is cited ``as-is'' in perpetuity.
-The validation of neuroscience models must be formalized to supplement the publication system and provide a straightforward way to determine how well models do what they claim to do.
+In professional software development, software is not validated simply by trying the program on a few example inputs at one point in its development.
+Instead, developers often follow a \emph{test-driven development} process by creating a suite of \emph{unit tests} that collectively validate the functionality of a program as it is being developed and modified.
+Each test is responsible for verifying that a small portion of the program meets a single correctness criterion.
+For example, a unit test might verify that one function within the program correctly handles malformed inputs.
+Collectively, these tests serve as a summary of the validity of the software as it progresses through its development cycle.
+Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many more tests pass after a given period of time.
+This methodology has been highly successful in practice \cite{tdd}\todo{cite tdd}.
 
-Modeling competitions in neuroscience have resulted in important advances. 
-For example, the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} addressed the complexity-accuracy tradeoff among reduced models of excitable membranes; 
+%publications would be analagous to user manuals, rather than rigorous justifications that a program meets a specific specification.
+Unit tests serve this purpose for software, so we argue that the validation of neuroscience models by means of executable tests would be useful to scientists as a supplement the publication system.
+
+\todo{paragraph transitioning between the previous one and this one???}Test-driven methodologies have started to see success in science as well.
+Modeling competitions in neuroscience, for example, are typically structured around a collection of simple validation criteria, and these competitions continue to produce important advances and improve scientists' understanding of the state-of-the-art in their research areas.
+The quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} addressed the complexity-accuracy tradeoff among reduced models of excitable membranes; 
 the ``Hopfield'' challenge\cite{hopfield_what_2000} asked for neuronal network form, given function; 
-the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity\cite{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction\cite{diadem_url};
-examples from other subfields of biology abound\cite{dream_url}.
+the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity\cite{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction\cite{diadem_url}; and
+examples from other subfields of biology also abound\cite{dream_url}.
 
-\begin{wrapfigure}{r}{0.6\textwidth}
-\vspace{-38px}
+\begin{figure}%{r}{0.6\textwidth}
+%\vspace{-38px}
 \includegraphics[scale=0.75]{sciunit_overview.pdf}
@@
 \textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
-\vspace{-10px}
+%\vspace{-10px}
 \label{fig:sciunit_overview}
-\end{wrapfigure}
+\end{figure}
 \leavevmode
 \vspace{-0px}
-Recognizing that neuroscience contains a wide variety of models that aim to explain phenomena at multiple levels, we leveraged a discipline-agnostic Python framework called \textit{SciUnit}\cite{sciunit_url} to create tools for testing neuroscience models and associated tests.
-The result is \textit{NeuroUnit}, which extends \textit{SciUnit} into neuroscience by supporting the testing of models described using \textit{NeuroML}, the construction of test logic using \textit{NeuroTools} \cite{neurotools_url}, and employing a test ``answer key" using electrophysiology data from the \textit{NeuroElectro Project} \cite{neuroelectro_url}.
-In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
+Each of these examples leveraged \emph{ad hoc} infrastructure.
+Although the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that can be implemented once.
+Recognizing this, we have developed a discipline-agnostic framework for developing scientific model validation test suites called \textit{SciUnit}\cite{sciunit_url}.
+To demonstrate the power of this framework in combination with existing neuroinformatics tools, we developed \textit{NeuronUnit\-}, which allows scientists to build \textit{SciUnit} tests that validate neural models described using the  \text{NeuroML} modeling standard against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}.% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
 

### 2013-10-22 NeurounitFrontiers/Paper.tex
Added acknowledgements

@@
 Recognizing this, we have developed a discipline-agnostic framework for developing scientific model validation test suites called \textit{SciUnit}\cite{sciunit_url}.
-To demonstrate the power of this framework in combination with existing neuroinformatics tools, we developed \textit{NeuronUnit\-}, which allows scientists to build \textit{SciUnit} tests that validate neural models described using the  \text{NeuroML} modeling standard against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}.% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
+To demonstrate the power of this framework in combination with existing neuroinformatics tools, we developed \textit{NeuronUnit\-}, which allows scientists to build \textit{SciUnit} tests that validate neural models described using the  \text{NeuroML} modeling standard against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}.\todo{This is what NeuronUnit can do now, but it is not in principle limited to this.
+I would rather have this pipeline be described in the results as one thing that is fully implemented, but not limit ourselves to this in the introduciton.}% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
 
@@
 
+\section{Acknowledgements}
+This work was supported in part by grant R01MH081905 from the National Institute of Mental Health.
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
+
 \bibliographystyle{unsrt}

### 2013-10-31 NeurounitFrontiers/Paper.tex
Updated abstract

--- 2013-09-29 NeurounitFrontiers/Paper.tex
@@
 Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
-However, model validation remains an informal and incomplete process, especially in fields, like neuroscience, where the available data is growing rapidly.   
-This makes it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models to determine the state-of-the-art, and to precisely identify open modeling problems.
+However, model validation remains an informal and incomplete process, especially in fields like neuroscience where the available data is growing rapidly.   
+This makes it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.
 
@@
 Suites of such validation tests are used as a summary of modeling progress within a scientific community.
-Using this framework, we develop \textit{NeuroUnit}, a library that aids validation testing in neuroscience\todo{neurophys specifically?}.
+Building on this framework, we develop \textit{NeuronUnit}, a library that supports validation testing for neurophysiology\todo{is this accurate?}.
 

### 2013-10-31 NeurounitFrontiers/Paper.tex
Updated introduction

@@
 However, model validation remains an informal and incomplete process, especially in fields like neuroscience where the available data is growing rapidly.   
-This makes it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.
+This has made it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.
 
@@
 \section{Introduction}
-Neuroscientists construct quantitative models to explain observations about neurons, circuits, brain regions and behavior in a coherent and rigorous manner. 
-These models are characterized by their \textit{scope}: the set of observable quantities that the model can generate predictions about, and by their \textit{validity}: the extent to which these predictions agree with empirical observations of those quantities.
-As the number of models and the volume of empirical data in neuroscience increases, it has become a challenge to efficiently and exhaustively discover models that relate to a system of interest and to comparatively assess their  validity against  growing mountains of data.
-This is because today, modelers contribute their results to the community by publishing the technical details of a new model along with a few selected demonstrations that they predict some observable quantities better than previous models do.
-Unfortunately, these demonstrations are necessarily incomplete, they naturally tend to serve the goals of authors rather than readers, they quickly go out of date and there is no easy way to summarize and compare the claims being made across modeling papers in order to synthesize an understanding of a research area as a whole.
-%Indeed, requiring exhaustive comparisons to all existing models and data would make publications encyclopedic and obscure their main points.
-Similarly, it is unrealistic to expect that publications containing new data exhaustively evaluate how they affect the validity of previously-developed models.
-A strength of publications are their focused descriptions of new data and models. 
-A weakness, however, is that evaluating the scope and validity of models against known data is intractable using a body of publications alone.
+Neuroscientists construct quantitative models to coherently explain a body of observations about neurons, circuits, brain regions and behavior. 
+These models can be characterized by their \textit{scope}: the set of observable quantities that the model can generate predictions about, and by their \textit{validity}: the extent to which these predictions agree with empirical observations of those quantities.
 
-In professional software development, software is not validated simply by trying the program on a few example inputs at one point in its development.
-Instead, developers often follow a \emph{test-driven development} process by creating a suite of \emph{unit tests} that collectively validate the functionality of a program as it is being developed and modified.
-Each test is responsible for verifying that a small portion of the program meets a single correctness criterion.
+Today, modelers contribute a new model to the research community by submitting a paper describing how it works, along with selected figures demonstrating its scope and validity and comparing its validity to other models with the same scope.
+Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, relying on their knowledge of the publication history of the field.
+Unfortunately, in many research areas, the volume of research being published every year is outpacing the abilities of even the most SOMETHING \todo{need good adjective} scientists \todo{citation/stats?}.
+
+%This suggests that tools that help researchers answer questions like these could help readers and reviewers develop a more comprehensive understanding of the state-of-the-art and improve the quality of the research being published as a result: to renewed calls for tools that help researchers .
+
+Readers, like reviewers, face similar challenges when attempting to answer fundamental questions like these, given the enormity of the publication history in many fields:
+\begin{itemize}
+\item Which models are capable of predicting the quantities I am interested in?
+\item Which metrics should be used to evaluate the goodness-of-fit between these models and  data?
+\item How well do these models perform, according to these metrics?
+\item What other quantities can these models predict?
+\item What observations are not adequately explained by available models?
+\end{itemize}
+
+%These questions are particularly relevant for young scientists and  scientists aiming to enter a new research area to answer.
+
+%understanding of the state-of-the-art from publications containing only a few pieces of data, and then only that data available at the time of publication.
+
+%These demonstrations also quickly go out of date.
+Finally, there is no easy way to summarize and compare the claims being made in modeling papers in order to synthesize an understanding of a research area as a whole.
+%A strength of publications are their focused descriptions of new data and models. 
+%A weakness, however, is that evaluating the scope and validity of models against known data is intractable using a body of publications alone.
+
+In professional software development, complex programs are not validated by simply choosing a few interesting inputs and presenting the outputs of the program on these inputs to reviewers.
+Instead, developers typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively validate the functionality of a program as it is being developed and modified.
+Each test is responsible for checking that a small portion of the program meets a single correctness criterion.
 For example, a unit test might verify that one function within the program correctly handles malformed inputs.
-Collectively, these tests serve as a summary of the validity of the software as it progresses through its development cycle.
-Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many more tests pass after a given period of time.
-This methodology has been highly successful in practice \cite{tdd}\todo{cite tdd}.
+Collectively, the test results serve as summary of the validity of the software as it progresses through its development cycle.
+Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time.
+This methodology is widely adopted and has been highly successful in practice \cite{tdd}\todo{cite tdd}.
 

### 2013-11-01 NeurounitFrontiers/Paper.tex
further progress

--- 2013-10-31 NeurounitFrontiers/Paper.tex
@@
 \section{Introduction}
-Neuroscientists construct quantitative models to coherently explain a body of observations about neurons, circuits, brain regions and behavior. 
+Neuroscientists construct quantitative models to coherently explain observations of neurons, circuits, brain regions and behavior. 
 These models can be characterized by their \textit{scope}: the set of observable quantities that the model can generate predictions about, and by their \textit{validity}: the extent to which these predictions agree with empirical observations of those quantities.
 
-Today, modelers contribute a new model to the research community by submitting a paper describing how it works, along with selected figures demonstrating its scope and validity and comparing its validity to other models with the same scope.
-Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, relying on their knowledge of the publication history of the field.
-Unfortunately, in many research areas, the volume of research being published every year is outpacing the abilities of even the most SOMETHING \todo{need good adjective} scientists \todo{citation/stats?}.
+Today, scientists contribute a new model to the research community by submitting a paper describing how the model works, along with selected figures demonstrating its scope and validity and comparing its validity to other models with the same scope.
+Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, drawing on their knowledge of prior publications.
+Unfortunately, in many areas, the number of publications being generated every year can overwhelm  even the most conscientious  scientists \todo{citation/stats?}.
 
@@
 
-Readers, like reviewers, face similar challenges when attempting to answer fundamental questions like these, given the enormity of the publication history in many fields:
+Unfortunately, there are few alternatives to a comprehensive literature review available when scientists need to answer questions like these:
 \begin{itemize}
@@
 \item Which metrics should be used to evaluate the goodness-of-fit between these models and  data?
-\item How well do these models perform, according to these metrics?
-\item What other quantities can these models predict?
-\item What observations are not adequately explained by available models?
+\item How well do these models perform, as judged to these metrics, given currently available data?
+\item What other quantities can and can't these models predict?
+\item What observations are not adequately explained by any available model?
 \end{itemize}
@@
 
-In professional software development, complex programs are not validated by simply choosing a few interesting inputs and presenting the outputs of the program on these inputs to reviewers.
-Instead, developers typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively validate the functionality of a program as it is being developed and modified.
-Each test is responsible for checking that a small portion of the program meets a single correctness criterion.
+Professional software developers face similar issues.
+They must understand the scope of each component of a software project and validate it by measuring how well each component achieves its stated goals.
+But software developers do not validate components by simply choosing a few interesting inputs and presenting the outputs to reviewers.
+Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively specify the scope of each component and validate the functionality of its implementation as it is being developed and modified.
+Each test individually checks that a small portion of the program meets a single correctness criterion.
 For example, a unit test might verify that one function within the program correctly handles malformed inputs.
-Collectively, the test results serve as summary of the validity of the software as it progresses through its development cycle.
+Collectively, the test results serve as a summary of the validity of the project as it progresses through its development cycle.
 Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time.
-This methodology is widely adopted and has been highly successful in practice \cite{tdd}\todo{cite tdd}.
+This methodology is widely adopted in practice \cite{tdd}\todo{cite tdd}.
 
@@
 
-\todo{paragraph transitioning between the previous one and this one???}Test-driven methodologies have started to see success in science as well.
-Modeling competitions in neuroscience, for example, are typically structured around a collection of simple validation criteria, and these competitions continue to produce important advances and improve scientists' understanding of the state-of-the-art in their research areas.
-The quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} addressed the complexity-accuracy tradeoff among reduced models of excitable membranes; 
-the ``Hopfield'' challenge\cite{hopfield_what_2000} asked for neuronal network form, given function; 
+Test-driven methodologies have started to see success in science as well.
+Modeling competitions in neuroscience, for example, are typically organized around a collection of simple validation criteria, implemented as executable tests.
+These competitions continue to drive important advances and improve scientists' understanding of the relative merits of different models.
+For example,
+the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
+the ``Hopfield'' challenge\cite{hopfield_what_2000} tested techniques for generating neuronal network form given its function; 
 the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity\cite{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction\cite{diadem_url}; and
-examples from other subfields of biology also abound\cite{dream_url}.
+examples from other subfields of biology abound\cite{dream_url}.
 
-\begin{figure}%{r}{0.6\textwidth}
-%\vspace{-38px}
-\includegraphics[scale=0.75]{sciunit_overview.pdf}
-\caption{Proposal overview. 
-\small{i) The \textit{SciUnit} framework can generate discipline-specific libraries for tests generation and model interfacing.  
-\textit{NeuronUnit} is proposed and described here.  Experimental data guides test development; model generation informs and is informed by these \textit{SciUnit} libraries.  
-Each \text{SciUnit} test suite repository on GitHub is indexed by the \textit{SciDash} web application.  
-Test suites for OSB and QSNMC (described in the text) are being built. 
-\textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
-%\vspace{-10px}
+% \begin{figure}%{r}{0.6\textwidth}
+% %\vspace{-38px}
+% \includegraphics[scale=0.75]{sciunit_overview.pdf}
+% \caption{Proposal overview. 
+% \small{i) The \textit{SciUnit} framework can generate discipline-specific libraries for tests generation and model interfacing.  
+% \textit{NeuronUnit} is proposed and described here.  Experimental data guides test development; model generation informs and is informed by these \textit{SciUnit} libraries.  
+% Each \text{SciUnit} test suite repository on GitHub is indexed by the \textit{SciDash} web application.  
+% Test suites for OSB and QSNMC (described in the text) are being built. 
+% \textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
+% %\vspace{-10px}
+% \label{fig:sciunit_overview}
+% \end{figure}
+% \leavevmode
+% \vspace{-0px}
+\begin{figure}
+\vspace{-38px}
+\includegraphics[scale=0.5]{diagram1.pdf}
+\vspace{-25px}
+\caption{Paper overview.}
 \label{fig:sciunit_overview}
@@
 \vspace{-0px}
-Each of these examples leveraged \emph{ad hoc} infrastructure.
-Although the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that can be implemented once.
-Recognizing this, we have developed a discipline-agnostic framework for developing scientific model validation test suites called \textit{SciUnit}\cite{sciunit_url}.
-To demonstrate the power of this framework in combination with existing neuroinformatics tools, we developed \textit{NeuronUnit\-}, which allows scientists to build \textit{SciUnit} tests that validate neural models described using the  \text{NeuroML} modeling standard against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}.% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
+
+Each of these examples has leveraged \emph{ad hoc} infrastructure to support test generation.
+While the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that could be implemented once.
+Recognizing this, we have developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit}\cite{sciunit_url}.
+To demonstrate the power of this framework and show how it can be used to bridge several existing neuroinformatics tools, we then  developed \textit{NeuronUnit\-}.
+This library allows scientists to build \textit{SciUnit} tests that validate \text{NeuroML}  models against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}\todo{refer to and describe figure 1}.% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
 
 % Section 2.
-\section{Implementation of Testing}
-
+\section{Validation Testing with \textit{SciUnit}}
+\subsection{Example: Quantitative Single Neuron Modeling Competition}
 \begin{figure}
@@
     return sciunit.PValue(pooled_p, related_data={
-      "inputs": input_current,
-      "obs_means": means,
-      "obs_stds": stds
+      "inputs": inputs, "counts": counts, "obs_means": means, "obs_stds": stds
     })
@@
 \vspace{-5px}
-\caption{A single neuron spike count test family implemented in \textit{SciUnit}}
+\caption{A single neuron spike count test family implemented using \textit{SciUnit}.
+This family contains logic common to many different domains, so it is distributed in the \textit{NeuronUnit} repository (see Sec.
+\ref{sec:neuronunit}).}
 \label{fig:rate_test}
@@
 
-Simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.
-We begin by describing abstractly the outlines of a test suite related to single-neuron neurophysiology.
-Suppose that the tests in this suite are designed for experiments where stimuli are delivered to neurons as somatically injected current (in pA), while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
+%Simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.  
+We begin by constructing an example validation test suite. 
+Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons in some brain region, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
 A model claiming to capture this cell type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.
 
-One simple validation test would ask candidate models to predict the number of action potentials generated in response to a series of stimuli, and compare these \emph{spike count} predictions to the distribution observed in repeated experimental trials with the same stimuli.
-The test creator is responsible for specifying how to measure the goodness-of-fit; 
-for example, a p-value derived from a chi-squared statistic could be calculated for each prediction and then these p-values could be combined using Fisher's method\cite{fisher_statistical_1925}.
+One simple validation test would ask candidate models to predict the number of action potentials generated in response to a stimulus (e.g.
+white noise), and compare these \emph{spike count} predictions to the distribution observed in repeated experimental trials with the same stimulus.
+Goodness-of-fit can be measured in different ways.
+Each test makes a choice about  how goodness-of-fit is measured.
+In our example, we will calculate a p-value derived from a chi-squared statistic for each prediction and then combine these p-values using Fisher's method\cite{fisher_statistical_1925}.
+Importantly, the validation criteria is made explicit by the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model.
+Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative tests.
+A community consensus will emerge in the form a common test suite (see Sec.
+\ref{sec:scidash}).
 
@@
 
-Importantly, the validation criteria in each case are made explicit by the specification of a test suite, so modelers need not guess which criteria are being used to validate or invalidate their model.
-Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative test suites.
-In many cases, models require no modifications to take the new tests because the same type of model output is being requested.
-
+%In many cases, models require no modifications to take the new tests because the same type of model output is being requested.
+\subsection{Implementing a Validation Test in \textit{SciUnit}}
 Fig. \ref{fig:rate_test} shows how a scientist would implement the spike count test described above using \textit{SciUnit}. 
 A \textit{SciUnit} validation test is an {instance} of a Python class implementing the \verbx{sciunit.Test} interface. 
-Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor; the parameters' meaning is documented on lines 5-8). 
-For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
+Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor.
+The meaning of each parameter along with the goodness-of-fit metric used by the test is documented on lines 5-8.
+%For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
 To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
@@
 \end{python}
-We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test.
+We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the parameters above, derived from data, have been provided.
 As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often consist simply of instantiating a previously-developed family with particular experimental parameters and data.
-For single-neuron tests like the \verbx{SpikeCountTest}, we have developed a library \cite{neurounit_url} to facilitate development (Sec. \ref{sec:neuronunit}).
+For single-neuron test families like \verbx{SpikeCountTest}, we have developed a library called \textit{NeuronUnit} \cite{neurounit_url} (Sec. \ref{sec:neuronunit}).
 
 Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{run_test} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
-To specify the interface between the test and the model (that is, to constrain the test's scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
+To specify the interface between the test and the model (that is, to specify what must be in a model's scope for it to be eligible to even take the test), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
 \ref{fig:rate_test}.
@@
 The capability required by the test in Fig. \ref{fig:rate_test} (used on line 19) is shown in Fig. \ref{fig:capability}. 
-In \textit{SciUnit}, classes defining capabilities be tagged by inheriting from \verbx{sciunit.Capability}, and discovered automatically (Figs. \ref{fig:capability},\ref{fig:training}).
+In \textit{SciUnit}, classes defining capabilities are tagged as such by inheriting from \verbx{sciunit.Capability}.
+The test in Figure \ref{fig:rate_test} uses this capability on line 19 to produce a spike count prediction.
+The remainder of the \verbx{run_test} method implements the goodness-of-fit test described above, returning an instance of \verbx{sciunit.PValue} which is a subclass of \verbx{sciunit.Score}.
+In addition to the score itself, the returned score object also contains metadata of use to those wishing to examine the result in detail.
+In this case we saved the inputs, model outputs and observed means and standard deviations alongside the score by using the \verbx{related_data} parameter. 
+We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.
 
@@
 \end{figure}
-
-In the test in Fig.
-\ref{fig:rate_test}, the \verbx{run_test} method simply calls the \verbx{spike_count_from_current} capability method to produce spike count predictions for each input current on line 18.
-There are many possibly statistical choices for deriving a test score.  
-In the figure, the resulting spike count is compared to the empirical mean to produce a chi-squared statistic, and ultimately a p-value. 
-Alternatively, the array of standard deviations (line 10) could be used to derive a Z-score.  
-In addition to the score itself, the returned score object also contains metadata of use to those wishing to examine the result in detail. 
-In this test we saved the inputs and observed means and standard deviations alongside the score by using the \verbx{related_data} parameter. 
-We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.
 

### 2013-11-01 NeurounitFrontiers/Paper.tex
Updated acknowledgements

@@
 
+\section{Acknowledgements}
+We thank Sharon Crook, Jonathan Aldrich, Shreejoy Tripathy, and Padraig Gleeson for their support of this project.  
+The work was supported in part by grant R01MH081905 from the National Institute of Mental Health. 
+The content is solely the responsibility of the authors and does not necessarily represent the official views of the National Institutes of Health.
+
 \bibliographystyle{unsrt}

### 2013-11-02 NeurounitFrontiers/Paper.tex
UPdated through 3.2

@@
 \vspace{-38px}
-\includegraphics[scale=0.5]{diagram1.pdf}
-\vspace{-25px}
+\centering
+\includegraphics[scale=0.6]{diagram1.pdf}
+\vspace{-55px}
 \caption{Paper overview.}
@@
 To demonstrate the power of this framework and show how it can be used to bridge several existing neuroinformatics tools, we then  developed \textit{NeuronUnit\-}.
-This library allows scientists to build \textit{SciUnit} tests that validate \text{NeuroML}  models against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}\todo{refer to and describe figure 1}.% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
+This library allows scientists to build \textit{SciUnit} tests that validate \text{NeuroML}  models against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}\todo{refer to and describe figure 1}\todo{add caption to figure 1}.% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
 
@@
 class SpikeCountTest(sciunit.Test):
-  """Tests models that generates spike counts from currents. Computes p-values based on a chi-squared test statistic, and pools them using Fisher's method.
+  """Tests spike counts produced in response to several current stimuli against observed means and standard deviations.
 
+  goodness of fit metric: Computes p-values based on a chi-squared test statistic, and pools them using Fisher's method.
   parameters:
     inputs: list of numpy arrays containing input currents (nA)
-    means, stds: list of means and standard deviations of the 
-      spike counts observed in response to the inputs
+    means, stds: lists of observed means and standard deviations, one per input
   """
@@
 \caption{A single neuron spike count test family implemented using \textit{SciUnit}.
-This family contains logic common to many different domains, so it is distributed in the \textit{NeuronUnit} repository (see Sec.
+This family contains logic common to many different systems, so it is distributed in the \textit{NeuronUnit} repository (see Sec.
 \ref{sec:neuronunit}).}
@@
 
-One simple validation test would ask candidate models to predict the number of action potentials generated in response to a stimulus (e.g.
-white noise), and compare these \emph{spike count} predictions to the distribution observed in repeated experimental trials with the same stimulus.
-Goodness-of-fit can be measured in different ways.
-Each test makes a choice about  how goodness-of-fit is measured.
-In our example, we will calculate a p-value derived from a chi-squared statistic for each prediction and then combine these p-values using Fisher's method\cite{fisher_statistical_1925}.
-Importantly, the validation criteria is made explicit by the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model.
-Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative tests.
-A community consensus will emerge in the form a common test suite (see Sec.
-\ref{sec:scidash}).
+One simple validation test would ask candidate models to predict the number of action potentials (a.k.a.
+spikes) generated in response to a stimulus (e.g.
+white noise), and compare these \emph{spike count} predictions to the distribution observed in repeated experimental trials using the same stimulus.
+In our example, we will determine goodness-of-fit by first calculating a p-value from a chi-squared statistic for each prediction and then combining these p-values using Fisher's method\cite{fisher_statistical_1925}.
 
-Alongside this \emph{spike count test}, a number of other tests capturing different features of the data could be specified to produce a more comprehensive suite. 
+Alongside this \emph{spike count test}, a number of other tests capturing different features of the data can be specified to produce a more comprehensive suite. 
 For data of this sort, the QSNMC defined 17 other validation criteria in addition to one based on the overall spike count, capturing features like spike latencies (SL), mean subthreshold voltage (SV), interspike intervals (ISI) and interspike minima (ISM) that can be extracted from the data\cite{jolivet_quantitative_2008}.
@@
 \subsection{Implementing a Validation Test in \textit{SciUnit}}
-Fig. \ref{fig:rate_test} shows how a scientist would implement the spike count test described above using \textit{SciUnit}. 
-A \textit{SciUnit} validation test is an {instance} of a Python class implementing the \verbx{sciunit.Test} interface. 
-Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor.
-The meaning of each parameter along with the goodness-of-fit metric used by the test is documented on lines 5-8.
+Fig. \ref{fig:rate_test} shows how a scientist would implement spike count tests such as the one described above using \textit{SciUnit}. 
+A \textit{SciUnit} validation test is an {instance} (i.e. an object) of a Python class implementing the \verbx{sciunit.Test} interface (cf. line 1). 
+Here, we show a class \verbx{SpikeCountTest} taking three \emph{parameters} in its constructor (constructors are named \verbx{__init__} in Python, lines 9-10).
+The meaning of each parameter along with a description of the goodness-of-fit metric used by the test is documented on lines 4-7.
 %For convenience, we also make use of functions provided by the popular NumPy\cite{numpy_url} and SciPy\cite{scipy_url} libraries, although these are not required by \textit{SciUnit}.  
@@
 \end{python}
-We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the parameters above, derived from data, have been provided.
-As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often consist simply of instantiating a previously-developed family with particular experimental parameters and data.
-For single-neuron test families like \verbx{SpikeCountTest}, we have developed a library called \textit{NeuronUnit} \cite{neurounit_url} (Sec. \ref{sec:neuronunit}).
+We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided.
+As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data.
+For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} \cite{neurounit_url} (Sec. \ref{sec:neuronunit}).
 
 Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{run_test} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
-To specify the interface between the test and the model (that is, to specify what must be in a model's scope for it to be eligible to even take the test), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
+To specify the interface between the test and the model (that is, to specify an appropriate scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
 \ref{fig:rate_test}.
@@
 In Python, they are written as classes with unimplemented members. 
-The capability required by the test in Fig. \ref{fig:rate_test} (used on line 19) is shown in Fig. \ref{fig:capability}. 
+The capability required by the test in Fig. \ref{fig:rate_test} is shown in Fig. \ref{fig:capability}. 
 In \textit{SciUnit}, classes defining capabilities are tagged as such by inheriting from \verbx{sciunit.Capability}.
-The test in Figure \ref{fig:rate_test} uses this capability on line 19 to produce a spike count prediction.
-The remainder of the \verbx{run_test} method implements the goodness-of-fit test described above, returning an instance of \verbx{sciunit.PValue} which is a subclass of \verbx{sciunit.Score}.
-In addition to the score itself, the returned score object also contains metadata of use to those wishing to examine the result in detail.
-In this case we saved the inputs, model outputs and observed means and standard deviations alongside the score by using the \verbx{related_data} parameter. 
-We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.
+The test in Figure \ref{fig:rate_test} uses this capability on line 19 to produce a spike count prediction for each input current.
+
+The remainder of the \verbx{run_test} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.PValue}, a subclass of \verbx{sciunit.Score} included with \textit{SciUnit}.
+In addition to the score itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for  those who may wish to examine the result in more detail.
+In this case we save the input currents, the model outputs and the observed means and standard deviations alongside the score (line 24). 
+%We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.
 
@@
 
+\subsection{Models}
 Capabilities are \emph{implemented} by models.
-A simple \emph{family} of models implementing this capability is shown in Fig. \ref{fig:simple_model}. 
-Models in this family produce a spike count by applying a linear transformation to the mean of the provided input current. 
+In \textit{SciUnit}, models are instances of Python classes that inherit from \verbx{sciunit.Model}.
+Like tests, the class itself represents a family of models, parameterized by the arguments needed in the constructor.
+A particular model is an object created by supplying the parameters.
+
+A simple {family} of models, \verb{LinearModel}, implementing the capability in Fig.
+\ref{fig:capability} as well as another capability shown in Fig.
+\ref{fig:training}, is shown in Fig.
+\ref{fig:simple_model}.
+Models in this family, \verbx{LinearModel}, produce a spike count by applying a linear transformation to the mean of the provided input current. 
 The family is parameterized by a scale factor and offset, both scalars. 
@@
 \section{Discussion}
+The validation criteria is made explicit in the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model. 
+Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative tests.
+A community consensus will slowly emerge in the form a commonly-accepted test suite (see Sec.
+\ref{sec:scidash}).
+\todo{integrate this somewhere down here}
 

### 2013-11-02 NeurounitFrontiers/Paper.tex
Addressed to do items

@@
 Suites of such validation tests are used as a summary of modeling progress within a scientific community.
-Building on this framework, we develop \textit{NeuronUnit}, a library that supports validation testing for neurophysiology\todo{is this accurate?}.
+Building on this framework, we develop \textit{NeuronUnit}, a library that supports validation testing for neurophysiology.
 
@@
 Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, drawing on their knowledge of prior publications. 
-Unfortunately, in many areas, the number of publications being generated every year can overwhelm  even the most conscientious  scientists \todo{citation/stats?}.
+Unfortunately, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists\cite{jinha_article_2010}.
 
@@
 Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
-This methodology is widely adopted in practice \cite{tdd}\todo{cite tdd}.
+This methodology is widely adopted in practice\cite{beck2003}.
 
@@
 These competitions continue to drive important advances and improve scientists' understanding of the relative merits of different models. 
-For example,
-the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
+For example, the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
 the ``Hopfield'' challenge\cite{hopfield_what_2000} tested techniques for generating neuronal network form given its function; 
@@
 examples from other subfields of biology abound\cite{dream_url}.
-
 % \begin{figure}%{r}{0.6\textwidth}
@@
 \vspace{-55px}
-\caption{Paper overview.}
+\caption{NeuronUnit overview.
+NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework.
+NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project \cite{osb_url}, and single neuron electrophysiology data available as part of the NeuroElectro Project \cite{neuroelectro_url}.
+Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}
 \label{fig:sciunit_overview}
@@
 To demonstrate the power of this framework and show how it can be used to bridge several existing neuroinformatics tools, we then developed \textit{NeuronUnit\-}. 
-This library allows scientists to build \textit{SciUnit} tests that validate \text{NeuroML}  models against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} project to..\todo{what does NeuroTools do?}\todo{refer to and describe figure 1}\todo{add caption to figure 1}.% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
+This library allows scientists to build \textit{SciUnit} tests that validate \text{NeuroML} models against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.
+This is summarized in Figure \ref{fig:sciunit_overview}, which shows the relationships between the layers described here.
+% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
 
@@
 
-A simple {family} of models, \verb{LinearModel}, implementing the capability in Fig.
+A simple \emph{family} of models, \verbx{LinearModel}, implementing the capability in Fig.
 \ref{fig:capability} as well as another capability shown in Fig.
@@
 
-\begin{wrapfigure}[18]{r}{0.45\textwidth}
-\center
-\vspace{-10px}
-\includegraphics[scale=0.72]{scidash_github.png}
-\caption{A \textit{SciDash} repository on GitHub}
-\label{fig:scidash_repo}
-\end{wrapfigure}
-\vspace{-10px}
-\leavevmode
-
 \textit{SciDash} exists in three layers.
@@
 Each record links to test records (stored in the repository), displaying line-by-line the executed code and intermediate output statements, as well as the underlying models and tests.
+
+\begin{wrapfigure}[18]{r}{0.45\textwidth}
+\center
+\vspace{-10px}
+\includegraphics[scale=0.72]{scidash_github.png}
+\caption{A \textit{SciDash} repository on GitHub}
+\label{fig:scidash_repo}
+\end{wrapfigure}
+\vspace{-10px}
+\leavevmode
 
@@
 \section{Discussion}
-The validation criteria is made explicit in the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model. 
-Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative tests.
-A community consensus will slowly emerge in the form a commonly-accepted test suite (see Sec.
-\ref{sec:scidash}).
-\todo{integrate this somewhere down here}
 
@@
 identification and correction of flawed methodology is becoming increasingly common\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010,fish_fmri_url}, and is accelerated by an open framework.
-The community can judge which test version is most appropriate, i.e.
+The validation criteria is made explicit in the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model. 
+Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative tests.
+A community consensus will slowly emerge in the form a commonly-accepted test suite (see Sec. \ref{sec:scidash}). 
+This community can judge which test version is most appropriate, i.e.
 what a model \textit{should} do -- this process documented via standard moderation techiniques used on GitHub -- and the \textit{SciUnit} framework determines whether the model \textit{does} it.

### 2013-11-02 NeurounitFrontiers/Paper.tex
Updated thru sec 3

--- 2013-11-02 NeurounitFrontiers/Paper.tex
@@
 
-  def run_test(self, model):
+  def _judge(self, model):
     inputs, means, stds = self.inputs, self.means, self.stds
@@
 To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
-For example, given observations from hippocampal CA1 cells (not shown), we can instantiate a test as follows:
+For example, given observations from hippocampal CA1 cells (not shown), we can instantiate a test as follows\todo{use iPython style In[0] notation?}:
 \begin{python}
@@
 
-Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{run_test} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
+Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{_judge} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
 To specify the interface between the test and the model (that is, to specify an appropriate scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
@@
 In \textit{SciUnit}, models are instances of Python classes that inherit from \verbx{sciunit.Model}.
-Like tests, the class itself represents a family of models, parameterized by the arguments needed in the constructor.
-A particular model is an object created by supplying the parameters.
+Like tests, the class itself represents a family of models, parameterized by the arguments of the constructor.
+A particular model is an instance of such a class.
 
-A simple {family} of models, \verb{LinearModel}, implementing the capability in Fig.
+Figure \ref{fig:simple_model} shows how to write a simple {family} of models, \verbx{LinearModel}, that implement the capability in Fig.
 \ref{fig:capability} as well as another capability shown in Fig.
-\ref{fig:training}, is shown in Fig.
-\ref{fig:simple_model}.
-Models in this family, \verbx{LinearModel}, produce a spike count by applying a linear transformation to the mean of the provided input current. 
-The family is parameterized by a scale factor and offset, both scalars. 
-To create a \emph{particular} model, the modeler may choose particular parameter values, just as with test families:
+\ref{fig:training}, discussed below.
+Models in this family generate a spike count by applying a linear transformation to the mean of the provided input current.
+The family is parameterized by the scale factor and the offset of the transformation, both scalars.
+To create a \emph{particular} linear model, a modeler can provide particular parameter values, just as with test families:
 \begin{python}
@@
 Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
-An alternative test design to the one in Fig. \ref{fig:rate_test} would add a second required capability (Fig. \ref{fig:training}) and a corresponding training phase to the \verb|run_test| method. 
-This design would be relevant only for those models for which parameters can be adjusted without human involvement. 
+An alternative test design would add a training phase where these parameters were fit to data using the capability shown in Fig. \ref{fig:training}. 
+This test could thus only be used for those models for which parameters can be adjusted without human involvement. 
 Whether to build a training phase into the test protocol is a choice left to each modeler. 
-Although Fig.
-\ref{fig:rate_test} does not include a training phase, if training data is available then models that nevertheless implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
+For example, Fig. \ref{fig:rate_test} does not include a training phase.
+
+If training data is externally available, then models that nevertheless do implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
 \begin{python}
@@
 \end{python}
-\caption{A simple model that returns a spike count by scaling the mean of the input by a fixed parameter.}
+\caption{A model that returns a spike count by applying a linear transformation to the mean input current.
+The parameters can be provided manually or learned from data provided by a test or user (see text).}
 \label{fig:simple_model}
@@
 
-Finally, a test is executed against a model instance, using the \verbx{sciunit.judge} function:
+\subsection{Executing Tests} A test is executed against a model using the \verbx{judge} method:
 \begin{python}
-score = sciunit.judge(CA1_sc_test, CA1_linear_model_heuristic)
+score = CA1_sc_test.judge(CA1_linear_model_heuristic)
 \end{python}
 
-Collection of tests with mutually coherent requirments, i.e. various summaries of the available empirical data, can form test suites.
+This method proceeds by first checking that the provided model implements all required capabilities.
+It then calls the test's \verbx{_judge} method to produce a score.
+A reference to the test and model are added to the score for convenience before it is ultimately returned to the user.
+
+\subsection{Test Suites and Score Matrices} A collection of tests intended to be run on the same model can be put together to form a test suite.
 The following is a test suite that could be used for a simplified version of the QSNMC:  
@@
 \end{python}
-When a test suite is executed against a model, it produces summary data that can be shown on the console or visualized by other tools, such as the web application described in Sec. \ref{sec:scidash}.
+Like a single test, a test suite is capable of judging one or more models. The result is a score matrix much like the one diagramed in Fig. \ref{fig:sciunit_overview}.
+\begin{python}
+CA1_matrix = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
+\end{python}
+A simple summary of the scores in a score matrix can be printed to the console or  visualized by other tools, such as the web application \textit{SciDash} described in Sec. \ref{sec:scidash}.
 

### 2013-11-02 NeurounitFrontiers/Paper.tex
Wrapped with Frontiers template

--- 2013-11-02 NeurounitFrontiers/Paper.tex
@@
-\documentclass[11pt,letterpaper]{article}
-\pagestyle{plain}
+\documentclass{frontiersSCNS}
 \usepackage{amsmath}
 \usepackage{amssymb}
-\usepackage[utf8]{inputenc}
 \usepackage{times}
@@
 \usepackage{python_syntax}
-\usepackage[sort&compress]{natbib}
 \usepackage{bibentry}
@@
 \usepackage{url}
-\usepackage[compact]{titlesec}
-\titleformat{\subsection}[runin]
-{\normalfont\large\bfseries}{\thesubsection}{1em}{}
-\titleformat{\subsubsection}[runin]
-{\normalfont\large\bfseries}{\thesubsubsection}{1em}{}
-\usepackage{enumitem}
-\usepackage[
-top    = 1in,
-bottom = 1in,
-left   = 1in,
-right  = 1in]{geometry}
+\usepackage{lineno}
 \usepackage{caption}
-\captionsetup{belowskip=0pt,aboveskip=0pt}
-\linespread{0.92} % NSF allows up to 6 lines per inch.  
+\usepackage[english]{babel} 
 \def\UrlFont{\em} % Italicize all URLs.  
-\frenchspacing
-\setlist{nolistsep} % or \setlist{noitemsep} to leave space around whole list
 \lstset{
@@
 
+\linenumbers
+\copyrightyear{}
+\pubyear{}
+
+\def\journal{NeuroInformatics}%%% write here for which journal %%%
+\def\DOI{}
+\def\articleType{Methods}
+\def\keyFont{\fontsize{8}{11}\helveticabold }
+\def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
+\def\Authors{Richard C. Gerkin\,$^{1,*}$, Cyrus Omar\,$^{2}$}
+% Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
+% If one of the authors has a change of address, list the new address below the correspondence details using a superscript symbol and use the same symbol to indicate the author in the author list.
+\def\Address{$^{1}$School of Life Sciences, Arizona State University, Tempe, AZ, USA \\
+$^{2}$Dept. of Computer Science, Carnegie Mellon University, Pittsburgh, PA, USA  }
+% The Corresponding Author should be marked with an asterisk
+% Provide the exact contact address (this time including street name and city zip code) and email of the corresponding author
+\def\corrAuthor{Rick Gerkin}
+\def\corrAddress{ISTB-1 476}
+\def\corrEmail{rgerkin@asu.edu}
+
+% \color{FrontiersColor} Is the color used in the Journal name, in the title, and the names of the sections.
+
 \begin{document}
 
-\section{Abstract}
+\onecolumn
+\firstpage{1}
+
+\title[Running Title]{NeuronUnit: Validation Tests for Neurophysiology}
+\author[\firstAuthorLast ]{\Authors}
+\address{}
+\correspondance{}
+\extraAuth{}% If there are more than 1 corresponding author, comment this line and uncomment the next one.
+%\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
+\topic{}% If your article is part of a Research Topic, please indicate here which.
+
+\maketitle
+
+\begin{abstract}
 Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
@@
 Suites of such unit tests that collectively capture the desired program behavior provide evidence for its validity and correctness. 
-Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' --
+Drawing inspiration from this practice, we developed the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
 executable functions, here written in Python, that compare model predictions against single empirical observations to produce a score indicating agreement between the model and the data. 
 Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
-Building on this framework, we develop \textit{NeuronUnit}, a library that supports validation testing for neurophysiology.
+Building on this framework, we describe here \textit{NeuronUnit}, a library that supports validation testing for neurophysiology.
+
+\tiny
+ \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+\end{abstract}
 
@@
 Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, drawing on their knowledge of prior publications. 
-Unfortunately, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists\cite{jinha_article_2010}.
+However, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists\cite{jinha_article_2010}.
 
@@
 But software developers do not validate components by simply choosing a few interesting inputs and presenting the outputs to reviewers. 
-Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively specify the scope of each component and validate the functionality of its implementation as it is being developed and modified.
+Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively specify the scope of each component and validate the functionality of its implementation as it is being developed and modified\cite{beck2003}.
 Each test individually checks that a small portion of the program meets a single correctness criterion.
@@
 
-Test-driven methodologies have started to see success in science as well. 
+Test-driven methodologies have started to see success in neuroscience as well. 
 Modeling competitions in neuroscience, for example, are typically organized around a collection of simple validation criteria, implemented as executable tests. 
@@
 NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework.
-NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project \cite{osb_url}, and single neuron electrophysiology data available as part of the NeuroElectro Project \cite{neuroelectro_url}.
+NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project\cite{osb_url}, and single neuron electrophysiology data available as part of the NeuroElectro Project\cite{neuroelectro_url}.
 Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}
@@
 While the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that could be implemented once. 
-Recognizing this, we have developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit}\cite{sciunit_url}. 
-To demonstrate the power of this framework and show how it can be used to bridge several existing neuroinformatics tools, we then developed \textit{NeuronUnit\-}. 
-This library allows scientists to build \textit{SciUnit} tests that validate \text{NeuroML} models against electrophysiological data collected by the \textit{NeuroElectro Project} \cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.
+Recognizing this, we developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit}\cite{sciunit_url}. 
+Here we describe \textit{NeuronUnit\-}, which builds upon \textit{SciUnit}, allowing neuroscientists to build \textit{SciUnit} tests that validate neurophysiology models against electrophysiological data.
+We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the Open Source Brain project\cite{osb_url} can be test in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project}\cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.
 This is summarized in Figure \ref{fig:sciunit_overview}, which shows the relationships between the layers described here.
@@
 \vspace{-5px}
-\caption{A single neuron spike count test family implemented using \textit{SciUnit}.
-This family contains logic common to many different systems, so it is distributed in the \textit{NeuronUnit} repository (see Sec.
+\caption{An example single neuron spike count test class implemented using \textit{SciUnit}.
+Because this implementation contains logic common to many different systems, \textit{NeuronUnit} was developed to provide a simpler means to deliver it (see Sec.
 \ref{sec:neuronunit}).}
@@
 %Simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.  
-We begin by constructing an example validation test suite. 
+We first illustrate the form of a generic example \textit{SciUnit} test suite that could be used in neurophysiology. 
 Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons in some brain region, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
@@
 In this case we save the input currents, the model outputs and the observed means and standard deviations alongside the score (line 24).
+A \verbx{sciunit.judge} function executes the test's \verbx{_judge} method on the model, and then on the returned \verbx{sciunit.Score} object sets attributes referring to the model and test instances themselves, producing a complete record of the test result (Fig.
+\ref{fig:neuronunit_example}).
 %We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.
@@
 Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
-An alternative test design to the one in Fig. \ref{fig:rate_test} would add a second required capability (Fig. \ref{fig:training}) and a corresponding training phase to the \verb|run_test| method. 
+An alternative test design to the one in Fig. \ref{fig:rate_test} would add a second required capability (Fig. \ref{fig:training}) and a corresponding training phase to the \verbx{_judge} method. 
 This design would be relevant only for those models for which parameters can be adjusted without human involvement. 
@@
 Although Fig.
-\ref{fig:rate_test} does not include a training phase, if training data is available then models that nevertheless implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
+\ref{fig:rate_test} does not include a training phase, if training data is available then models that nevertheless implement a training capability (like \verbx{LinearModel}) can simply be trained explicitly by calling the capability method just like any other Python method:
 \begin{python}
@@
 
+\begin{wrapfigure}[18]{r}{0.45\textwidth}
+\center
+\vspace{-10px}
+\includegraphics[scale=0.72]{scidash_github.png}
+\caption{A \textit{SciDash} repository on GitHub}
+\label{fig:scidash_repo}
+\end{wrapfigure}
+\vspace{-10px}
+\leavevmode
+
 \textit{SciDash} exists in three layers.
@@
 Each record links to test records (stored in the repository), displaying line-by-line the executed code and intermediate output statements, as well as the underlying models and tests.
-
-\begin{wrapfigure}[18]{r}{0.45\textwidth}
-\center
-\vspace{-10px}
-\includegraphics[scale=0.72]{scidash_github.png}
-\caption{A \textit{SciDash} repository on GitHub}
-\label{fig:scidash_repo}
-\end{wrapfigure}
-\vspace{-10px}
-\leavevmode
 
@@
 \end{python}
-\caption{Working example of a testing in \textit{NeuronUnit}}
+\caption{Working example of testing in \textit{NeuronUnit}}
 \label{fig:neuronunit_example}
@@
 
-\section{Acknowledgements}
+\section*{Disclosure/Conflict-of-Interest Statement}
+%All relationships financial, commercial or otherwise that might be perceived by the academic community as representing a potential conflict of interest must be described.
+If no such relationship exists, authors will be asked to declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
+The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.
+
+\section*{Acknowledgements}
 We thank Sharon Crook, Jonathan Aldrich, Shreejoy Tripathy, and Padraig Gleeson for their support of this project.  
@@
 
-\bibliographystyle{unsrt}
+%\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
+\bibliographystyle{frontiersinSCNS&ENG} % for Medicine articles
 \bibliography{references,references_crook,urls,references_ja}
+
+%\bibliographystyle{unsrt}
+%\bibliography{references,references_crook,urls,references_ja}
 %\listoftodos

### 2013-11-02 NeurounitFrontiers/Paper.tex

@@
 In \textit{SciUnit}, models are instances of Python classes that inherit from \verbx{sciunit.Model}.
-Like tests, the class itself represents a family of models, parameterized by the arguments needed in the constructor.
-A particular model is an object created by supplying the parameters.
+Like tests, the class itself represents a family of models, parameterized by the arguments of the constructor.
+A particular model is an instance of such a class.
 
-A simple \emph{family} of models, \verbx{LinearModel}, implementing the capability in Fig.
+Figure \ref{fig:simple_model} shows how to write a simple {family} of models, \verbx{LinearModel}, that implement the capability in Fig.
 \ref{fig:capability} as well as another capability shown in Fig.
-\ref{fig:training}, is shown in Fig.
-\ref{fig:simple_model}.
-Models in this family, \verbx{LinearModel}, produce a spike count by applying a linear transformation to the mean of the provided input current. 
-The family is parameterized by a scale factor and offset, both scalars. 
-To create a \emph{particular} model, the modeler may choose particular parameter values, just as with test families:
+\ref{fig:training}, discussed below.
+Models in this family generate a spike count by applying a linear transformation to the mean of the provided input current.
+The family is parameterized by the scale factor and the offset of the transformation, both scalars.
+To create a \emph{particular} linear model, a modeler can provide particular parameter values, just as with test families:
 \begin{python}
@@
 Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
-An alternative test design to the one in Fig. \ref{fig:rate_test} would add a second required capability (Fig. \ref{fig:training}) and a corresponding training phase to the \verbx{_judge} method. 
-This design would be relevant only for those models for which parameters can be adjusted without human involvement. 
+An alternative test design would add a training phase where these parameters were fit to data using the capability shown in Fig. \ref{fig:training}. 
+This test could thus only be used for those models for which parameters can be adjusted without human involvement. 
 Whether to build a training phase into the test protocol is a choice left to each modeler. 
-Although Fig.
-\ref{fig:rate_test} does not include a training phase, if training data is available then models that nevertheless implement a training capability (like \verbx{LinearModel}) can simply be trained explicitly by calling the capability method just like any other Python method:
+For example, Fig. \ref{fig:rate_test} does not include a training phase.
+
+If training data is externally available, then models that nevertheless do implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
 \begin{python}

### 2013-11-04 NeurounitFrontiers/Paper.tex
Citation formatting changes

@@
 \documentclass{frontiersSCNS}
-\usepackage{amsmath}
-\usepackage{amssymb}
-\usepackage{times}
-\usepackage{hyperref}
-\usepackage{graphicx}
+%\documentclass{article}
+%\usepackage{biblatex}
+%\usepackage{amsmath}
+%\usepackage{amssymb}
+%\usepackage{times}
+%\usepackage{hyperref}
+%\usepackage{graphicx}
 \usepackage{wrapfig}
 \usepackage{listings}
-\usepackage[usenames,dvipsnames]{xcolor}
-\usepackage{setspace}
+%\usepackage[usenames,dvipsnames]{xcolor}
+%\usepackage{setspace}
 \usepackage{python_syntax}
-\usepackage{bibentry}
+%\usepackage{bibentry}
 \usepackage{todonotes}
@@
 \usepackage{lineno}
-\usepackage{caption}
+%\usepackage{natbib}
+%\usepackage{caption}
+
+%\usepackage{biblatex}
+%\DeclareCiteCommand{\wcite}
+%    [\mkbibfootnote]
+%    {}
+%    {\printfield{title}--\printfield{howpublished}}
+%    {\addcomma\addspace}
+%    {}
+
 \usepackage[english]{babel} 
@@
 \def\firstAuthorLast{Sample {et~al.}} %use et al only if is more than 1 author
-\def\Authors{Richard C. Gerkin\,$^{1,*}$, Cyrus Omar\,$^{2}$}
+\def\Authors{Richard C. Gerkin\,$^{1,*}$ and Cyrus Omar\,$^{2}$}
 % Affiliations should be keyed to the author's name with superscript numbers and be listed as follows: Laboratory, Institute, Department, Organization, City, State abbreviation (USA, Canada, Australia), and Country (without detailed address information such as city zip codes or street names).
@@
 
-\title[Running Title]{NeuronUnit: Validation Tests for Neurophysiology}
+\title[Running Title]{NeuronUnit: Validation Tests for Neurophysiology Models}
 \author[\firstAuthorLast ]{\Authors}
@@
 %\extraAuth{corresponding Author2 \\ Laboratory X2, Institute X2, Department X2, Organization X2, Street X2, City X2 , State XX2 (only USA, Canada and Australia), Zip Code2, X2 Country X2, email2@uni2.edu}
-\topic{}% If your article is part of a Research Topic, please indicate here which.
+\topic{Python in Neuroscience II}% If your article is part of a Research Topic, please indicate here which.
 
@@
 Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, drawing on their knowledge of prior publications. 
-However, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists\cite{jinha_article_2010}.
+However, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists \citep{jinha_article_2010}.
 
@@
 But software developers do not validate components by simply choosing a few interesting inputs and presenting the outputs to reviewers. 
-Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively specify the scope of each component and validate the functionality of its implementation as it is being developed and modified\cite{beck2003}.
+Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively specify the scope of each component and validate the functionality of its implementation as it is being developed and modified \citep{beck2003}.
 Each test individually checks that a small portion of the program meets a single correctness criterion.
@@
 Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
-This methodology is widely adopted in practice\cite{beck2003}.
+This methodology is widely adopted in practice \citep{beck2003}.
 
@@
 These competitions continue to drive important advances and improve scientists' understanding of the relative merits of different models. 
-For example, the quantitative single neuron modeling competition (QSNMC)\cite{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
-the ``Hopfield'' challenge\cite{hopfield_what_2000} tested techniques for generating neuronal network form given its function; 
-the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity\cite{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction\cite{diadem_url}; and
-examples from other subfields of biology abound\cite{dream_url}.
+For example, the quantitative single neuron modeling competition (QSNMC) \citep{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
+the ``Hopfield'' challenge \citep{hopfield_what_2000} tested techniques for generating neuronal network form given its function; 
+the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity \citep{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction \citep{diadem_url}; and
+examples from other subfields of biology abound \citep{dream_url}.
 % \begin{figure}%{r}{0.6\textwidth}
@@
 NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework.
-NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project\cite{osb_url}, and single neuron electrophysiology data available as part of the NeuroElectro Project\cite{neuroelectro_url}.
+NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project \citep{osb_url}, and single neuron electrophysiology data available as part of the NeuroElectro Project \citep{neuroelectro_url}.
 Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}
@@
 While the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that could be implemented once. 
-Recognizing this, we developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit}\cite{sciunit_url}. 
+Recognizing this, we developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit} \citep{sciunit_url}. 
 Here we describe \textit{NeuronUnit\-}, which builds upon \textit{SciUnit}, allowing neuroscientists to build \textit{SciUnit} tests that validate neurophysiology models against electrophysiological data.
-We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the Open Source Brain project\cite{osb_url} can be test in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project}\cite{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.
+We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the Open Source Brain project \citep{osb_url} can be test in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project} \citep{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.
 This is summarized in Figure \ref{fig:sciunit_overview}, which shows the relationships between the layers described here.
@@
 white noise), and compare these \emph{spike count} predictions to the distribution observed in repeated experimental trials using the same stimulus.
-In our example, we will determine goodness-of-fit by first calculating a p-value from a chi-squared statistic for each prediction and then combining these p-values using Fisher's method\cite{fisher_statistical_1925}.
+In our example, we will determine goodness-of-fit by first calculating a p-value from a chi-squared statistic for each prediction and then combining these p-values using Fisher's method \citep{fisher_statistical_1925}.
 
 Alongside this \emph{spike count test}, a number of other tests capturing different features of the data can be specified to produce a more comprehensive suite. 
-For data of this sort, the QSNMC defined 17 other validation criteria in addition to one based on the overall spike count, capturing features like spike latencies (SL), mean subthreshold voltage (SV), interspike intervals (ISI) and interspike minima (ISM) that can be extracted from the data\cite{jolivet_quantitative_2008}.
+For data of this sort, the QSNMC defined 17 other validation criteria in addition to one based on the overall spike count, capturing features like spike latencies (SL), mean subthreshold voltage (SV), interspike intervals (ISI) and interspike minima (ISM) that can be extracted from the data \citep{jolivet_quantitative_2008}.
 They then defined a combined metric favoring models that broadly succeeded at meeting these criteria, to produce an overall ranking. 
@@
 As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data.
-For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} \cite{neurounit_url} (Sec. \ref{sec:neuronunit}).
+For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} \citep{neurounit_url} (Sec. \ref{sec:neuronunit}).
 
@@
 \ref{fig:rate_test}.
-Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java \cite{java_interfaces_url}. 
+Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java \citep{java_interfaces_url}. 
 In Python, they are written as classes with unimplemented members. 
@@
 \subsection{\textit{NeuronUnit}: A Suite of Tests for Neurophysiology}\label{sec:neuronunit}
-By using machine-readable models from Open Source Brain (OSB), and machine-readable data from resources like The NeuroElectro Project\cite{neuroelectro_url}, we have produced a suite of data-driven validation tests in \textit{NeuronUnit}, as well as tools for capability implementation, and model interfaces for a representative set of canonical neurophysiology models, all publicly available.
+By using machine-readable models from Open Source Brain (OSB), and machine-readable data from resources like The NeuroElectro Project \citep{neuroelectro_url}, we have produced a suite of data-driven validation tests in \textit{NeuronUnit}, as well as tools for capability implementation, and model interfaces for a representative set of canonical neurophysiology models, all publicly available.
 
 \label{sec:neuronunit_acitivities}
-Here we describe standard neuroinformatics tools we have adopted to develop \textit{NeuronUnit}\cite{neurounit_url}.
+Here we describe standard neuroinformatics tools we have adopted to develop \textit{NeuronUnit} \citep{neurounit_url}.
 
 \subsubsection{Models from NeuroML}\label{sec:neuroml_models}
-NeuroML is a standardized model description language for neuroscience \cite{gleeson_neuroml:_2010}. 
+NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
 It permits many neurophysiological/neuroanatomical models to be described in a simulator-independent fashion, and executed across many popular simulators due to inter-conversion capabilities of the NeuroML API.
@@
 
-NeuroConstruct\cite{neuroconstruct_url,gleeson_neuroconstruct:_2007} is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
+NeuroConstruct \citep{neuroconstruct_url,gleeson_neuroconstruct:_2007} is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
 \textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, instantiated with the path to a NeuroML model.  
@@
 
-The Open Source Brain project (OSB,\cite{osb_url}) curates many models described in NeuroML. 
-OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators\cite{neuron_url,genesis_url,nest_url,moose_url}. 
+The Open Source Brain project (OSB, \citep{osb_url}) curates many models described in NeuroML. 
+OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators \citep{neuron_url,genesis_url,nest_url,moose_url}. 
 Concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files) is reported for each model. 
 Thus, OSB is an excellent source of models that, in addition to being open source, are sufficiently described to enable validation. 
-The hippocampal CA1 pyramidal cell is commonly modeled, and we implement one such model hosted on OSB\cite{osb_ca1_url} by simply declaring a \verbx{CA1PyramidalCellModel} class, inheriting from \verbx{NeuroConstructModel}.
+The hippocampal CA1 pyramidal cell is commonly modeled, and we implement one such model hosted on OSB \citep{osb_ca1_url} by simply declaring a \verbx{CA1PyramidalCellModel} class, inheriting from \verbx{NeuroConstructModel}.
 This basic implementation simply ``wraps'' the components of the existing model, with simulator interaction taken care of by \verbx{NeuroConstructModel} methods; 
@@
 All OSB models, and indeed any NeuroML model, can be tested similarly.
-Working together with OSB is part of our \textbf{first collaboration}, and our integration efforts can be publicly tracked\cite{neuroconstruct_rgerkin_url}.
 
@@
 \subsubsection{Capabilities from NeuroTools}
-NeuroTools\cite{neuralensemble_url} is a Python library supporting tasks associated with analysis of neural data (or model output), such as membrane potential time series, spike trains, etc. 
+NeuroTools \citep{neuralensemble_url} is a Python library supporting tasks associated with analysis of neural data (or model output), such as membrane potential time series, spike trains, etc. 
 It is an open source and actively developed project, containing reliable algorithms on which to base neurophysiology tests.
@@
 Answering \textit{how well} requires validation testing against data. 
-The NeuroElectro project\cite{neuroelectro_url} is an effort to curate all published single cell neurophysiology data\cite{tripathy_neuroelectro:_2012}.  
+The NeuroElectro project \citep{neuroelectro_url} is an effort to curate all published single cell neurophysiology data \citep{tripathy_neuroelectro:_2012}.  
 Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning $>$ 2000 single pieces of published data extracted from article tables. 
@@
 As NeuroElectro is the only publicly curated source of such data, it represents a key component for \textit{NeuronUnit} test constuction.
-Continued development of the NeuroElectro API, through which data are systematically exposed to test authors, represents our \textbf{second collaboration}\cite{neuroelectro_dev_url}.
 
@@
 Community-oriented cyberinfrastructure to support the creation and summarization of such collections is essential.
-We used a service called \textit{SciDash} \cite{scidash_url} for coordinated development of software repositories.
+We used a service called \textit{SciDash} \citep{scidash_url} for coordinated development of software repositories.
 
@@
 \textit{SciDash} exists in three layers.
-The \textbf{first layer} is completely under the control of individual developer communities, and consists of git repositories \cite{ram_git_2013} stored on GitHub \cite{github_url}. 
+The \textbf{first layer} is completely under the control of individual developer communities, and consists of git repositories \citep{ram_git_2013} stored on GitHub \citep{github_url}. 
 \textit{SciDash} identifies all similarly structured repositories (by tracking the lineage of a vanilla \textit{SciDash} repository above using the GitHub API).
@@
 \ref{sec:neuronunit_acitivities} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal.
-In the \textit{NeuronUnit} repository\cite{neurounit_url} is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
+In the \textit{NeuronUnit} repository \citep{neurounit_url} is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
 It (1) selects an OSB model; 
@@
 While this does not meet our idealized vision of development and testing, in practice this may be a common scenario. 
-As part of our outreach efforts (Sec. \ref{sec:broader_impacts}) we will train modelers in the use of this framework, and encourage them to use it as part of their workflow of choice. 
 Adoption of \textit{SciUnit} into traditional, custom workflows would be reflected in the Methods sections of articles.
@@
 Importantly, the modeler is not required to expose or rewrite any model flow control. 
-\textbf{Second}, we support multiple environments automatically by using NeuroML\cite{gleeson_neuroml:_2010}, and other simulator-independent model descriptions are possible for other domains. 
-Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator\cite{neuron_url}, this functionality is already mature and in use.
+\textbf{Second}, we support multiple environments automatically by using NeuroML \citep{gleeson_neuroml:_2010}, and other simulator-independent model descriptions are possible for other domains. 
+Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator \citep{neuron_url}, this functionality is already mature and in use.
 This minimizes modeler effort for a large and growing number of models. 
 \textbf{Third}, modelers have an incentive to demonstrate publicly their models' validity. 
-Participation in public modeling competitions (Sec. \ref{sec:existing_efforts}) demonstrates this incentive. 
+Participation in public modeling competitions demonstrates this incentive. 
 \textbf{Fourth}, modelers have an incentive to use \textit{SciUnit} during development (see TDD, above) to ensure that ongoing development preserves correspondence between model and data. 
@@
 \textbf{Second}, NeuroML naturally addresses diversity of scales because it is organized hierarchically, in ``levels.''  
-Models can be sub- or supersets of other models; similarly for SBML\cite{sbml_url,hucka_systems_2003}, a general systems biology markup language. 
-\textbf{Third}, cross-level testing can use ``Representional Similarity Analysis'' (RSA)\cite{kriegeskorte_representational_2008}, requiring only that a model respond to defined inputs (e.g.
+Models can be sub- or supersets of other models; similarly for SBML \citep{sbml_url,hucka_systems_2003}, a general systems biology markup language. 
+\textbf{Third}, cross-level testing can use ``Representional Similarity Analysis'' (RSA) \citep{kriegeskorte_representational_2008}, requiring only that a model respond to defined inputs (e.g.
 stimuli).
@@
 Statistics as applied to neuroscience have been notoriously ``fast and loose''; 
-identification and correction of flawed methodology is becoming increasingly common\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010,fish_fmri_url}, and is accelerated by an open framework.
+identification and correction of flawed methodology is becoming increasingly common \citep{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010,fish_fmri_url}, and is accelerated by an open framework.
 The validation criteria is made explicit in the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model. 
@@
 \textbf{Second}, models cannot perfectly reproduce data that is itself a random draw from a ``true'' distribution. 
-Uncertainty in data must be made explicit, by asking how well a data set validates its own experimental replications\cite{kriegeskorte_representational_2008}. 
+Uncertainty in data must be made explicit, by asking how well a data set validates its own experimental replications \citep{kriegeskorte_representational_2008}. 
 The degree of such ``self-validation'' represents the upper limit of what a model can be expected to achieve, and should represent a ``perfect'' score.
@@
 All things being equal, simpler models are better. 
-Model complexity has many definitions, so \textit{SciDash} will report several complexity metrics\cite{mccabe_complexity_1976}, including: 
+Model complexity has many definitions, so \textit{SciDash} will report several complexity metrics \citep{mccabe_complexity_1976}, including: 
 1) model length; 2) memory use; 3) CPU load; 4) \# of capabilities. 
 \textit{SciDash} will report the model validity vs complexity tradeoff in tabular form (e.g.
-Table \ref{table:record_matrix}), and in a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot.
+Table \ref{fig:scidash_matrix}), and in a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot.
 The set of models which \textit{dominate} all others, i.e.
-that have the highest validity for a given complexity, can be represented as a ``frontier'' in such a scatter plot, a visualization familiar from the symbolic regression package Eureqa\cite{schmidt_distilling_2009}.
+that have the highest validity for a given complexity, can be represented as a ``frontier'' in such a scatter plot, a visualization familiar from the symbolic regression package Eureqa \citep{schmidt_distilling_2009}.
 
@@
 Community participation begins with enumerating the capabilities relevant to a sub-discipline, and then writing tests. 
-Model description can expand within NeuroML (which already covers multiple levels within neuroscience) and tools for capability implementation can incorporate libraries for neuroimaging (NiBabel\cite{nibabel_url}), neuroanatomy (NeuroHDF,\cite{neurohdf_url}) and other sub-disciplines.
-SBML\cite{hucka_systems_2003,sbml_url} will enable expansion beyond neuroscience, facilitated by parallel efforts among NeuroML developers to interface with it (Crook, unpublished). 
-One intriguing possiblity is applying \textit{SciUnit} to the OpenWorm project\cite{open_worm_url}, which through open, collaborative development seeks to model the entire organism C. elegans.
+Model description can expand within NeuroML (which already covers multiple levels within neuroscience) and tools for capability implementation can incorporate libraries for neuroimaging (NiBabel \citep{nibabel_url}), neuroanatomy (NeuroHDF, \citep{neurohdf_url}) and other sub-disciplines.
+SBML \citep{hucka_systems_2003,sbml_url} will enable expansion beyond neuroscience, facilitated by parallel efforts among NeuroML developers to interface with it (Crook, unpublished). 
+One intriguing possiblity is applying \textit{SciUnit} to the OpenWorm project \citep{open_worm_url}, which through open, collaborative development seeks to model the entire organism C. elegans.
 

### 2013-11-04 NeurounitFrontiers/Paper.tex
Replaced URL citations with \url fields

@@
 %\usepackage{times}
-%\usepackage{hyperref}
+\usepackage{hyperref}
 %\usepackage{graphicx}
@@
 the ``Hopfield'' challenge \citep{hopfield_what_2000} tested techniques for generating neuronal network form given its function; 
-the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity \citep{neural_prediction_url}; the Diadem challenge is advancing the art of neurite reconstruction \citep{diadem_url}; and
-examples from other subfields of biology abound \citep{dream_url}.
+the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity (\url{http://neuralprediction.berkeley.edu}); the Diadem challenge is advancing the art of neurite reconstruction (\url{http://www.diademchallenge.org}); and
+examples from other subfields of biology abound (\url{http://www.the-dream-project.org}).
 % \begin{figure}%{r}{0.6\textwidth}
@@
 \vspace{-55px}
-\caption{NeuronUnit overview.
-NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework.
-NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project \citep{osb_url}, and single neuron electrophysiology data available as part of the NeuroElectro Project \citep{neuroelectro_url}.
+\caption{NeuronUnit overview. NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework. 
+NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project (\url{http://www.opensourcebrain.org}), and single neuron electrophysiology data available as part of the NeuroElectro Project (\url{http://neuroelectro.org}).
 Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}
@@
 While the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that could be implemented once. 
-Recognizing this, we developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit} \citep{sciunit_url}. 
+Recognizing this, we developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit} (\url{http://www.sciunit.org}). 
 Here we describe \textit{NeuronUnit\-}, which builds upon \textit{SciUnit}, allowing neuroscientists to build \textit{SciUnit} tests that validate neurophysiology models against electrophysiological data.
-We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the Open Source Brain project \citep{osb_url} can be test in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project} \citep{neuroelectro_url}, leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.
+We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the Open Source Brain project (\url{http://www.opensourcebrain.org}) can be test in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project} (\url{http://neuroelectro.org}), leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.
 This is summarized in Figure \ref{fig:sciunit_overview}, which shows the relationships between the layers described here.
@@
 As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data.
-For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} \citep{neurounit_url} (Sec. \ref{sec:neuronunit}).
+For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec. \ref{sec:neuronunit}).
 
@@
 \ref{fig:rate_test}.
-Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g. Java \citep{java_interfaces_url}. 
+Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g.
+Java (\url{http://docs.oracle.com/javase/tutorial/java/concepts/interface.html}).
 In Python, they are written as classes with unimplemented members. 
@@
 \subsection{\textit{NeuronUnit}: A Suite of Tests for Neurophysiology}\label{sec:neuronunit}
-By using machine-readable models from Open Source Brain (OSB), and machine-readable data from resources like The NeuroElectro Project \citep{neuroelectro_url}, we have produced a suite of data-driven validation tests in \textit{NeuronUnit}, as well as tools for capability implementation, and model interfaces for a representative set of canonical neurophysiology models, all publicly available.
+By using machine-readable models from Open Source Brain (OSB), and machine-readable data from resources like The NeuroElectro Project (\url{http://www.neuroelectro.org}), we have produced a suite of data-driven validation tests in \textit{NeuronUnit}, as well as tools for capability implementation, and model interfaces for a representative set of canonical neurophysiology models, all publicly available.
 
 \label{sec:neuronunit_acitivities}
-Here we describe standard neuroinformatics tools we have adopted to develop \textit{NeuronUnit} \citep{neurounit_url}.
+Here we describe standard neuroinformatics tools we have adopted to develop \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
 
@@
 
-NeuroConstruct \citep{neuroconstruct_url,gleeson_neuroconstruct:_2007} is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
+NeuroConstruct (\citep{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
 \textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, instantiated with the path to a NeuroML model.  
@@
 
-The Open Source Brain project (OSB, \citep{osb_url}) curates many models described in NeuroML. 
-OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators \citep{neuron_url,genesis_url,nest_url,moose_url}. 
+The Open Source Brain project (OSB, \url{http://www.opensourcebrain.org}) curates many models described in NeuroML. 
+OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators (\url{http://www.neuron.yale.edu/neuron}, \url{http://genesis-sim.org}, \url{http://www.nest-initiative.org}, \url{http://moose.ncbs.res.in}).
 Concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files) is reported for each model. 
 Thus, OSB is an excellent source of models that, in addition to being open source, are sufficiently described to enable validation. 
-The hippocampal CA1 pyramidal cell is commonly modeled, and we implement one such model hosted on OSB \citep{osb_ca1_url} by simply declaring a \verbx{CA1PyramidalCellModel} class, inheriting from \verbx{NeuroConstructModel}.
+The hippocampal CA1 pyramidal cell is commonly modeled, and we implement one such model hosted on OSB (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}) by simply declaring a \verbx{CA1PyramidalCellModel} class, inheriting from \verbx{NeuroConstructModel}.
 This basic implementation simply ``wraps'' the components of the existing model, with simulator interaction taken care of by \verbx{NeuroConstructModel} methods; 
@@
 However, there is no mechanism for establishing \textit{how well} they work, i.e. how well the models accord with data. 
-\textit{NeuroUnit} fills this gap by helping OSB (and the larger biology community) assess models using data-driven tests. 
+\textit{NeuronUnit} fills this gap by helping OSB (and the larger biology community) assess models using data-driven tests. 
 \textit{SciUnit} can be applied similarly to other neuroscience (or biology) sub-disciplines using \textit{NeuronUnit} analogues written by the corresponding communities.
@@
 \subsubsection{Capabilities from NeuroTools}
-NeuroTools \citep{neuralensemble_url} is a Python library supporting tasks associated with analysis of neural data (or model output), such as membrane potential time series, spike trains, etc. 
+NeuroTools (\url{http://neuralensemble.org/NeuroTools}) is a Python library supporting tasks associated with analysis of neural data (or model output), such as membrane potential time series, spike trains, etc.
 It is an open source and actively developed project, containing reliable algorithms on which to base neurophysiology tests.
@@
 Answering \textit{how well} requires validation testing against data. 
-The NeuroElectro project \citep{neuroelectro_url} is an effort to curate all published single cell neurophysiology data \citep{tripathy_neuroelectro:_2012}.  
+The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to curate all published single cell neurophysiology data \citep{tripathy_neuroelectro:_2012}.  
 Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning $>$ 2000 single pieces of published data extracted from article tables. 
@@
 Community-oriented cyberinfrastructure to support the creation and summarization of such collections is essential.
-We used a service called \textit{SciDash} \citep{scidash_url} for coordinated development of software repositories.
+We used a service called \textit{SciDash} (\url{http://www.scidash.org}) for coordinated development of software repositories.
 
@@
 \textit{SciDash} exists in three layers.
-The \textbf{first layer} is completely under the control of individual developer communities, and consists of git repositories \citep{ram_git_2013} stored on GitHub \citep{github_url}. 
+The \textbf{first layer} is completely under the control of individual developer communities, and consists of git repositories \citep{ram_git_2013} stored on GitHub \url{http://github.com}. 
 \textit{SciDash} identifies all similarly structured repositories (by tracking the lineage of a vanilla \textit{SciDash} repository above using the GitHub API).
@@
 \ref{sec:neuronunit_acitivities} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal.
-In the \textit{NeuronUnit} repository \citep{neurounit_url} is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
+In the \textit{NeuronUnit} repository (\url{http://github.com/scidash/neuronunit}) is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
 It (1) selects an OSB model; 
@@
 \textbf{Second}, we support multiple environments automatically by using NeuroML \citep{gleeson_neuroml:_2010}, and other simulator-independent model descriptions are possible for other domains. 
-Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator \citep{neuron_url}, this functionality is already mature and in use.
+Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator (\url{http://www.neuron.yale.edu/neuron}), this functionality is already mature and in use.
 This minimizes modeler effort for a large and growing number of models. 
@@
 \textbf{Second}, NeuroML naturally addresses diversity of scales because it is organized hierarchically, in ``levels.''  
-Models can be sub- or supersets of other models; similarly for SBML \citep{sbml_url,hucka_systems_2003}, a general systems biology markup language. 
+Models can be sub- or supersets of other models; similarly for SBML (\citep{hucka_systems_2003}, \url{http://sbml.org}) a general systems biology markup language. 
 \textbf{Third}, cross-level testing can use ``Representional Similarity Analysis'' (RSA) \citep{kriegeskorte_representational_2008}, requiring only that a model respond to defined inputs (e.g.
@@
 Statistics as applied to neuroscience have been notoriously ``fast and loose''; 
-identification and correction of flawed methodology is becoming increasingly common \citep{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010,fish_fmri_url}, and is accelerated by an open framework.
+identification and correction of flawed methodology is becoming increasingly common (\citep{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010}, \url{http://prefrontal.org/files/posters/Bennett-Salmon-2009.jpg}), and is accelerated by an open framework.
 The validation criteria is made explicit in the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model. 
@@
 Community participation begins with enumerating the capabilities relevant to a sub-discipline, and then writing tests. 
-Model description can expand within NeuroML (which already covers multiple levels within neuroscience) and tools for capability implementation can incorporate libraries for neuroimaging (NiBabel \citep{nibabel_url}), neuroanatomy (NeuroHDF, \citep{neurohdf_url}) and other sub-disciplines.
-SBML \citep{hucka_systems_2003,sbml_url} will enable expansion beyond neuroscience, facilitated by parallel efforts among NeuroML developers to interface with it (Crook, unpublished). 
-One intriguing possiblity is applying \textit{SciUnit} to the OpenWorm project \citep{open_worm_url}, which through open, collaborative development seeks to model the entire organism C. elegans.
+Model description can expand within NeuroML (which already covers multiple levels within neuroscience) and tools for capability implementation can incorporate libraries for neuroimaging (NiBabel, \url{http://nipy.org/nibabel}), neuroanatomy (NeuroHDF, \url{http://neurohdf.readthedocs.org}) and other sub-disciplines.
+SBML (\citep{hucka_systems_2003}, \url{http://sbml.org} will enable expansion beyond neuroscience, facilitated by parallel efforts among NeuroML developers to interface with it (Crook, unpublished). 
+One intriguing possiblity is applying \textit{SciUnit} to the OpenWorm project (\url{http://www.openworm.org}), which through open, collaborative development seeks to model the entire organism C.
+elegans.
 

### 2013-11-04 NeurounitFrontiers/Paper.tex
Added more references.

@@
 \caption{NeuronUnit overview. NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework. 
-NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the Open Source Brain (OSB) project (\url{http://www.opensourcebrain.org}), and single neuron electrophysiology data available as part of the NeuroElectro Project (\url{http://neuroelectro.org}).
+NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the \textit{Open Source Brain Project} (OSB, \citep{gleeson_open_2012}, \url{http://www.opensourcebrain.org}), and single neuron electrophysiology data available as part of the NeuroElectro Project (Neuroelectro, \citep{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}).
 Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}
@@
 Here we describe \textit{NeuronUnit\-}, which builds upon \textit{SciUnit}, allowing neuroscientists to build \textit{SciUnit} tests that validate neurophysiology models against electrophysiological data.
-We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the Open Source Brain project (\url{http://www.opensourcebrain.org}) can be test in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project} (\url{http://neuroelectro.org}), leveraging facilities from the \textit{NeuroTools} library to extract relevant features of model output.
+We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the \textit{Open Source Brain Project} (OSB, \cite{gleeson_open_2012}, \url{http://www.opensourcebrain.org}) can be tested in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project} (Neuroelectro, \cite{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}), leveraging facilities from the \textit{NeuroTools} library (\url{http://neuralensemble.org/NeuroTools}) to extract relevant features of model output.
 This is summarized in Figure \ref{fig:sciunit_overview}, which shows the relationships between the layers described here.
@@
 \subsection{\textit{NeuronUnit}: A Suite of Tests for Neurophysiology}\label{sec:neuronunit}
-By using machine-readable models from Open Source Brain (OSB), and machine-readable data from resources like The NeuroElectro Project (\url{http://www.neuroelectro.org}), we have produced a suite of data-driven validation tests in \textit{NeuronUnit}, as well as tools for capability implementation, and model interfaces for a representative set of canonical neurophysiology models, all publicly available.
+By using machine-readable models from \textit{OSB}, and machine-readable data from resources like \textit{NeuroElectro}, we have produced a suite of data-driven validation tests in \textit{NeuronUnit}, as well as tools for capability implementation, and model interfaces for a representative set of canonical neurophysiology models, all publicly available.
 
@@
 
-NeuroConstruct (\citep{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
+NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
 \textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, instantiated with the path to a NeuroML model.  
@@
 
-The Open Source Brain project (OSB, \url{http://www.opensourcebrain.org}) curates many models described in NeuroML. 
-OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators (\url{http://www.neuron.yale.edu/neuron}, \url{http://genesis-sim.org}, \url{http://www.nest-initiative.org}, \url{http://moose.ncbs.res.in}).
+\textit{OSB} curates many models described in NeuroML. 
+OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators such as Neuron (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}).
 Concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files) is reported for each model. 
@@
 \textbf{Second}, we support multiple environments automatically by using NeuroML \citep{gleeson_neuroml:_2010}, and other simulator-independent model descriptions are possible for other domains. 
-Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator (\url{http://www.neuron.yale.edu/neuron}), this functionality is already mature and in use.
-This minimizes modeler effort for a large and growing number of models. 
+Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator (\cite{carnevale_neuron_2006}), this functionality is already mature and in use.
+This minimizes modeler effort for a large (at least 1000, \url{http://www.neuron.yale.edu/neuron/node/69}) and growing number of neuronal models. 
 \textbf{Third}, modelers have an incentive to demonstrate publicly their models' validity. 
@@
 \textbf{Second}, NeuroML naturally addresses diversity of scales because it is organized hierarchically, in ``levels.''  
-Models can be sub- or supersets of other models; similarly for SBML (\citep{hucka_systems_2003}, \url{http://sbml.org}) a general systems biology markup language. 
+Models can be sub- or supersets of other models; similarly for SBML (\cite{hucka_systems_2003}, \url{http://sbml.org}) a general systems biology markup language. 
 \textbf{Third}, cross-level testing can use ``Representional Similarity Analysis'' (RSA) \citep{kriegeskorte_representational_2008}, requiring only that a model respond to defined inputs (e.g.
@@
 Statistics as applied to neuroscience have been notoriously ``fast and loose''; 
-identification and correction of flawed methodology is becoming increasingly common (\citep{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010}, \url{http://prefrontal.org/files/posters/Bennett-Salmon-2009.jpg}), and is accelerated by an open framework.
+identification and correction of flawed methodology is becoming increasingly common (\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010}, \url{http://prefrontal.org/files/posters/Bennett-Salmon-2009.jpg}), and is accelerated by an open framework.
 The validation criteria is made explicit in the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model. 
@@
 what a model \textit{should} do -- this process documented via standard moderation techiniques used on GitHub -- and the \textit{SciUnit} framework determines whether the model \textit{does} it.
+This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).
 
@@
 Model description can expand within NeuroML (which already covers multiple levels within neuroscience) and tools for capability implementation can incorporate libraries for neuroimaging (NiBabel, \url{http://nipy.org/nibabel}), neuroanatomy (NeuroHDF, \url{http://neurohdf.readthedocs.org}) and other sub-disciplines.
-SBML (\citep{hucka_systems_2003}, \url{http://sbml.org} will enable expansion beyond neuroscience, facilitated by parallel efforts among NeuroML developers to interface with it (Crook, unpublished). 
+SBML will enable expansion beyond neuroscience, facilitated by parallel efforts among NeuroML developers to interface with it (Crook, unpublished). 
 One intriguing possiblity is applying \textit{SciUnit} to the OpenWorm project (\url{http://www.openworm.org}), which through open, collaborative development seeks to model the entire organism C.

### 2013-11-07 NeurounitFrontiers/Paper.tex
updated abstracted slightly

@@
 
-Software engineers validate software by developing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. 
-Suites of such unit tests that collectively capture the desired program behavior provide evidence for its validity and correctness. 
-Drawing inspiration from this practice, we developed the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
-executable functions, here written in Python, that compare model predictions against single empirical observations to produce a score indicating agreement between the model and the data. 
+Software engineers validate software by writing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. 
+Suites of such unit tests can collectively provide evidence for its validity and correctness. 
+Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
+executable functions, here written in Python, that compare model predictions against a single empirical observation to produce a score indicating agreement between the model and the data. 
 Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
-Building on this framework, we describe here \textit{NeuronUnit}, a library that supports validation testing for neurophysiology.
+As a first application of this framework, we describe \textit{NeuronUnit}, a library that supports validation testing for neurophysiology and integrates with several existing neuroinformatics resources.
 

### 2013-11-07 NeurounitFrontiers/Paper.tex
Minor edits to Section 2

@@
 Professional software developers face similar issues. 
-They must understand the scope of each component of a software project and validate it by measuring how well each component achieves its stated goals. 
+They must understand the scope of each component of a complex software project and validate it by measuring how well each component achieves its specified input/output behavior. 
 But software developers do not validate components by simply choosing a few interesting inputs and presenting the outputs to reviewers. 
-Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that collectively specify the scope of each component and validate the functionality of its implementation as it is being developed and modified \citep{beck2003}.
+Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that serve to specify each component's scope and validate its implementation as it is being developed and modified \citep{beck2003}.
 Each test individually checks that a small portion of the program meets a single correctness criterion.
@@
 \section{Validation Testing with \textit{SciUnit}}
-\subsection{Example: Quantitative Single Neuron Modeling Competition}
+\subsection{Example: The Quantitative Single Neuron Modeling Competition}
 \begin{figure}
@@
 white noise), and compare these \emph{spike count} predictions to the distribution observed in repeated experimental trials using the same stimulus.
-In our example, we will determine goodness-of-fit by first calculating a p-value from a chi-squared statistic for each prediction and then combining these p-values using Fisher's method \citep{fisher_statistical_1925}.
+For data of this type, goodness-of-fit can be measured by first calculating a p-value from a chi-squared statistic for each prediction and then combining these p-values using Fisher's method \citep{fisher_statistical_1925}.
 
-Alongside this \emph{spike count test}, a number of other tests capturing different features of the data can be specified to produce a more comprehensive suite. 
+Alongside this \emph{spike count test}, we might also specify a number of other tests capturing different features of the data  to produce a more comprehensive suite. 
 For data of this sort, the QSNMC defined 17 other validation criteria in addition to one based on the overall spike count, capturing features like spike latencies (SL), mean subthreshold voltage (SV), interspike intervals (ISI) and interspike minima (ISM) that can be extracted from the data \citep{jolivet_quantitative_2008}.
@@
 \subsection{Implementing a Validation Test in \textit{SciUnit}}
-Fig. \ref{fig:rate_test} shows how a scientist would implement spike count tests such as the one described above using \textit{SciUnit}. 
+Fig. \ref{fig:rate_test} shows how a scientist can implement spike count tests such as the one described above using \textit{SciUnit}. 
 A \textit{SciUnit} validation test is an {instance} (i.e. an object) of a Python class implementing the \verbx{sciunit.Test} interface (cf. line 1). 
@@
 \ref{fig:rate_test}.
-Capabilities are simply collections of methods that a test may need to invoke to receive relevant data, and are analogous to \emph{interfaces} in e.g.
+Capabilities are simply collections of methods that a test will need to invoke in order to receive relevant data, and are analogous to \emph{interfaces} in e.g.
 Java (\url{http://docs.oracle.com/javase/tutorial/java/concepts/interface.html}).
-In Python, they are written as classes with unimplemented members. 
+In Python, capabilities are written as classes with unimplemented members. 
 The capability required by the test in Fig. \ref{fig:rate_test} is shown in Fig. \ref{fig:capability}. 
@@
 
-The remainder of the \verbx{run_test} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.PValue}, a subclass of \verbx{sciunit.Score} included with \textit{SciUnit}.
-In addition to the score itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for  those who may wish to examine the result in more detail.
-In this case we save the input currents, the model outputs and the observed means and standard deviations alongside the score (line 24).
-A \verbx{sciunit.judge} function executes the test's \verbx{_judge} method on the model, and then on the returned \verbx{sciunit.Score} object sets attributes referring to the model and test instances themselves, producing a complete record of the test result (Fig.
-\ref{fig:neuronunit_example}).
+The remainder of the \verbx{_judge} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.PValue}, a subclass of \verbx{sciunit.Score} that is included with \textit{SciUnit}.
+In addition to the $p$-value itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for  scientists who may wish to examine the result in more detail later.
+In this case we save the input currents, the model outputs and the observed means and standard deviations (line 24). 
 %We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.
@@
 \ref{fig:capability} as well as another capability shown in Fig.
-\ref{fig:training}, discussed below.
+\ref{fig:training}, which we will discuss below.
 Models in this family generate a spike count by applying a linear transformation to the mean of the provided input current.
@@
 This test could thus only be used for those models for which parameters can be adjusted without human involvement. 
-Whether to build a training phase into the test protocol is a choice left to each modeler. 
-For example, Fig. \ref{fig:rate_test} does not include a training phase.
+Whether to build a training phase into the test protocol is a choice left to each test development community.
 
-If training data is externally available, then models that nevertheless do implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
+Fig. \ref{fig:rate_test} does not include a training phase. 
+If training data is externally available, models that nevertheless do implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
 \begin{python}
@@
 It then calls the test's \verbx{_judge} method to produce a score.
-A reference to the test and model are added to the score for convenience before it is ultimately returned to the user.
+A reference to the test and model are added to the score for convenience (accessible via the \verbx{test} and \verbx{model} attributes, respectively), before it is returned.
 
 \subsection{Test Suites and Score Matrices} A collection of tests intended to be run on the same model can be put together to form a test suite.
-The following is a test suite that could be used for a simplified version of the QSNMC:  
+The following is a test suite that could be used for a simplified version of the QSNMC, as described above:  
 \begin{python}

### 2013-11-08 NeurounitFrontiers/Paper.tex
Updated intro to sec 3

@@
 % Section 3.
-\section{Results}
+\section{Integrating With Neuroinformatics Tools and Infrastructure}
+In the examples above, tests were parameterized by data explicitly, and models implemented capabilities directly.
+In practice, however, both models and data are being published in specialized repositories.
+These repositories standardize the data according to emerging standards, making them available in a uniform manner.
+In this section, we will show how to leverage this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
 
-\subsection{\textit{NeuronUnit}: A Suite of Tests for Neurophysiology}\label{sec:neuronunit}
-By using machine-readable models from \textit{OSB}, and machine-readable data from resources like \textit{NeuroElectro}, we have produced a suite of data-driven validation tests in \textit{NeuronUnit}, as well as tools for capability implementation, and model interfaces for a representative set of canonical neurophysiology models, all publicly available.
+\subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit}\label{sec:neuronunit_acitivities}
+In particular, we will focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}.
+Functions that conveniently link these tools to \textit{SciUnit}, along with collection of relevant model and test families and associated capabilities are available in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
+\todo{Sentence about how great github is for collaboratively doing things, particularly in science?} Scientists can use these tools to create test suites tailored to specific systems of interest (for example, scientists interested specifically in models of cells in the hippocampus would use \textit{NeuronUnit} to create a suite, \textit{HippocampusSuite}, parameterized by relevant data from \textit{NeuroElectro}).
 
-\label{sec:neuronunit_acitivities}
-Here we describe standard neuroinformatics tools we have adopted to develop \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
+We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop similar repositories that synergistically link \textit{SciUnit} to relevant ongoing standardization efforts and provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain.
 
-\subsubsection{Models from NeuroML}\label{sec:neuroml_models}
+\subsection{Models from NeuroML}\label{sec:neuroml_models}
 NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
@@
 
-\subsubsection{Capabilities from NeuroTools}
+\subsection{Capabilities from NeuroTools}
 NeuroTools (\url{http://neuralensemble.org/NeuroTools}) is a Python library supporting tasks associated with analysis of neural data (or model output), such as membrane potential time series, spike trains, etc.
@@
 
-\subsubsection{Reference Data for Tests from NeuroElectro}
+\subsection{Reference Data for Tests from NeuroElectro}
 Answering \textit{how well} requires validation testing against data. 
@@
 
-\subsection{\textit{SciDash}: A community web application}\label{sec:scidash}
+\section{\textit{SciDash}: A community web application}\label{sec:scidash}
 A collection of tests, models, and test records can summarize the current state of modeling in a research area.  

### 2013-11-15 NeurounitFrontiers/Paper.tex
Removed all mention of SciDash

@@
 % \textit{NeuronUnit} is proposed and described here.  Experimental data guides test development; model generation informs and is informed by these \textit{SciUnit} libraries.  
-% Each \text{SciUnit} test suite repository on GitHub is indexed by the \textit{SciDash} web application.  
 % Test suites for OSB and QSNMC (described in the text) are being built. 
-% \textit{SciDash} automatically runs the test collections in each suite and publicly displays the results.}}
 % %\vspace{-10px}
@@
 \caption{NeuronUnit overview. NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework. 
-NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the \textit{Open Source Brain Project} (OSB, \citep{gleeson_open_2012}, \url{http://www.opensourcebrain.org}), and single neuron electrophysiology data available as part of the NeuroElectro Project (Neuroelectro, \citep{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}).
-Records of test results for various model/test combinations are accessible via SciDash, which indexes GitHub repositories of these records, models, and tests so they can be searched and filtered by the community.}
+NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the \textit{Open Source Brain Project} (OSB, \citep{gleeson_open_2012}, \url{http://www.opensourcebrain.org}), and single neuron electrophysiology data available as part of the NeuroElectro Project (Neuroelectro, \citep{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}).}
 \label{fig:sciunit_overview}
@@
 In this case we save the input currents, the model outputs and the observed means and standard deviations (line 24).
-%We discuss visualization of results in Secs. \ref{sec:scidash_activities} and \ref{sec:scidash_visualization}.
 
@@
 \end{python}
-A simple summary of the scores in a score matrix can be printed to the console or  visualized by other tools, such as the web application \textit{SciDash} described in Sec. \ref{sec:scidash}.
+A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.
 
@@
 
-\section{\textit{SciDash}: A community web application}\label{sec:scidash}
-A collection of tests, models, and test records can summarize the current state of modeling in a research area.  
-Community-oriented cyberinfrastructure to support the creation and summarization of such collections is essential.
-We used a service called \textit{SciDash} (\url{http://www.scidash.org}) for coordinated development of software repositories.
-
-\begin{wrapfigure}[18]{r}{0.45\textwidth}
-\center
-\vspace{-10px}
-\includegraphics[scale=0.72]{scidash_github.png}
-\caption{A \textit{SciDash} repository on GitHub}
-\label{fig:scidash_repo}
-\end{wrapfigure}
-\vspace{-10px}
-\leavevmode
-
-\textit{SciDash} exists in three layers.
-The \textbf{first layer} is completely under the control of individual developer communities, and consists of git repositories \citep{ram_git_2013} stored on GitHub \url{http://github.com}. 
-\textit{SciDash} identifies all similarly structured repositories (by tracking the lineage of a vanilla \textit{SciDash} repository above using the GitHub API).
-This list of repositories is indexed by \textit{SciDash} to form the \textbf{second layer}, an overview of the state of all \textit{SciDash} repositories on GitHub.  
-This index is searchable and filterable on the \textit{SciDash} website to identify repositories of interest to a particular research community.  
-The \textbf{third layer} is a ``dashboard'' view of the state of a field, visible through a matrix of records for model/test combinations in a GitHub repository (Fig. \ref{fig:scidash_repo}). 
-Test records are visualized as a ``record matrix'' composed of large numbers of model/test combinations (Fig. \ref{fig:scidash_matrix}).  
-Each row in this matrix contains results for all tests taken by one model and serve as clear evidence of that model's scope and validity.  
-Hyperlinks in the record matrix point to models, tests, and records available on GitHub. 
-Each record links to test records (stored in the repository), displaying line-by-line the executed code and intermediate output statements, as well as the underlying models and tests.
-
 \begin{figure}%[18]{r}{1\textwidth}
 \includegraphics[scale=0.65]{table.png}
-\caption{A \textit{SciDash} record matrix}
+\caption{A record matrix for SciUnit tests}
 \label{fig:scidash_matrix}
@@
 Adoption of \textit{SciUnit} into traditional, custom workflows would be reflected in the Methods sections of articles.
-
-\subsubsection{Collaboration}
-Community-moderated comments on GitHub will allow test-makers and test-takers to discuss issues associated with test suites. 
-On GitHub, these takes the form of ``issues,'' commit messages, and comments surrounding merge requests from forked repositories. 
-Thus, disagreements about the appropriateness of a test can be openly aired and in many cases resolved. 
-The \textit{SciDash} website itself can also support public comment to extend the features of GitHub. 
-More importantly, we will enable sorting and filtering of \textit{SciDash} results by repository statistics, e.g. the volume of activity and the number of followers, via the GitHub API. 
-This will allow the most important test suites, as judged by each community, to be featured prominently on \textit{SciDash}. 
-Simple tagging should enable filtering by subject matter. 
-We also will support open authentication via existing web applications (Google, Twitter, etc.), lowering the barrier to participation.
 
@@
 Indeed, rank ordering of models may prove more valuable than test scores themselves. 
-\textbf{Second}, suite repositories are open (e.g. Fig. \ref{fig:scidash_repo}), so tests can be cloned and new statistical choices implemented. 
+\textbf{Second}, suite repositories should be open, so tests can be cloned and new statistical choices implemented. 
 Statistics as applied to neuroscience have been notoriously ``fast and loose''; 
@@
 Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative tests.
-A community consensus will slowly emerge in the form a commonly-accepted test suite (see Sec. \ref{sec:scidash}). 
+A community consensus will slowly emerge in the form a commonly-accepted test suite. 
 This community can judge which test version is most appropriate, i.e.
-what a model \textit{should} do -- this process documented via standard moderation techiniques used on GitHub -- and the \textit{SciUnit} framework determines whether the model \textit{does} it.
+what a model \textit{should} do -- this process documented via standard moderation techiniques used on GitHub.
 This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).
@@
 GitHub supports community moderation, permitting users to comment on tests, indicating their concerns. 
-Suite repository popularity, by which \textit{SciDash} results can be filtered, can reflect consensus. 
+Suite repository popularity can reflect consensus. 
 Experimental metadata also constrains a test's relevance, so test writers should select data with metadata appropriate to the system being modeled, and attach the metadata to resulting test scores. 
@@
 1) model length; 2) memory use; 3) CPU load; 4) \# of capabilities. 
-\textit{SciDash} will report the model validity vs complexity tradeoff in tabular form (e.g.
+Future \textit{SciUnit} tools will report the model validity vs complexity tradeoff in tabular form (e.g.
 Table \ref{fig:scidash_matrix}), and in a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot.

### 2013-11-28 NeurounitFrontiers/Paper.tex
Updated

--- 2013-11-08 NeurounitFrontiers/Paper.tex
@@
 
-\title[Running Title]{NeuronUnit: Validation Tests for Neurophysiology Models}
+\title[Running Title]{NeuronUnit: Collaborative Validation Testing of Neurophysiological Models}
 \author[\firstAuthorLast ]{\Authors}
@@
 However, model validation remains an informal and incomplete process, especially in fields like neuroscience where the available data is growing rapidly.   
-This has made it difficult to develop a contemporary understanding of a model's strengths and weaknesses, to adequately compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.
+This has made it difficult to develop compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.
 
-Software engineers validate software by writing simple executable tests, called ``unit tests'', that individually check a portion of a program against a single correctness criterion. 
+Software engineers validate software by writing simple executable tests, called ``unit tests''. 
 Suites of such unit tests can collectively provide evidence for its validity and correctness. 
@@
 In the examples above, tests were parameterized by data explicitly, and models implemented capabilities directly.
-In practice, however, both models and data are being published in specialized repositories.
-These repositories standardize the data according to emerging standards, making them available in a uniform manner.
+In many cases, however, both models and data can be accessed from specialized repositories in standardized formats.
 In this section, we will show how to leverage this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
@@
 In particular, we will focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}.
-Functions that conveniently link these tools to \textit{SciUnit}, along with collection of relevant model and test families and associated capabilities are available in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
+We will provide functions that  link these tools to \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
 \todo{Sentence about how great github is for collaboratively doing things, particularly in science?} Scientists can use these tools to create test suites tailored to specific systems of interest (for example, scientists interested specifically in models of cells in the hippocampus would use \textit{NeuronUnit} to create a suite, \textit{HippocampusSuite}, parameterized by relevant data from \textit{NeuroElectro}).

### 2013-11-28 NeurounitFrontiers/Paper.tex
Revamped abstract

@@
 
-\title[Running Title]{NeuronUnit: Collaborative Validation Testing of Neurophysiological Models}
+\title[Running Title]{NeuronUnit: Collaborative Validation Testing of Neuroscientific Models}
 \author[\firstAuthorLast ]{\Authors}
@@
 \begin{abstract}
-Rigorously validating a scientific model's explanatory power requires comparing its predictions against empirical data on an ongoing basis. 
-However, model validation remains an informal and incomplete process, especially in fields like neuroscience where the available data is growing rapidly.   
-This has made it difficult to develop compare competing models, to determine the state-of-the-art, and to precisely identify open modeling problems.
+Rigorously validating a quantitative scientific model requires comparing its predictions against an unbiased selection of experimental observations according to sound statistical criteria.
+Developing new models thus requires a comprehensive and contemporary understanding of competing models, relevant data and statistical best practices.
+Today, this can only be achieved by developing an encyclopedic knowledge of the literature.
+Unfortunately, in rapidly-growing fields like neuroscience, this has become increasingly untenable, even for the most conscientious scientists.
 
-Software engineers validate software by writing simple executable tests, called ``unit tests''. 
-Suites of such unit tests can collectively provide evidence for its validity and correctness. 
-Drawing inspiration from this practice, we develop the \textit{SciUnit} framework for developing suites of ``model validation tests'' -- 
-executable functions, here written in Python, that compare model predictions against a single empirical observation to produce a score indicating agreement between the model and the data. 
-Suites of such validation tests are used as a summary of modeling progress within a scientific community. 
-As a first application of this framework, we describe \textit{NeuronUnit}, a library that supports validation testing for neurophysiology and integrates with several existing neuroinformatics resources.
+%However, today's model validation process is based on one-time peer review of a scientific publication.
+, and thus remains an informal and incomplete process, particularly in fields like neuroscience where the number of competing models and the volume of relevant data is growing rapidly.
+%This makes it difficult to determine community-accepted validation criteria, compare competing models,  determine the state-of-the-art given the latest experimental data, and to precisely identify open modeling problems.
+
+Software engineers seeking to verify, validate and contribute to a complex software project rely not only on peer review, but on suites of simple executable tests, called ``unit tests''. 
+Drawing inspiration from this practice, we have developed \textit{SciUnit}, a framework for developing ``model validation tests'' -- 
+executable functions, here written in Python, that compare a quantitative model's predictions against a single experimental  observation to produce a score indicating agreement between the model and the data, as determined by a statistical test.
+Suites of such validation tests are collaboratively developed by a scientific community and can be used as a  summary of the state-of-the-art in a scientific community.
+In this paper, we aim to introduce this test-driven workflow to the neuroscience community.
+We proceed by describing \textit{NeuronUnit}, a library that builds upon \textit{SciUnit} and integrates with several existing neuroinformatics standards and resources to support validation testing of single-neuron models using data gathered by neurophysiologists.
 
 \tiny
- \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+ \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling\todo{is this the right format for this?} } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
 \end{abstract}

### 2013-11-28 NeurounitFrontiers/Paper.tex
Revamped abstract v2

@@
 Developing new models thus requires a comprehensive and contemporary understanding of competing models, relevant data and statistical best practices.
-Today, this can only be achieved by developing an encyclopedic knowledge of the literature.
-Unfortunately, in rapidly-growing fields like neuroscience, this has become increasingly untenable, even for the most conscientious scientists.
+Today, developing such an understanding requires an encyclopedic knowledge of the literature.
+Unfortunately, in rapidly-growing fields like neuroscience, this is becoming increasingly untenable, even for the most conscientious scientists.
+For new scientists, this can be a significant barrier to entry.
 
@@
 
-Software engineers seeking to verify, validate and contribute to a complex software project rely not only on peer review, but on suites of simple executable tests, called ``unit tests''. 
-Drawing inspiration from this practice, we have developed \textit{SciUnit}, a framework for developing ``model validation tests'' -- 
-executable functions, here written in Python, that compare a quantitative model's predictions against a single experimental  observation to produce a score indicating agreement between the model and the data, as determined by a statistical test.
-Suites of such validation tests are collaboratively developed by a scientific community and can be used as a  summary of the state-of-the-art in a scientific community.
-In this paper, we aim to introduce this test-driven workflow to the neuroscience community.
-We proceed by describing \textit{NeuronUnit}, a library that builds upon \textit{SciUnit} and integrates with several existing neuroinformatics standards and resources to support validation testing of single-neuron models using data gathered by neurophysiologists.
+Software engineers seeking to verify, validate and contribute to a complex software project rely not only on volumes of human documentation, but on suites of simple executable tests, called ``unit tests''.
+Drawing inspiration from this practice, we have developed \textit{SciUnit}, an easy-to-use framework for developing ``model validation tests'' -- 
+executable functions, here written in Python, that generate predictions from a quantitative model and statistically validate these predictions against a relevant experimental observation to produce a score indicating agreement between the model and the data.
+Suites of such validation tests are collaboratively developed by a scientific community in common repositories  to produce up-to-date statistical summaries of the state-of-the-art in a scientific community.
+In this paper, we aim to detail this test-driven workflow and introduce it to the neuroscience community.
+To be concrete, we describe \textit{NeuronUnit}, a library that builds upon \textit{SciUnit} and integrates with several existing neuroinformatics resources to support validating single-neuron models using data gathered by neurophysiologists.
 

### 2013-11-29 NeurounitFrontiers/Paper.tex
Cyrus' final intro text.

@@
 
-\title[Running Title]{NeuronUnit: Collaborative Validation Testing of Neuroscientific Models}
+\title[Running Title]{NeuronUnit: Collaboratively Testing the Validity of Neuroscientific Models}
 \author[\firstAuthorLast ]{\Authors}
@@
 Drawing inspiration from this practice, we have developed \textit{SciUnit}, an easy-to-use framework for developing ``model validation tests'' -- 
-executable functions, here written in Python, that generate predictions from a quantitative model and statistically validate these predictions against a relevant experimental observation to produce a score indicating agreement between the model and the data.
-Suites of such validation tests are collaboratively developed by a scientific community in common repositories  to produce up-to-date statistical summaries of the state-of-the-art in a scientific community.
+executable functions, here written in Python, that generate and statistically validate predictions from a specified class of scientific models against one relevant empirical observation to produce a score indicating agreement between the model and the data.
+Suites of such validation tests, collaboratively developed by a scientific community in common repositories, produce up-to-date statistical summaries of the state of the field.
 In this paper, we aim to detail this test-driven workflow and introduce it to the neuroscience community.
-To be concrete, we describe \textit{NeuronUnit}, a library that builds upon \textit{SciUnit} and integrates with several existing neuroinformatics resources to support validating single-neuron models using data gathered by neurophysiologists.
+As an initial example, we describe \textit{NeuronUnit}, a library that builds upon \textit{SciUnit} and integrates with several existing neuroinformatics resources to support validating single-neuron models using data gathered by neurophysiologists.
 
 \tiny
- \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling\todo{is this the right format for this?} } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+ \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling Validation\todo{is this the right format for these?} } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
 \end{abstract}
@@
 \section{Introduction}
-Neuroscientists construct quantitative models to coherently explain observations of neurons, circuits, brain regions and behavior. 
-These models can be characterized by their \textit{scope}: the set of observable quantities that the model can generate predictions about, and by their \textit{validity}: the extent to which these predictions agree with empirical observations of those quantities.
+Neuroscientists construct quantitative models to coherently explain experimental observations of neurons, circuits, brain regions and behavior. 
+A model can be characterized by its \textit{scope}: the set of observable quantities that it can generate predictions about, and by its \textit{validity}: the extent to which its predictions agree with available experimental  observations of those quantities.
 
-Today, scientists contribute a new model to the research community by submitting a paper describing how the model works, along with selected figures demonstrating its scope and validity and comparing its validity to other models with the same scope.
-Reviewers are then responsible for discovering relevant data and competing models that the paper did not adequately consider, drawing on their knowledge of prior publications. 
-However, in many areas, the number of publications being generated every year can overwhelm even the most conscientious scientists \citep{jinha_article_2010}.
+Today, scientists contribute a new model to the research community by submitting a paper containing a description of the model's structure and scope along with text and figures that demonstrate its validity and argue for its novelty.
+The scientists tasked with reviewing the paper are  responsible for evaluating these claims, discovering competing models and relevant data the paper did not adequately consider, and ensuring that goodness-of-fit was measured in a statistically sound manner, drawing on their knowledge of prior literature.
+Once a modeling paper is published, it is frozen and cited as-is in perpetuity.
+
+Because publications are the sole vehicle for knowledge about model scope and validity, scientists must rely on an encyclopedic knowledge of the literature to answer \emph{summary questions} like the following:
+\begin{itemize}
+\item Which models are capable of predicting the quantities I am interested in?
+\item What are the best practices for evaluating the goodness-of-fit between these models and  data?
+\item How well do these models perform, as judged to these metrics, given currently available data?
+\item What other quantities can and can't these models predict?
+\item What observations have not yet been adequately explained by any available model?
+\end{itemize}
+
+In some fields, like neuroscience, where the number of relevant publications being generated every year is growing rapidly \citep{jinha_article_2010}, these questions can be difficult for even conscientious senior scientists to answer comprehensively.
+For new scientists, this represents a serious barrier to entry.
 
 %This suggests that tools that help researchers answer questions like these could help readers and reviewers develop a more comprehensive understanding of the state-of-the-art and improve the quality of the research being published as a result: to renewed calls for tools that help researchers .
-
-Unfortunately, there are few alternatives to a comprehensive literature review available when scientists need to answer questions like these:
-\begin{itemize}
-\item Which models are capable of predicting the quantities I am interested in?
-\item Which metrics should be used to evaluate the goodness-of-fit between these models and  data?
-\item How well do these models perform, as judged to these metrics, given currently available data?
-\item What other quantities can and can't these models predict?
-\item What observations are not adequately explained by any available model?
-\end{itemize}
 
@@
 
-Professional software developers face similar issues. 
-They must understand the scope of each component of a complex software project and validate it by measuring how well each component achieves its specified input/output behavior. 
-But software developers do not validate components by simply choosing a few interesting inputs and presenting the outputs to reviewers. 
-Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that serve to specify each component's scope and validate its implementation as it is being developed and modified \citep{beck2003}.
+Professional software developers face similar issues\todo{probably cite our in submission paper here??}. 
+They must understand the scope of each component of a complex software project and verify that each component achieves desired input/output behavior. 
+But software developers do not verify components by simply documenting a few interesting inputs and corresponding outputs and presenting them to other developers for one-time review leading to an archived document.
+Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that serve to specify each component's scope and verify its implementation on an ongoing basis as it is being developed and modified \citep{beck2003}.
 Each test individually checks that a small portion of the program meets a single correctness criterion.
 For example, a unit test might verify that one function within the program correctly handles malformed inputs.
-Collectively, the test results serve as a summary of the validity of the project as it progresses through its development cycle. 
+Collectively, the test results serve as a summary of the project as it progresses through its development cycle. 
 Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
-This methodology is widely adopted in practice \citep{beck2003}.
+This methodology is widely adopted in practice.
 
@@
 
-Test-driven methodologies have started to see success in neuroscience as well. 
-Modeling competitions in neuroscience, for example, are typically organized around a collection of simple validation criteria, implemented as executable tests. 
-These competitions continue to drive important advances and improve scientists' understanding of the relative merits of different models. 
+Test-driven methodologies have started to see success in neuroscience as well, in the form of \emph{modeling competitions}. 
+During these competitions, competitors develop and parameterize models based on publicly-available training data and submit them to a central server.
+There, submitted model are provided hidden testing data which they must use to produce predictions.
+These predictions are validated using publicly available criteria to produce summaries of the relative merits of different models, just as a test suite summarizes the state of a software project.
+Such competitions continue to drive important advances and improve scientists' understanding of their fields. 
 For example, the quantitative single neuron modeling competition (QSNMC) \citep{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
@@
 the Neural Prediction Challenge sought the best stimulus reconstructions, given neuronal activity (\url{http://neuralprediction.berkeley.edu}); the Diadem challenge is advancing the art of neurite reconstruction (\url{http://www.diademchallenge.org}); and
-examples from other subfields of biology abound (\url{http://www.the-dream-project.org}).
+examples from other areas of biomedical research abound (e.g. \url{http://www.the-dream-project.org}).
 % \begin{figure}%{r}{0.6\textwidth}
@@
 
-Each of these examples has leveraged \emph{ad hoc} infrastructure to support test generation. 
-While the specific criteria used to evaluate models varies widely between disciplines in neuroscience, the underlying test-driven methodology has many common features that could be implemented once. 
-Recognizing this, we developed a discipline-agnostic framework for developing scientific validation test suites called \textit{SciUnit} (\url{http://www.sciunit.org}). 
-Here we describe \textit{NeuronUnit\-}, which builds upon \textit{SciUnit}, allowing neuroscientists to build \textit{SciUnit} tests that validate neurophysiology models against electrophysiological data.
-We provide a concrete example pipeline, showing how models described using \text{NeuroML} and provided freely by the \textit{Open Source Brain Project} (OSB, \cite{gleeson_open_2012}, \url{http://www.opensourcebrain.org}) can be tested in fully automated fashion using published, curated data available through the \textit{NeuroElectro Project} (Neuroelectro, \cite{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}), leveraging facilities from the \textit{NeuroTools} library (\url{http://neuralensemble.org/NeuroTools}) to extract relevant features of model output.
-This is summarized in Figure \ref{fig:sciunit_overview}, which shows the relationships between the layers described here.
-% In addition to this open testing toolkit we also provide a library of tests for models of spiking single neurons.
+Each of these examples has leveraged \emph{ad hoc} infrastructure to support model validation. 
+While the specific criteria used to evaluate models can vary widely between modeling domains, the underlying methodology is common and could be implemented once. 
+Recognizing this, and inspired by unit testing practices, we have developed a discipline-agnostic framework for developing \emph{model validation test suites} called \textit{SciUnit} (available from \url{http://sciunit.scidash.org}) \todo{cite sciunit paper again here?}.
+In this paper, we will begin by detailing \textit{SciUnit}, focusing on examples from single-neuron physiology (Sec. \ref{sec:sciunit}).
+
+\textit{SciUnit} contains validation logic common across scientific disciplines, but a particular discipline, such as neurophysiology, might have more specialized logic associated with it that can be shared amongst its sub-disciplines (e.g.
+hippocampal neurophysiology).
+We anticipate a collaborative workflow where this common logic is developed in common repositories on a social coding service, here \textit{Github}.
+For neurophysiology, we have developed such a repository, called \textit{NeuronUnit}.
+This repository contains common testing logic as well as bridges to existing informatics infrastructure to make it easy to import existing data and models.
+In particular, we will show how models described using \text{NeuroML} and provided freely by the \textit{Open Source Brain Project} (OSB, \cite{gleeson_open_2012}, \url{http://www.opensourcebrain.org}) can be tested in a fully automated fashion using published data curated by the \textit{NeuroElectro Project} (NeuroElectro, \cite{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}), leveraging facilities from the \textit{NeuroTools} library (\url{http://neuralensemble.org/NeuroTools}) to extract features from model outputs (Sec.
+\ref{sec:neuronunit}).
+Particular sub-disciplines, like hippocampal neurophysiologists, can use this common logic to select relevant models and tests, forming particular test suites in common repositories.
+The end result of this workflow is a table like the one shown in Figure \ref{fig:sciunit_overview}, where submitted models can be compared based on the scores they achieve on different selected tests.
+These tables serve as a summary of the status of a modeling community, just as the results from a suite of unit tests serve as a summary of the status of a software project, and help scientists answer the questions mentioned above more easily and accurately.
 
 % Section 2.
-\section{Validation Testing with \textit{SciUnit}}
+\section{Validation Testing with \textit{SciUnit}}\label{sec:sciunit}
 \subsection{Example: The Quantitative Single Neuron Modeling Competition}
@@
 % Section 3.
-\section{Integrating With Neuroinformatics Tools and Infrastructure}
+\section{Integrating With Neuroinformatics Tools and Infrastructure}\label{sec:neuronunit}
 In the examples above, tests were parameterized by data explicitly, and models implemented capabilities directly.
@@
 
-\subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit}\label{sec:neuronunit_acitivities}
+\subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit_acitivities}
 In particular, we will focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}.
@@
 
+\section{SciDash: A Lightweight Portal and Visualization Tool}\label{sec:scidash}
 % Section 4.
-\section{Discussion}
+TODO: Short summary of how SciDash works
+
+\section{Discussion}\label{sec:discussion}
 

### 2013-11-29 NeurounitFrontiers/Paper.tex
Updated figure 1
Final secs 1-2

@@
 \begin{figure}
-\vspace{-38px}
+\vspace{-45px}
 \centering
 \includegraphics[scale=0.6]{diagram1.pdf}
-\vspace{-55px}
+\vspace{-65px}
 \caption{NeuronUnit overview. NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework. 
@@
 %Simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.  
-We first illustrate the form of a generic example \textit{SciUnit} test suite that could be used in neurophysiology. 
-Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons in some brain region, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
+We begin by building an example \textit{SciUnit} test suite that could be used in neurophysiology. 
+Suppose we have collected data from an experiment where current stimuli (measured in pA) was delivered to neurons in some brain region, while the somatic membrane potential of each stimulated cell (in mV) was recorded and stored.
 A model claiming to capture this cell type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.
@@
 To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
-For example, given observations from hippocampal CA1 cells (not shown), we can instantiate a test as follows\todo{use iPython style In[0] notation?}:
+For example, given observations from CA1 cells (not shown), we can instantiate a test as follows\todo{use iPython style In[0] notation?}:
 \begin{python}
@@
 As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data.
-For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec. \ref{sec:neuronunit}).
+For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec.
+\ref{sec:neuronunit}).
+Particular tests, like \verbx{CA1_sc_test}, will be derived from these families in suite repositories (e.g.
+\verbx{HippocampusTests}, as shown in Figure \ref{fig:sciunit_overview}).
 
 Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{_judge} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
-To specify the interface between the test and the model (that is, to specify an appropriate scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
+To specify the interface between the test and the model, the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
 \ref{fig:rate_test}.
-Capabilities are simply collections of methods that a test will need to invoke in order to receive relevant data, and are analogous to \emph{interfaces} in e.g.
+Capabilities are simply collections of methods that a test needs a model to implement so that it can provide inputs and generate relevant predictions, and are analogous to \emph{interfaces} in e.g.
 Java (\url{http://docs.oracle.com/javase/tutorial/java/concepts/interface.html}).
@@
 The family is parameterized by the scale factor and the offset of the transformation, both scalars.
-To create a \emph{particular} linear model, a modeler can provide particular parameter values, just as with test families:
+To create a \emph{particular} linear model, a modeler provides parameter values, just as with test families:
 \begin{python}
@@
 An alternative test design would add a training phase where these parameters were fit to data using the capability shown in Fig. \ref{fig:training}. 
-This test could thus only be used for those models for which parameters can be adjusted without human involvement. 
+This alternative test could thus only be used for those models for which parameters can be adjusted without human involvement. 
 Whether to build a training phase into the test protocol is a choice left to each test development community. 
-
 Fig. \ref{fig:rate_test} does not include a training phase. 
-If training data is externally available, models that nevertheless do implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
+If training data is externally available, models that nevertheless are capable of being automatically trained (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
 \begin{python}
@@
 \end{python}
-A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.
+A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development\todo{mention use within iPython to generate an HTML table}.
 
@@
 \label{fig:scidash_matrix}
-\vspace{-15px}
+\vspace{-25px}
 \end{figure}
@@
 \leavevmode
-
-\section{SciDash: A Lightweight Portal and Visualization Tool}\label{sec:scidash}
-% Section 4.
-TODO: Short summary of how SciDash works
-
 \section{Discussion}\label{sec:discussion}

### 2013-11-30 NeurounitFrontiers/Paper.tex
Updated secs 1-3 and figure

@@
 NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the \textit{Open Source Brain Project} (OSB, \citep{gleeson_open_2012}, \url{http://www.opensourcebrain.org}), and single neuron electrophysiology data available as part of the NeuroElectro Project (Neuroelectro, \citep{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}).}
-\label{fig:sciunit_overview}
+\label{fig:sciunit_overview}\vspace{-10px}
 \end{figure}
 \leavevmode
-\vspace{-0px}
 
@@
 \end{python}
-\vspace{-5px}
+\vspace{-15px}
 \caption{An example single neuron spike count test class implemented using \textit{SciUnit}.
@@
 \label{fig:rate_test}
-\vspace{-15px}
+\vspace{-10px}
 \end{figure}
@@
   CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
-\end{python}
+\end{python}\todo{decrease vertical space after python}
 We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided.
@@
 \end{python}
+\vspace{-15px}
 \caption{An example capability specifying a single required method (used by the test in Figure \ref{fig:rate_test}).}
@@
 \end{figure}
-
 \begin{figure}
@@
 \end{python}
+\vspace{-15px}
 \caption{Another capability specifying a training protocol (not used by the test in Figure \ref{fig:rate_test}).}
 \label{fig:training}
-\vspace{-15px}
+\vspace{-10px}
 \end{figure}
@@
 \end{python}
+\vspace{-15px}
 \caption{A model that returns a spike count by applying a linear transformation to the mean input current.
@@
 \label{fig:simple_model}
-\vspace{-15px}
+\vspace{-10px}
 \end{figure}
@@
 \begin{python}
-CA1_matrix = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
+scores = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
 \end{python}
@@
 \section{Integrating With Neuroinformatics Tools and Infrastructure}\label{sec:neuronunit}
-In the examples above, tests were parameterized by data explicitly, and models implemented capabilities directly.
-In many cases, however, both models and data can be accessed from specialized repositories in standardized formats.
+In the examples in the previous section, tests were generated from data explicitly, and models implemented capabilities directly.
+In many fields, however, both models and data are available from existing  repositories in standardized formats.
 In this section, we will show how to leverage this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
@@
 \subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit_acitivities}
-In particular, we will focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}.
-We will provide functions that  link these tools to \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
+In particular, we will continue to focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}.
+We provide functions that  link these tools to \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
 \todo{Sentence about how great github is for collaboratively doing things, particularly in science?} Scientists can use these tools to create test suites tailored to specific systems of interest (for example, scientists interested specifically in models of cells in the hippocampus would use \textit{NeuronUnit} to create a suite, \textit{HippocampusSuite}, parameterized by relevant data from \textit{NeuroElectro}).

### 2013-11-30 NeurounitFrontiers/Paper.tex
Rick edits 1-2.3

--- 2013-11-29 NeurounitFrontiers/Paper.tex
@@
 Drawing inspiration from this practice, we have developed \textit{SciUnit}, an easy-to-use framework for developing ``model validation tests'' -- 
-executable functions, here written in Python, that generate and statistically validate predictions from a specified class of scientific models against one relevant empirical observation to produce a score indicating agreement between the model and the data.
+executable functions, here written in Python. 
+These tests generate and statistically validate predictions from a specified class of scientific models against one relevant empirical observation to produce a score indicating agreement between the model and the data.
 Suites of such validation tests, collaboratively developed by a scientific community in common repositories, produce up-to-date statistical summaries of the state of the field.
@@
 \tiny
- \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling Validation\todo{is this the right format for these?} } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
+ \keyFont{ \section{Keywords:} Neuroinformatics Simulation Electrophysiology Software Modeling Validation } %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
 \end{abstract}
@@
 \section{Introduction}
+\label{sec:introduction}
 Neuroscientists construct quantitative models to coherently explain experimental observations of neurons, circuits, brain regions and behavior. 
@@
 \item What are the best practices for evaluating the goodness-of-fit between these models and  data?
-\item How well do these models perform, as judged to these metrics, given currently available data?
+\item How well do these models perform, as judged by these metrics, given currently available data?
 \item What other quantities can and can't these models predict?
@@
 
-Professional software developers face similar issues\todo{probably cite our in submission paper here??}. 
+Professional software developers face similar issues\citep{omar_sciunit_2013}\todo{probably cite our in submission paper here??}. 
 They must understand the scope of each component of a complex software project and verify that each component achieves desired input/output behavior. 
-But software developers do not verify components by simply documenting a few interesting inputs and corresponding outputs and presenting them to other developers for one-time review leading to an archived document.
+But software developers do not verify components by simply documenting a few interesting inputs and corresponding outputs and then presenting them to other developers for one-time review leading to an archived document.
 Rather, they typically follow a \emph{test-driven development} methodology by creating a suite of executable \emph{unit tests} that serve to specify each component's scope and verify its implementation on an ongoing basis as it is being developed and modified \citep{beck2003}.
@@
 Developers can determine which features are unimplemented or buggy by examining the set of failed tests, and progress can be measured in terms of how many tests the program passes over time. 
-This methodology is widely adopted in practice.
+This methodology is widely adopted in practice \citep{beck2003}.
 
@@
 During these competitions, competitors develop and parameterize models based on publicly-available training data and submit them to a central server.
-There, submitted model are provided hidden testing data which they must use to produce predictions.
+There, submitted models are provided hidden testing data which they must use to produce predictions.
 These predictions are validated using publicly available criteria to produce summaries of the relative merits of different models, just as a test suite summarizes the state of a software project.
 Such competitions continue to drive important advances and improve scientists' understanding of their fields. 
-For example, the quantitative single neuron modeling competition (QSNMC) \citep{jolivet_quantitative_2008} investigates the complexity-accuracy tradeoff among reduced models of excitable membranes; 
+For example, the quantitative single neuron modeling competition (QSNMC) \citep{jolivet_quantitative_2008} investigated the complexity-accuracy tradeoff among reduced models of excitable membranes; 
 the ``Hopfield'' challenge \citep{hopfield_what_2000} tested techniques for generating neuronal network form given its function; 
@@
 While the specific criteria used to evaluate models can vary widely between modeling domains, the underlying methodology is common and could be implemented once. 
-Recognizing this, and inspired by unit testing practices, we have developed a discipline-agnostic framework for developing \emph{model validation test suites} called \textit{SciUnit} (available from \url{http://sciunit.scidash.org}) \todo{cite sciunit paper again here?}.
+Recognizing this, and inspired by unit testing practices, we have developed a discipline-agnostic framework for developing \emph{model validation test suites} called \textit{SciUnit} \citep{omar_sciunit_2013} (available from \url{http://sciunit.scidash.org}) \todo{cite sciunit paper again here?}.
 In this paper, we will begin by detailing \textit{SciUnit}, focusing on examples from single-neuron physiology (Sec. \ref{sec:sciunit}).
 
-\textit{SciUnit} contains validation logic common across scientific disciplines, but a particular discipline, such as neurophysiology, might have more specialized logic associated with it that can be shared amongst its sub-disciplines (e.g.
-hippocampal neurophysiology).
+\textit{SciUnit} contains validation logic common across scientific disciplines.
+But a particular discipline, such as neurophysiology, might have more specialized logic associated with it that can be shared amongst its sub-disciplines (e.g. hippocampal neurophysiology). 
 We anticipate a collaborative workflow where this common logic is developed in common repositories on a social coding service, here \textit{Github}. 
@@
 \ref{sec:neuronunit}).
-Particular sub-disciplines, like hippocampal neurophysiologists, can use this common logic to select relevant models and tests, forming particular test suites in common repositories.
+Scientists in particular sub-disciplines, like hippocampal neurophysiologists, can use this common logic to select relevant models and tests, forming focused test suites in common repositories. 
 The end result of this workflow is a table like the one shown in Figure \ref{fig:sciunit_overview}, where submitted models can be compared based on the scores they achieve on different selected tests.
-These tables serve as a summary of the status of a modeling community, just as the results from a suite of unit tests serve as a summary of the status of a software project, and help scientists answer the questions mentioned above more easily and accurately.
+These tables serve as a summary of the status of a modeling community, just as the results from a suite of unit tests serve as a summary of the status of a software project, and help scientists answer the questions mentioned in section \ref{sec:introduction} more easily and accurately.
 
@@
 We first illustrate the form of a generic example \textit{SciUnit} test suite that could be used in neurophysiology. 
-Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons in some brain region, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
-A model claiming to capture this cell type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.
+Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons of a particular subtype, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
+A model claiming to capture this neuron type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.
 
@@
 An alternative test design would add a training phase where these parameters were fit to data using the capability shown in Fig. \ref{fig:training}. 
-This test could thus only be used for those models for which parameters can be adjusted without human involvement. 
+This latter test could thus only be used for those models for which parameters can be adjusted without human involvement. 
 Whether to build a training phase into the test protocol is a choice left to each test development community.
@@
 It then calls the test's \verbx{_judge} method to produce a score.
-A reference to the test and model are added to the score for convenience (accessible via the \verbx{test} and \verbx{model} attributes, respectively), before it is returned.
+\todo{judge vs \_judge} A reference to the test and model are added to the score for convenience (accessible via the \verbx{test} and \verbx{model} attributes, respectively), before it is returned.
 

### 2013-11-30 NeurounitFrontiers/Paper.tex

@@
 %Simple executable \emph{validation tests} that compute agreement between a model prediction and an experimental observation.  
-We first illustrate the form of a generic example \textit{SciUnit} test suite that could be used in neurophysiology. 
+We begin by building an example \textit{SciUnit} test suite that could be used in neurophysiology. 
 Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons of a particular subtype, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
@@
 To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
-For example, given observations from hippocampal CA1 cells (not shown), we can instantiate a test as follows\todo{use iPython style In[0] notation?}:
+For example, given observations from CA1 cells (not shown), we can instantiate a test as follows\todo{use iPython style In[0] notation?}:
 \begin{python}
   CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
-\end{python}
+\end{python}\todo{decrease vertical space after python}
 We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided.
 As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data.
-For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec. \ref{sec:neuronunit}).
+For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec.
+\ref{sec:neuronunit}).
+Particular tests, like \verbx{CA1_sc_test}, will be derived from these families in suite repositories (e.g.
+\verbx{HippocampusTests}, as shown in Figure \ref{fig:sciunit_overview}).
 
 Classes that implement the \verbx{sciunit.Test} interface must contain a \verbx{_judge} method that receives a candidate \emph{model} as input and produces a \textit{score} as output. 
-To specify the interface between the test and the model (that is, to specify an appropriate scope), the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
+To specify the interface between the test and the model, the test author provides a list of \emph{capabilities} in the \verbx{required_capabilities} attribute, seen on line 12 of Fig.
 \ref{fig:rate_test}.
-Capabilities are simply collections of methods that a test will need to invoke in order to receive relevant data, and are analogous to \emph{interfaces} in e.g.
+Capabilities are simply collections of methods that a test needs a model to implement so that it can provide inputs and generate relevant predictions, and are analogous to \emph{interfaces} in e.g.
 Java (\url{http://docs.oracle.com/javase/tutorial/java/concepts/interface.html}).
@@
 An alternative test design would add a training phase where these parameters were fit to data using the capability shown in Fig. \ref{fig:training}. 
-This latter test could thus only be used for those models for which parameters can be adjusted without human involvement. 
+This alternative test could thus only be used for those models for which parameters can be adjusted without human involvement. 
 Whether to build a training phase into the test protocol is a choice left to each test development community. 
-
 Fig. \ref{fig:rate_test} does not include a training phase. 
-If training data is externally available, models that nevertheless do implement a training capability (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
+If training data is externally available, models that nevertheless are capable of being automatically trained (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
 \begin{python}
@@
 \begin{python}
-CA1_matrix = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
+scores = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
 \end{python}
-A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.
+A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development\todo{mention use within iPython to generate an HTML table}.
 

### 2013-11-30 NeurounitFrontiers/Paper.tex
Updated section 3.1-3.2

--- 2013-11-30 NeurounitFrontiers/Paper.tex
@@
 \subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit_acitivities}
-In particular, we will continue to focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}.
-We provide functions that  link these tools to \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
-\todo{Sentence about how great github is for collaboratively doing things, particularly in science?} Scientists can use these tools to create test suites tailored to specific systems of interest (for example, scientists interested specifically in models of cells in the hippocampus would use \textit{NeuronUnit} to create a suite, \textit{HippocampusSuite}, parameterized by relevant data from \textit{NeuroElectro}).
+In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
+We implement functions bridging this infrastructure with \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}.
+This package is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
+Scientists can use these tools to easily create test suites tailored to specific systems of interest.
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{HippocampusTests},  parameterized by relevant data from \textit{NeuroElectro}.
+To submit a new model for testing, a scientist can fork this repository, add their models, test it locally, and when satisfied, submit a pull request to the common repository.
+Each community can develop suitable quality standards for merging pull requests.
+Similarly, statisticians interested in improving the methods by which goodness-of-fit are tested can follow the same procedure, rather than attempting to convince scientists socially that the methods used in canonical papers need to be changed.\todo{Sentence about how great github is for collaboratively doing things, particularly in science?}
 
-We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop similar repositories that synergistically link \textit{SciUnit} to relevant ongoing standardization efforts and provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain.
+We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure.
+Using these common repositories, small groups of scientists interested in particular systems of interest will develop tests and curate models in test repositories like \textit{HippocampusTests}.
+The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that help scientists understand, precisely, the state-of-the-art in their field.
 
@@
 NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
-It permits many neurophysiological/neuroanatomical models to be described in a simulator-independent fashion, and executed across many popular simulators due to inter-conversion capabilities of the NeuroML API.
-Because NeuroML is an XML specification, model descriptions can be validated for correctness and queried for model properties and components, exposing potential capabilities. 
-It is ideal for model sharing, curation, and for answering both \textit{what} and \textit{how} programatically.
+It allows many neurophysiological and neuroanatomical models to be described in a simulator-independent fashion. 
+Because NeuroML is an XML specification, model descriptions can be validated for correctness and queried for model properties and components.
+We use these facilities to expose capabilities automatically.
+It has proven ideal for model sharing, curation, and for answering both questions about \textit{what a model does} and \textit{how to do it} programatically.
 
 NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
-\textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, instantiated with the path to a NeuroML model.  
-Because NeuroML can describe such a wide range of models, \verbx{NeuroConstructModel} makes few assumptions about them: that each one is \verbx{TimeIntegrable}, and \verbx{HasMembranePotential}.  
-It is subclassed to test \textit{specific} NeuroML models (Fig. \ref{fig:ca1_model}).
+\textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, parameterized by a path to a NeuroML model.  
+NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that have capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}.
+It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig.
+\ref{fig:ca1_model}).
 
-\textit{OSB} curates many models described in NeuroML. 
-OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators such as Neuron (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}).
+\textit{OSB} curates many models described using NeuroML. 
+OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators including Neuron (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}).
 Concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files) is reported for each model. 
@@
 		project_path = neuroconstruct.get_path("hippocampus","CA1_pyramidal_neuron","CA1PyramidalCell","neuroConstruct")
-		models.NeuroConstructModel.__init__(self,project_path,**kwargs)
+		NeuroConstructModel.__init__(self,project_path,**kwargs)
 \end{python}

### 2013-11-30 NeurounitFrontiers/Paper.tex

@@
 We begin by building an example \textit{SciUnit} test suite that could be used in neurophysiology. 
-Suppose we have collected data from an experiment where current stimuli (measured in pA) was delivered to neurons in some brain region, while the somatic membrane potential of each stimulated cell (in mV) was recorded and stored.
-A model claiming to capture this cell type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.
+Suppose we have collected data from an experiment where current stimuli (measured in pA) are delivered to neurons of a particular subtype, while the somatic membrane potential of each stimulated cell (in mV) is recorded and stored.
+A model claiming to capture this neuron type's membrane potential dynamics must be able to accurately predict a variety of features observed in these data.
 

### 2013-11-30 NeurounitFrontiers/Paper.tex
Rick edits 2.4-4

--- 2013-11-30 NeurounitFrontiers/Paper.tex
@@
 
-This method proceeds by first checking that the provided model implements all required capabilities.
-It then calls the test's \verbx{_judge} method to produce a score.
-\todo{judge vs \_judge} A reference to the test and model are added to the score for convenience (accessible via the \verbx{test} and \verbx{model} attributes, respectively), before it is returned.
+\verbx{judge} is a stock \verbx{sciunit.Test} method that proceeds by first checking that the provided model implements all required capabilities.
+It then calls the test's author-implemented \verbx{_judge} method (note leading underscore) to produce a score.
+A reference to the test and model are added to the score for convenience (accessible via the \verbx{test} and \verbx{model} attributes, respectively), before it is returned.
 
@@
 \end{python}
-A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development\todo{mention use within iPython to generate an HTML table}.
+A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.
+For example, the score matrix might be visualized as an HTML table inside an IPython notebook recording the execution of the test suite.
+
+\begin{figure}%[18]{r}{1\textwidth}
+\includegraphics[scale=0.65]{table.png}
+\caption{A record matrix for SciUnit tests}
+\label{fig:scidash_matrix}
+\vspace{-5px}
+\end{figure}
+\vspace{-10px}
+\leavevmode
 
@@
 In particular, we will continue to focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}.
-We provide functions that  link these tools to \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}) \todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
-\todo{Sentence about how great github is for collaboratively doing things, particularly in science?} Scientists can use these tools to create test suites tailored to specific systems of interest (for example, scientists interested specifically in models of cells in the hippocampus would use \textit{NeuronUnit} to create a suite, \textit{HippocampusSuite}, parameterized by relevant data from \textit{NeuroElectro}).
+We provide functions that  link these tools to \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
+\todo{Sentence about how great github is for collaboratively doing things, particularly in science?} Neuroscientists can use these tools to create test suites tailored to specific systems of interest (for example, investigators interested specifically in models of cells in the hippocampus would use \textit{NeuronUnit} to create a suite, \textit{hippocampus\_tests}, parameterized by relevant data from \textit{NeuroElectro}).
 
@@
 \textit{OSB} curates many models described in NeuroML. 
-OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators such as Neuron (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}).
-Concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files) is reported for each model. 
+OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators such as NEURON (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}).
+Concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files or published figures) is reported for each model. 
 Thus, OSB is an excellent source of models that, in addition to being open source, are sufficiently described to enable validation. 
@@
 However, there is no mechanism for establishing \textit{how well} they work, i.e. how well the models accord with data. 
-\textit{NeuronUnit} fills this gap by helping OSB (and the larger biology community) assess models using data-driven tests. 
+\textit{NeuronUnit} fills this gap by helping OSB (and the larger neuroscience community) assess models using data-driven tests. 
 \textit{SciUnit} can be applied similarly to other neuroscience (or biology) sub-disciplines using \textit{NeuronUnit} analogues written by the corresponding communities.
@@
 For example, an \verbx{AnalogSignal} object (e.g. a membrane potential time series) from NeuroTools has a threshold detection method that returns a NeuroTools \verbx{SpikeTrain} object. 
-A \textit{NeuronUnit} \verbx{HasSpikeTrain} Capability requires that the method \verbx{getSpikeTrain} be implemented. 
+Meanwhile, a \textit{NeuronUnit} \verbx{HasSpikeTrain} Capability requires that the method \verbx{getSpikeTrain} be implemented. 
 \verbx{NeuroConstructModel} does so by placing the object method \verbx{AnalogSignal.threshold_detection} inside \verbx{getSpikeTrain}. 
 Many such NeuroTools objects are similarly exchanged between \verbx{NeuroConstructModel} methods. 
-This simplifies test writing, since basic model output properties are obtained trivially using NeuroTools object methods, and these NeuroTools objects are easily extracted from model output using candidate models subclassing \verbx{NeuroConstructModel}.
+This simplifies test writing, since basic model output properties are obtained trivially using the methods of NeuroTools objects, and these NeuroTools objects are easily extracted from model output, especially when the models subclass \verbx{NeuroConstructModel}.
 
@@
 The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to curate all published single cell neurophysiology data \citep{tripathy_neuroelectro:_2012}.  
-Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning $>$ 2000 single pieces of published data extracted from article tables. 
+Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning $>$ 2000 single pieces of published data extracted from journal article tables. 
 We have made it easy to construct \textit{NeuronUnit} tests using the NeuroElectro API to get reference data. 
 Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
-The former is illustrated in Figure \ref{fig:neuronunit_example}. 
+The latter is illustrated in Figure \ref{fig:neuronunit_example}. 
 Associated statistics of that data (e.g mean, standard error, and sample size) are attached and enable judgement of model output according to a chosen scoring mechanism. 
@@
 
-\begin{figure}%[18]{r}{1\textwidth}
-\includegraphics[scale=0.65]{table.png}
-\caption{A record matrix for SciUnit tests}
-\label{fig:scidash_matrix}
-\vspace{-25px}
-\end{figure}
-\vspace{-10px}
-\leavevmode
 \section{Discussion}\label{sec:discussion}
@@
 Although the tools described in Sec.
-\ref{sec:neuronunit_acitivities} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal.
+\ref{sec:neuronunit} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal.
 In the \textit{NeuronUnit} repository (\url{http://github.com/scidash/neuronunit}) is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
@@
 (2) simulates it using NeuroConstruct; 
-(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTestDynamic};
+(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTestDynamic}; \todo{Update this with current examples.py content}
 and (4) computes and prints a test score (Figure~\ref{fig:neuronunit_example}).
@@
 While this does not meet our idealized vision of development and testing, in practice this may be a common scenario.
-Adoption of \textit{SciUnit} into traditional, custom workflows would be reflected in the Methods sections of articles.
 
@@
 \textbf{Second}, we support multiple environments automatically by using NeuroML \citep{gleeson_neuroml:_2010}, and other simulator-independent model descriptions are possible for other domains. 
-Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator (\cite{carnevale_neuron_2006}), this functionality is already mature and in use.
+Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator (\cite{carnevale_neuron_2006}), this functionality is already implemented in use.
 This minimizes modeler effort for a large (at least 1000, \url{http://www.neuron.yale.edu/neuron/node/69}) and growing number of neuronal models. 
@@
 \textbf{Second}, data-sharing is becoming accepted, and test-writing can be distributed across scientists, including non-experimentalists with other aims such as analysis or modeling. 
-\textbf{Third}, many tests can be automatically generated using the NeuroElectro API, and the continued emergence of such data-aggregation initiatives will expand these possibilities. 
+\textbf{Third}, many tests can be automatically generated using NeuronUnit, and the continued emergence of data-aggregation initiatives such as NeuroElectro will expand these possibilities. 
 \textbf{Fourth}, an incentive to write tests for one's data exists: the ability to identify models that give the data clear context and impact.
@@
 \textbf{First}, we address this by providing an interface allowing modelers to express specific capabilities.  
-This capability set determines the range of eligible tests.  Scale hierarchies are embedded in capability inheritance.  =
+This capability set determines the range of eligible tests.  Scale hierarchies are embedded in capability inheritance. 
 For example, \verbx{HasActionPotentials} inherits from \verbx{HasNeurons}, and \verbx{HodgkinHuxley} inherits from \verbx{VoltageGated}. 
@@
 Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative tests.
-A community consensus will slowly emerge in the form a commonly-accepted test suite. 
-This community can judge which test version is most appropriate, i.e.
-what a model \textit{should} do -- this process documented via standard moderation techiniques used on GitHub.
-This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).
+A community consensus will slowly emerge in the form of commonly-accepted test suites. 
+Such a community can judge which test version is most appropriate, i.e.
+what a model \textit{should} do -- this process documented via standard moderation techiniques used e.g.
+on GitHub.
+This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).\todo{Fix Sumatra reference}
 
@@
 \textbf{First}, the community must evaluate experimental design and methods, discounting data produced using questionable techniques. 
-GitHub supports community moderation, permitting users to comment on tests, indicating their concerns. 
+Open source version control services such as GitHub support community moderation, permitting users to comment on tests, indicating their concerns. 
 Suite repository popularity can reflect consensus. 
-Experimental metadata also constrains a test's relevance, so test writers should select data with metadata appropriate to the system being modeled, and attach the metadata to resulting test scores. 
+Experimental metadata also constrain a test's relevance, so test writers should select data with metadata appropriate to the system being modeled, and attach the metadata to resulting test scores.
+Using the NeuroElectro API, for example, it is possible to select only data corresponding to specific experimental conditions, for example recording electrode type.
 Metadata can also be expressed as Capabilities, e.g. \verbx{At37Degrees} or \verbx{Calcium3mM}; and tests can require that models express them. 
@@
 All things being equal, simpler models are better. 
-Model complexity has many definitions, so \textit{SciDash} will report several complexity metrics \citep{mccabe_complexity_1976}, including: 
+Model complexity has many definitions \citep{mccabe_complexity_1976}, including: 
 1) model length; 2) memory use; 3) CPU load; 4) \# of capabilities. 
 Future \textit{SciUnit} tools will report the model validity vs complexity tradeoff in tabular form (e.g.
-Table \ref{fig:scidash_matrix}), and in a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot.
+Figure \ref{fig:scidash_matrix}), and in a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot.
 The set of models which \textit{dominate} all others, i.e.
@@
 \subsection{Expansion Into Other Areas of Biology}
-After covering neurophysiology, we would like \textit{SciUnit} to be applied across neuroscience and in other biological sciences. 
+After covering neurophysiology with continued development of \textit{NeuronUnit}, we would like \textit{SciUnit} to be applied across neuroscience and in other biological sciences. 
 The framework is discipline-agnostic, so community participation and model description are the only obstacles. 

### 2013-11-30 NeurounitFrontiers/Paper.tex

@@
 \subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit_acitivities}
-In particular, we will continue to focus on neurophysiology in this paper as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from resources like \textit{NeuroElectro}.
-We provide functions that  link these tools to \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}, collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
-\todo{Sentence about how great github is for collaboratively doing things, particularly in science?} Neuroscientists can use these tools to create test suites tailored to specific systems of interest (for example, investigators interested specifically in models of cells in the hippocampus would use \textit{NeuronUnit} to create a suite, \textit{hippocampus\_tests}, parameterized by relevant data from \textit{NeuroElectro}).
+In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
+We implement functions bridging this infrastructure with \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}. 
+This package is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
+Scientists can use these tools to easily create test suites tailored to specific systems of interest. 
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{hippocampus_tests}, parameterized by relevant data from \textit{NeuroElectro}.
+To submit a new model for testing, a scientist can fork this repository, add their models, test it locally, and when satisfied, submit a pull request to the common repository. 
+Each community can develop suitable quality standards for merging pull requests. 
+Similarly, statisticians interested in improving the methods by which goodness-of-fit are tested can follow the same procedure, rather than attempting to convince scientists socially that the methods used in canonical papers need to be changed.
+\todo{Sentence about how great github is for collaboratively doing things, particularly in science?}
 
-We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop similar repositories that synergistically link \textit{SciUnit} to relevant ongoing standardization efforts and provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain.
+We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure.
+Using these common repositories, small groups of scientists interested in particular systems of interest will develop tests and curate models in test repositories like \textit{HippocampusTests}.
+The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that help scientists understand, precisely, the state-of-the-art in their field.
 
@@
 NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
-It permits many neurophysiological/neuroanatomical models to be described in a simulator-independent fashion, and executed across many popular simulators due to inter-conversion capabilities of the NeuroML API.
-Because NeuroML is an XML specification, model descriptions can be validated for correctness and queried for model properties and components, exposing potential capabilities. 
-It is ideal for model sharing, curation, and for answering both \textit{what} and \textit{how} programatically.
+It allows many neurophysiological and neuroanatomical models to be described in a simulator-independent fashion. 
+Because NeuroML is an XML specification, model descriptions can be validated for correctness and queried for model properties and components.
+We use these facilities to expose capabilities automatically.
+It has proven ideal for model sharing, curation, and for answering both questions about \textit{what a model does} and \textit{how to do it} programatically.
 
 NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
-\textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, instantiated with the path to a NeuroML model.  
-Because NeuroML can describe such a wide range of models, \verbx{NeuroConstructModel} makes few assumptions about them: that each one is \verbx{TimeIntegrable}, and \verbx{HasMembranePotential}.  
-It is subclassed to test \textit{specific} NeuroML models (Fig. \ref{fig:ca1_model}).
+\textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, parameterized by a path to a NeuroML model.  
+NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that have capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}.
+It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig.
+\ref{fig:ca1_model}).
 

### 2013-11-30 NeurounitFrontiers/Paper.tex
Updated 3.1 substantially

--- 2013-11-30 NeurounitFrontiers/Paper.tex
@@
 The end result of this workflow is a table like the one shown in Figure \ref{fig:sciunit_overview}, where submitted models can be compared based on the scores they achieve on different selected tests.
-These tables serve as a summary of the status of a modeling community, just as the results from a suite of unit tests serve as a summary of the status of a software project, and help scientists answer the questions mentioned in section \ref{sec:introduction} more easily and accurately.
+These tables serve as a summary of the status of a modeling community, just as the results from a suite of unit tests serve as a summary of the status of a software project, and help scientists answer the questions mentioned earlier in this section more easily and accurately.
 
@@
 In this section, we will show how to leverage this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
+In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
 
-\subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit_acitivities}
-In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
-We implement functions bridging this infrastructure with \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}.
-This package is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
-Scientists can use these tools to easily create test suites tailored to specific systems of interest.
-For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{HippocampusTests},  parameterized by relevant data from \textit{NeuroElectro}.
-To submit a new model for testing, a scientist can fork this repository, add their models, test it locally, and when satisfied, submit a pull request to the common repository.
-Each community can develop suitable quality standards for merging pull requests.
-Similarly, statisticians interested in improving the methods by which goodness-of-fit are tested can follow the same procedure, rather than attempting to convince scientists socially that the methods used in canonical papers need to be changed.\todo{Sentence about how great github is for collaboratively doing things, particularly in science?}
+\subsection{A Collaborative Workflow}\label{sec:neuronunit_acitivities}
+The \textit{NeuronUnit} package contains a collection of test families and associated capabilities  relevant to neurophysiology, such as the tests used in the QSNMC, and is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit}.
+Scientists can use these tools to easily create test suites tailored to specific neural systems of interest.
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{hippocampus\_tests},  parameterizing them by relevant data from \textit{NeuroElectro}.
+To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec.
+\ref{sec:neuroelectro}).
 
-We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure.
-Using these common repositories, small groups of scientists interested in particular systems of interest will develop tests and curate models in test repositories like \textit{HippocampusTests}.
-The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that help scientists understand, precisely, the state-of-the-art in their field.
+Statisticians interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community.
+Rather than attempting to convince a large number of scientists socially that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community.
+Once the testing logic has been changed, all models, past and future, will be immediately re-evaluated against the new metrics.
+Scientists wanting to determine statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.
+
+To submit a new model for testing, a scientist can similarly fork the \textit{hippocampus\_tests} repository, add a new model to the relevant suite using the simple \textit{NeuroML}-\textit{NeuronUnit} bridge described in Sec.
+\ref{sec:neuroml_models} and test the model against available tests locally.
+When satisfied with parameter choices, the scientist can submit the model to \textit{OSB} and use the common \textit{OSB-NeuronUnit} bridge, also described in Sec.
+\ref{sec:neuroml_models}, to refer to it, and finally submit a pull request to the common repository.
+Once a model is in the repository, it will be evaluated on an ongoing basis against the latest accepted collections of tests, which use accepted statistical best practices, without needing the participation of the original modeler, assuming that the capabilities that need to be exposed by models stay stable.
+
+We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure.
+Using these common repositories, small groups of scientists interested in particular systems of interest will develop tests and models in test repositories like \textit{hippocampus\_tests}.
+Each research community can develop suitable quality standards and processes for merging these pull requests.
+
+The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that allow scientists to understand, precisely, the state-of-the-art in their field.
+We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \todo{cite icse paper?}.
+\textit{SciDash} will also facilitate viewing test results without needing to clone test repositories and run tests locally for exploratory purposes, based on the \textit{iPython notebook} technology mentioned in Sec.
+\ref{sec:visualization}.
+We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec.
+2) and on the details of the bridge technologies mentioned above.
+
+\subsection{Reference Data for Tests from NeuroElectro}\label{sec:neuroelectro} 
+The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to gather all published data on single cell neurophysiology into machine-readable formats \citep{tripathy_neuroelectro:_2012}.  
+Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning more than 2000 single pieces of published data extracted from tables in published papers. 
+We have made it easy to parameterize \textit{NeuronUnit} tests using data extracted from the NeuroElectro API. 
+Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
+The former is illustrated in Figure \ref{fig:neuronunit_example}. 
+Associated statistics of that data (e.g mean, standard error, and sample size) are attached and enable judgement of model output according to a chosen scoring mechanism. 
+While NeuroElectro alone cannot judge all model aspects, it can serve to validate basic features of many neurophysiology models, such as resting membrane potential, action potential width, after-hyperpolarization amplitude, etc.
+As NeuroElectro is the only publicly curated source of such data, it represents a key component for \textit{NeuronUnit} test constuction.
 
@@
 This simplifies test writing, since basic model output properties are obtained trivially using NeuroTools object methods, and these NeuroTools objects are easily extracted from model output using candidate models subclassing \verbx{NeuroConstructModel}.
-
-\subsection{Reference Data for Tests from NeuroElectro}
-Answering \textit{how well} requires validation testing against data. 
-The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to curate all published single cell neurophysiology data \citep{tripathy_neuroelectro:_2012}.  
-Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning $>$ 2000 single pieces of published data extracted from article tables. 
-We have made it easy to construct \textit{NeuronUnit} tests using the NeuroElectro API to get reference data. 
-Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
-The former is illustrated in Figure \ref{fig:neuronunit_example}. 
-Associated statistics of that data (e.g mean, standard error, and sample size) are attached and enable judgement of model output according to a chosen scoring mechanism. 
-While NeuroElectro alone cannot judge all model aspects, it can serve to validate basic features of many neurophysiology models, such as resting membrane potential, action potential width, after-hyperpolarization amplitude, etc.
-As NeuroElectro is the only publicly curated source of such data, it represents a key component for \textit{NeuronUnit} test constuction.
 

### 2013-11-30 NeurounitFrontiers/Paper.tex

--- 2013-11-30 NeurounitFrontiers/Paper.tex
@@
 In this section, we will show how to leverage this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
+In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
 
-\subsection{\textit{NeuronUnit}: Neurophysiology-Specific Testing Tools}\label{sec:neuronunit_acitivities}
-In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
-We implement functions bridging this infrastructure with \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}. 
-This package is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
-Scientists can use these tools to easily create test suites tailored to specific systems of interest. 
-For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{hippocampus_tests}, parameterized by relevant data from \textit{NeuroElectro}.
-To submit a new model for testing, a scientist can fork this repository, add their models, test it locally, and when satisfied, submit a pull request to the common repository. 
-Each community can develop suitable quality standards for merging pull requests. 
-Similarly, statisticians interested in improving the methods by which goodness-of-fit are tested can follow the same procedure, rather than attempting to convince scientists socially that the methods used in canonical papers need to be changed.
-\todo{Sentence about how great github is for collaboratively doing things, particularly in science?}
+\subsection{A Collaborative Workflow}\label{sec:neuronunit_acitivities}
+The \textit{NeuronUnit} package contains a collection of test families and associated capabilities  relevant to neurophysiology, such as the tests used in the QSNMC, and is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit}.
+Scientists can use these tools to easily create test suites tailored to specific neural systems of interest.
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{hippocampus\_tests},  parameterizing them by relevant data from \textit{NeuroElectro}.
+To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec.
+\ref{sec:neuroelectro}).
 
-We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families, model families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure.
-Using these common repositories, small groups of scientists interested in particular systems of interest will develop tests and curate models in test repositories like \textit{HippocampusTests}.
-The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that help scientists understand, precisely, the state-of-the-art in their field.
+Statisticians interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community.
+Rather than attempting to convince a large number of scientists socially that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community.
+Once the testing logic has been changed, all models, past and future, will be immediately re-evaluated against the new metrics.
+Scientists wanting to determine statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.
+
+To submit a new model for testing, a scientist can similarly fork the \textit{hippocampus\_tests} repository, add a new model to the relevant suite using the simple \textit{NeuroML}-\textit{NeuronUnit} bridge described in Sec.
+\ref{sec:neuroml_models} and test the model against available tests locally.
+When satisfied with parameter choices, the scientist can submit the model to \textit{OSB} and use the common \textit{OSB-NeuronUnit} bridge, also described in Sec.
+\ref{sec:neuroml_models}, to refer to it, and finally submit a pull request to the common repository.
+Once a model is in the repository, it will be evaluated on an ongoing basis against the latest accepted collections of tests, which use accepted statistical best practices, without needing the participation of the original modeler, assuming that the capabilities that need to be exposed by models stay stable.
+
+We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure.
+Using these common repositories, small groups of scientists interested in particular systems of interest will develop tests and models in test repositories like \textit{hippocampus\_tests}.
+Each research community can develop suitable quality standards and processes for merging these pull requests.
+
+The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that allow scientists to understand, precisely, the state-of-the-art in their field.
+We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \todo{cite icse paper?}.
+\textit{SciDash} will also facilitate viewing test results without needing to clone test repositories and run tests locally for exploratory purposes, based on the \textit{iPython notebook} technology mentioned in Sec.
+\ref{sec:visualization}.
+We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec.
+2) and on the details of the bridge technologies mentioned above.
+
+\subsection{Reference Data for Tests from NeuroElectro}\label{sec:neuroelectro} 
+The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to gather all published data on single cell neurophysiology into machine-readable formats \citep{tripathy_neuroelectro:_2012}.  
+Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning more than 2000 single pieces of published data extracted from tables in published papers. 
+We have made it easy to parameterize \textit{NeuronUnit} tests using data extracted from the NeuroElectro API. 
+Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
+The former is illustrated in Figure \ref{fig:neuronunit_example}. 
+Associated statistics of that data (e.g mean, standard error, and sample size) are attached and enable judgement of model output according to a chosen scoring mechanism. 
+While NeuroElectro alone cannot judge all model aspects, it can serve to validate basic features of many neurophysiology models, such as resting membrane potential, action potential width, after-hyperpolarization amplitude, etc.
+As NeuroElectro is the only publicly curated source of such data, it represents a key component for \textit{NeuronUnit} test constuction.
 
@@
 This simplifies test writing, since basic model output properties are obtained trivially using the methods of NeuroTools objects, and these NeuroTools objects are easily extracted from model output, especially when the models subclass \verbx{NeuroConstructModel}.
-
-\subsection{Reference Data for Tests from NeuroElectro}
-Answering \textit{how well} requires validation testing against data. 
-The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to curate all published single cell neurophysiology data \citep{tripathy_neuroelectro:_2012}.  
-Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning $>$ 2000 single pieces of published data extracted from journal article tables. 
-We have made it easy to construct \textit{NeuronUnit} tests using the NeuroElectro API to get reference data. 
-Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
-The latter is illustrated in Figure \ref{fig:neuronunit_example}. 
-Associated statistics of that data (e.g mean, standard error, and sample size) are attached and enable judgement of model output according to a chosen scoring mechanism. 
-While NeuroElectro alone cannot judge all model aspects, it can serve to validate basic features of many neurophysiology models, such as resting membrane potential, action potential width, after-hyperpolarization amplitude, etc.
-As NeuroElectro is the only publicly curated source of such data, it represents a key component for \textit{NeuronUnit} test constuction.
 

### 2013-11-30 NeurounitFrontiers/Paper.tex
Addressed todo comments

--- 2013-11-30 NeurounitFrontiers/Paper.tex
@@
 
-Professional software developers face similar issues\citep{omar_sciunit_2013}\todo{probably cite our in submission paper here??}. 
+Professional software developers face similar issues \citep{omar_sciunit_2013}. 
 They must understand the scope of each component of a complex software project and verify that each component achieves desired input/output behavior. 
@@
 While the specific criteria used to evaluate models can vary widely between modeling domains, the underlying methodology is common and could be implemented once. 
-Recognizing this, and inspired by unit testing practices, we have developed a discipline-agnostic framework for developing \emph{model validation test suites} called \textit{SciUnit} \citep{omar_sciunit_2013} (available from \url{http://sciunit.scidash.org}) \todo{cite sciunit paper again here?}.
+Recognizing this, and inspired by unit testing practices, we have developed a discipline-agnostic framework for developing \emph{model validation test suites} called \textit{SciUnit} \citep{omar_sciunit_2013} (available from \url{http://sciunit.scidash.org}).
 In this paper, we will begin by detailing \textit{SciUnit}, focusing on examples from single-neuron physiology (Sec. \ref{sec:sciunit}).
@@
 But a particular discipline, such as neurophysiology, might have more specialized logic associated with it that can be shared amongst its sub-disciplines (e.g. hippocampal neurophysiology). 
-We anticipate a collaborative workflow where this common logic is developed in common repositories on a social coding service, here \textit{Github}. 
+We anticipate a collaborative workflow where this common logic is developed in common repositories on a social coding service, here \textit{GitHub}. 
 For neurophysiology, we have developed such a repository, called \textit{NeuronUnit}. 
@@
   CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
-\end{python}\todo{decrease vertical space after python}
+\end{python}
 We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided.
@@
 We implement functions bridging this infrastructure with \textit{SciUnit}, as a collection of relevant model and test families and associated capabilities, in a package called \textit{NeuronUnit}. 
-This package is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit (after I am sure grant has been reviewed)}.
+This package is collaboratively developed on \textit{GitHub} (\url{http://github.com/scidash/neuronunit}). 
 Scientists can use these tools to easily create test suites tailored to specific systems of interest. 
-For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{hippocampus_tests}, parameterized by relevant data from \textit{NeuroElectro}.
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository called \textit{hippocampus\_tests}, parameterized by relevant data from \textit{NeuroElectro}.
 To submit a new model for testing, a scientist can fork this repository, add their models, test it locally, and when satisfied, submit a pull request to the common repository. 
@@
 Similarly, statisticians interested in improving the methods by which goodness-of-fit are tested can follow the same procedure, rather than attempting to convince scientists socially that the methods used in canonical papers need to be changed.
-\todo{Sentence about how great github is for collaboratively doing things, particularly in science?}
+GitHub is an excellent platform for this kind of activity, and is becoming a force for scientific collaboration, reproducibility, and transparency \citep{ram_git_2013}.
 
@@
 # Interface with neuroelectro.org to search for spike widths of CA1 Pyramidal cells. 
-reference_data = NeuroElectroSummary(neuron={'id':85}, ephysprop={'id':23})
+reference_data = neuroelectro.NeuroElectroSummary(
+  neuron = {'name':'Hippocampus CA1 pyramidal cell'}, # Neuron type.  
+  ephysprop = {'name':'Spike Width'}) # Electrophysiological property name.
 reference_data.get_values()  # Get summary data for the above. 
@@
 on GitHub.
-This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).\todo{Fix Sumatra reference}
+This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).
 

### 2013-11-30 NeurounitFrontiers/Paper.tex

--- 2013-11-30 NeurounitFrontiers/Paper.tex
@@
 \subsection{A Collaborative Workflow}\label{sec:neuronunit_acitivities}
-The \textit{NeuronUnit} package contains a collection of test families and associated capabilities  relevant to neurophysiology, such as the tests used in the QSNMC, and is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit})\todo{Must change name of repository on github to neuronunit}.
-Scientists can use these tools to easily create test suites tailored to specific neural systems of interest.
-For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a Github repository called \textit{hippocampus\_tests},  parameterizing them by relevant data from \textit{NeuroElectro}.
-To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec.
-\ref{sec:neuroelectro}).
+The \textit{NeuronUnit} package contains a collection of test families and associated capabilities relevant to neurophysiology, such as the tests used in the QSNMC, and is collaboratively developed on GitHub (\url{http://github.com/scidash/neuronunit}).
+Scientists can use these tools to easily create test suites tailored to specific neuronal systems of interest. 
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository called \textit{hippocampus\_tests}, parameterizing them by relevant data from \textit{NeuroElectro}.
+To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec. \ref{sec:neuroelectro}).
 
@@
 Once a model is in the repository, it will be evaluated on an ongoing basis against the latest accepted collections of tests, which use accepted statistical best practices, without needing the participation of the original modeler, assuming that the capabilities that need to be exposed by models stay stable.
+GitHub is an excellent platform for this kind of activity, and is becoming a force for scientific collaboration, reproducibility, and transparency \citep{ram_git_2013}.
 
@@
 The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that allow scientists to understand, precisely, the state-of-the-art in their field.
-We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \todo{cite icse paper?}.
+We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \citep{omar_sciunit_2013}.
 \textit{SciDash} will also facilitate viewing test results without needing to clone test repositories and run tests locally for exploratory purposes, based on the \textit{iPython notebook} technology mentioned in Sec.

### 2013-11-30 NeurounitFrontiers/Paper.tex
More progress

--- 2013-11-30 NeurounitFrontiers/Paper.tex
@@
 \textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, parameterized by a path to a NeuroML model.  
-NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that have capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}.
+NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that are time-integrable point neurons (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}).
 It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig.

### 2013-11-30 NeurounitFrontiers/Paper.tex
Some updates to text and moved figure 8 up

@@
 We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec.
-2) and on the details of the bridge technologies mentioned above.
+2) and on the details of the bridge technologies.
 
 \subsection{Reference Data for Tests from NeuroElectro}\label{sec:neuroelectro} 
-The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to gather all published data on single cell neurophysiology into machine-readable formats \citep{tripathy_neuroelectro:_2012}.  
-Currently, up to 27 electrophysiological properties are reported for 93 cell types, spanning more than 2000 single pieces of published data extracted from tables in published papers. 
+\begin{figure}
+\begin{python}
+# Interface with neuroelectro.org to search for spike widths of CA1 Pyramidal cells. 
+reference_data = neuroelectro.NeuroElectroSummary(
+  neuron = {'name':'Hippocampus CA1 pyramidal cell'}, # Neuron type.  
+  ephysprop = {'name':'Spike Width'}) # Electrophysiological property name.
+reference_data.get_values()  # Get summary data for the above. 
+model = CA1PyramidalCellModel(population_name="CG_CML_0") # Initialize the model with some parameters.
+test = SpikeWidthTestDynamic( # Initialize the test.    
+	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics from the reference data
+	model_args = {'current':40.0}, # Somatic current injection in pA.  
+	comparator = ZComparator), # A comparison class that implements a Z-score.  
+result = sciunit.judge(test,model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
+result.summarize() # Summarize the result.  
+\end{python}
+\caption{Working example of testing in \textit{NeuronUnit}}
+\label{fig:neuronunit_example}
+\vspace{-15px}
+\end{figure}
+The NeuroElectro project (\url{http://neuroelectro.org}) is an effort to make all published data on single cell neurophysiology available in a machine-readable format \citep{tripathy_neuroelectro:_2012}.
+Currently, up to 27 electrophysiological properties are available for 93 cell types, gathered from over 2000 single pieces of published data extracted from tables in published papers. 
 We have made it easy to parameterize \textit{NeuronUnit} tests using data extracted from the NeuroElectro API. 
@@
 and (4) computes and prints a test score (Figure~\ref{fig:neuronunit_example}).
-
-\begin{figure}
-\begin{python}
-# Interface with neuroelectro.org to search for spike widths of CA1 Pyramidal cells. 
-reference_data = neuroelectro.NeuroElectroSummary(
-  neuron = {'name':'Hippocampus CA1 pyramidal cell'}, # Neuron type.  
-  ephysprop = {'name':'Spike Width'}) # Electrophysiological property name.
-reference_data.get_values()  # Get summary data for the above. 
-model = CA1PyramidalCellModel(population_name="CG_CML_0") # Initialize the model with some parameters.
-test = SpikeWidthTestDynamic( # Initialize the test.    
-	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics from the reference data
-	model_args = {'current':40.0}, # Somatic current injection in pA.  
-	comparator = ZComparator), # A comparison class that implements a Z-score.  
-result = sciunit.judge(test,model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
-result.summarize() # Summarize the result.  
-\end{python}
-\caption{Working example of testing in \textit{NeuronUnit}}
-\label{fig:neuronunit_example}
-\vspace{-15px}
-\end{figure}
 

### 2013-11-30 NeurounitFrontiers/Paper.tex
Updated ipython notebook figure

@@
 A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.
-For example, the score matrix might be visualized as an HTML table inside an IPython notebook recording the execution of the test suite.
+For example, the score matrix might be visualized as a hyperlinked table inside an IPython notebook containing the specification and execution of the test suite (Fig.
+\ref{fig:scidash_matrix}).
+Such notebooks are stored in test repositories like \textit{hippocampus\_tests}.
 
 \begin{figure}%[18]{r}{1\textwidth}
-\includegraphics[scale=0.65]{table.png}
-\caption{A record matrix for SciUnit tests}
+\centering
+\includegraphics[scale=0.55]{table-ipy.pdf}
+\caption{A score matrix for a SciUnit test suite, visualized as a hyperlinked table inside an IPython notebook stored in a test repository like \textit{hippocampus\_tests}.}
 \label{fig:scidash_matrix}

### 2013-11-30 NeurounitFrontiers/Paper.tex
Added paths to figure captions

@@
 \vspace{-15px}
-\caption{An example single neuron spike count test class implemented using \textit{SciUnit}.
+\caption{\texttt{[neuronunit.SpikeCountTest]} An example single neuron spike count test class implemented using \textit{SciUnit}.
 Because this implementation contains logic common to many different systems, \textit{NeuronUnit} was developed to provide a simpler means to deliver it (see Sec.
@@
 \vspace{-15px}
-\caption{An example capability specifying a single required method (used by the test in Figure \ref{fig:rate_test}).}
+\caption{\texttt{[neuronunit.SpikeCountFromCurrent]} An example capability specifying a single required method (used by the test in Figure \ref{fig:rate_test}).}
 \label{fig:capability}
@@
 \vspace{-15px}
-\caption{Another capability specifying a training protocol (not used by the test in Figure \ref{fig:rate_test}).}
+\caption{\texttt{[neuronunit.TrainSpikeCountFromCurrent]} Another capability specifying a training protocol (not used by the test in Figure \ref{fig:rate_test}).}
 \label{fig:training}
@@
 \vspace{-15px}
-\caption{A model that returns a spike count by applying a linear transformation to the mean input current.
+\caption{\texttt{[neuronunit.LinearModel]} A model that returns a spike count by applying a linear transformation to the mean input current.
 The parameters can be provided manually or learned from data provided by a test or user (see text).}
@@
 A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.
-For example, the score matrix might be visualized as a hyperlinked table inside an IPython notebook containing the specification and execution of the test suite (Fig.
+For example, the score matrix might be visualized as a hyperlinked table inside an IPython notebook \todo{reference to ipython nb docs/paper?} containing the specification and execution of the test suite (Fig.
 \ref{fig:scidash_matrix}).
@@
 The \textit{NeuronUnit} package contains a collection of test families and associated capabilities relevant to neurophysiology, such as the tests used in the QSNMC, and is collaboratively developed on GitHub (\url{http://github.com/scidash/neuronunit}).
-Scientists can use these tools to easily create test suites tailored to specific neuronal systems of interest. 
-For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository called \textit{hippocampus\_tests}, parameterizing them by relevant data from \textit{NeuroElectro}.
+Scientists can use this package to easily create test suites tailored to specific neuronal systems of interest. 
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository containing an iPython notebook, as described above, called \textit{hippocampus\_tests}, parameterizing them by relevant data from \textit{NeuroElectro}.
 To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec. \ref{sec:neuroelectro}).
@@
 Rather than attempting to convince a large number of scientists socially that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community.
-Once the testing logic has been changed, all models, past and future, will be immediately re-evaluated against the new metrics. 
-Scientists wanting to determine statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.
+Once the testing logic has been changed, all past models will be immediately evaluated against the new metrics. 
+Scientists wishing to determine statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.
 

### 2013-11-30 NeurounitFrontiers/Paper.tex
Fixed ipython formatting; refactored section 3 into 2 sections

@@
 
-\title[Running Title]{NeuronUnit: Collaboratively Testing the Validity of Neuroscientific Models}
+\title[Running Title]{Collaboratively Testing the Validity of Neuroscientific Models}
 \author[\firstAuthorLast ]{\Authors}
@@
 \vspace{-65px}
-\caption{NeuronUnit overview. NeuronUnit is set of testing tools built upon the discipline-agnostic SciUnit framework. 
-NeuronUnit can in principle test arbitrary neurophysiology models using arbitrary data but we provide here an example using models described in NeuroML as part of the \textit{Open Source Brain Project} (OSB, \citep{gleeson_open_2012}, \url{http://www.opensourcebrain.org}), and single neuron electrophysiology data available as part of the NeuroElectro Project (Neuroelectro, \citep{tripathy_neuroelectro:_2012}, \url{http://neuroelectro.org}).}
+\caption{Paper overview.
+NeuronUnit is set of neurophysiology-specific testing tools built upon the domain-agnostic SciUnit framework.
+Scientists interested in testing neurophysiological models of particular systems, like the hippocampus, against relevant experimental data can construct test suites in a repository called \textit{hippocampus\_tests}.
+Models and data can be added directly or imported, via NeuronUnit, from model repositories like Open Source Brain (OSB) and data repositories like NeuroElectro.
+Testing tools and test repositories are developed collaboratively using Github.}
 \label{fig:sciunit_overview}\vspace{-10px}
@@
 \section{Validation Testing with \textit{SciUnit}}\label{sec:sciunit}
-\subsection{Example: The Quantitative Single Neuron Modeling Competition}
+\subsection{Example: The Quantitative Single Neuron Modeling Competition}\label{sec:example}
 \begin{figure}
@@
 For example, given observations from CA1 cells (not shown), we can instantiate a test as follows\todo{use iPython style In[0] notation?}:
-\begin{python}
-  CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
-\end{python}
+\begin{ipy}
+  In [0]: CA1_sc_test = SpikeCountTest(CA1_inputs, CA1_means, CA1_stds)
+\end{ipy}
 We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided.
@@
 To create a \emph{particular} linear model, a modeler provides parameter values, just as with test families:
-\begin{python}
-CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
-\end{python}
+\begin{ipy}
+  In [1]: CA1_linear_model_heuristic = LinearModel(3.0, 1.0)
+\end{ipy}
 Here, the parameters to the model were picked by the modeler heuristically, or based on externally-available knowledge. 
@@
 If training data is externally available, models that nevertheless are capable of being automatically trained (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
-\begin{python}
-CA1_linear_model_fit = LinearModel()
-CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
-\end{python}
+\begin{ipy}
+  In [2]: CA1_linear_model_fit = LinearModel()
+  In [3]: CA1_linear_model_fit.train_with_currents(CA1_training_in, CA1_training_out)
+\end{ipy}
 \begin{figure}
@@
 \subsection{Executing Tests} A test is executed against a model using the \verbx{judge} method:
-\begin{python}
-score = CA1_sc_test.judge(CA1_linear_model_heuristic)
-\end{python}
+\begin{ipy}
+  In [4]: score = CA1_sc_test.judge(CA1_linear_model_heuristic)
+\end{ipy}
 
@@
 
-\subsection{Test Suites and Score Matrices} A collection of tests intended to be run on the same model can be put together to form a test suite.
-The following is a test suite that could be used for a simplified version of the QSNMC, as described above:  
-\begin{python}
-CA1_suite = sciunit.TestSuite([CA1_sc_test, CA1_sl_test, CA1_sv_test, CA1_isi_test, CA1_ism_test])
-\end{python}
-Like a single test, a test suite is capable of judging one or more models. The result is a score matrix much like the one diagramed in Fig. \ref{fig:sciunit_overview}.
-\begin{python}
-scores = CA1_suite.judge([CA1_linear_model_heuristic, CA1_linear_model_fit])
-\end{python}
-A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools in development.
-For example, the score matrix might be visualized as a hyperlinked table inside an IPython notebook \todo{reference to ipython nb docs/paper?} containing the specification and execution of the test suite (Fig.
+\subsection{Test Suites and Score Matrices}\label{sec:visualization} A collection of tests intended to be run on the same model can be put together to form a test suite.
+The following test suite could be used for a simplified version of the QSNMC, as described in Sec. \ref{sec:example}:  
+\begin{ipy}
+  In [5]: CA1_suite = sciunit.TestSuite([CA1_overall_test, CA1_sc_test, CA1_sl_test, CA1_sv_test, CA1_isi_test, CA1_imi_test])
+\end{ipy}
+Like a single test, a test suite is capable of judging one or more models.
+The models must possess the union of the capabilities of the tests in a suite to be fully capable of running the suite, though partial results can also be generated.
+When a model cannot take a test because of a missing capability, the \texttt{NotApplicable} score is used (e.g.
+point processes cannot predict subthreshold voltages).
+The result is a \emph{score matrix}, like the one diagrammed in Fig. \ref{fig:sciunit_overview}.
+\begin{ipy}
+  In [6]: scores = CA1_suite.judge([ARX_model, AdEx1_model, aSRM_model, PP_model])
+\end{ipy}
+A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools.
+For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \todo{reference to ipython nb docs/paper?} (Fig.
 \ref{fig:scidash_matrix}).
-Such notebooks are stored in test repositories like \textit{hippocampus\_tests}.
 
@@
 \includegraphics[scale=0.55]{table-ipy.pdf}
+\vspace{-10px}
 \caption{A score matrix for a SciUnit test suite, visualized as a hyperlinked table inside an IPython notebook stored in a test repository like \textit{hippocampus\_tests}.}
 \label{fig:scidash_matrix}
-\vspace{-5px}
+\vspace{5px}
 \end{figure}
-\vspace{-10px}
-\leavevmode
 
-% Section 3.
+\section{A Collaborative Workflow}\label{sec:neuronunit_acitivities}
+The \textit{NeuronUnit} package contains a collection of test families and associated capabilities relevant to neurophysiology, such as those described in the previous section.
+It is collaboratively developed on Github (\url{http://github.com/scidash/neuronunit}).
+Scientists can use this package to easily create test suites tailored to specific neuronal systems of interest. 
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository containing an iPython notebook called \textit{hippocampus\_tests}, parameterized by data from the hippocampus.%, parameterizing them by relevant data from \textit{NeuroElectro}.
+%To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec. \ref{sec:neuroelectro}).
+
+Statisticians interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community.
+Rather than attempting to convince a large number of scientists socially that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community.
+Once the testing logic has been changed, all models can be immediately evaluated against the new metrics. 
+Scientists wishing to determine statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.
+
+To submit a new model for testing, a scientist can similarly fork the \textit{hippocampus\_tests} repository, add a new model to the relevant suite and test the model against available tests locally. 
+When satisfied with parameter choices, the scientist can submit a pull request to the common repository. 
+Once a model is in the repository, it will be evaluated on an ongoing basis against the latest accepted collections of tests, parameterized by the latest data, using the latest statistical best practices, without the participation of the original modeler, assuming only that the capabilities required by the tests stay stable.
+
+GitHub is an excellent platform for this kind of activity, and is becoming a widely-used tool for scientific collaboration, reproducibility, and transparency \citep{ram_git_2013}.  
+We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure.
+Using these common repositories, smaller groups of scientists interested in particular systems of interest will develop tests and models in test repositories like \textit{hippocampus\_tests}. 
+Each research community can develop suitable quality standards and processes for merging these pull requests.
+
+The end result of these efforts will be tables, like the one shown in Figure \ref{fig:scidash_matrix}, that allow scientists to understand, precisely, the state-of-the-art in their field. 
+We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \citep{omar_sciunit_2013}.
+\textit{SciDash} will also facilitate viewing test results without needing to clone test repositories and run tests locally for exploratory purposes, based on the \textit{iPython notebook} technology mentioned in Sec.
+\ref{sec:visualization}.
+We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec.
+2) and on the details of the bridge technologies, below.
+
 \section{Integrating With Neuroinformatics Tools and Infrastructure}\label{sec:neuronunit}
@@
 In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
-
-\subsection{A Collaborative Workflow}\label{sec:neuronunit_acitivities}
-The \textit{NeuronUnit} package contains a collection of test families and associated capabilities relevant to neurophysiology, such as the tests used in the QSNMC, and is collaboratively developed on GitHub (\url{http://github.com/scidash/neuronunit}).
-Scientists can use this package to easily create test suites tailored to specific neuronal systems of interest. 
-For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository containing an iPython notebook, as described above, called \textit{hippocampus\_tests}, parameterizing them by relevant data from \textit{NeuroElectro}.
-To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec. \ref{sec:neuroelectro}).
-
-Statisticians interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community.
-Rather than attempting to convince a large number of scientists socially that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community.
-Once the testing logic has been changed, all past models will be immediately evaluated against the new metrics. 
-Scientists wishing to determine statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.
-
-To submit a new model for testing, a scientist can similarly fork the \textit{hippocampus\_tests} repository, add a new model to the relevant suite using the simple \textit{NeuroML}-\textit{NeuronUnit} bridge described in Sec.
-\ref{sec:neuroml_models} and test the model against available tests locally.
-When satisfied with parameter choices, the scientist can submit the model to \textit{OSB} and use the common \textit{OSB-NeuronUnit} bridge, also described in Sec.
-\ref{sec:neuroml_models}, to refer to it, and finally submit a pull request to the common repository.
-Once a model is in the repository, it will be evaluated on an ongoing basis against the latest accepted collections of tests, which use accepted statistical best practices, without needing the participation of the original modeler, assuming that the capabilities that need to be exposed by models stay stable.
-GitHub is an excellent platform for this kind of activity, and is becoming a force for scientific collaboration, reproducibility, and transparency \citep{ram_git_2013}.
-
-We anticipate that other communities within neuroscience (and indeed, within science more broadly) will develop repositories similar to \textit{NeuronUnit} that provide a common, collaboratively-developed vocabulary of test families and capabilities relevant to their domain, and bridge with relevant standardization efforts and infrastructure.
-Using these common repositories, small groups of scientists interested in particular systems of interest will develop tests and models in test repositories like \textit{hippocampus\_tests}. 
-Each research community can develop suitable quality standards and processes for merging these pull requests.
-
-The end result of these efforts will be tables, like the one shown in Figure \ref{fig:sciunit_overview}, that allow scientists to understand, precisely, the state-of-the-art in their field.
-We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \citep{omar_sciunit_2013}.
-\textit{SciDash} will also facilitate viewing test results without needing to clone test repositories and run tests locally for exploratory purposes, based on the \textit{iPython notebook} technology mentioned in Sec.
-\ref{sec:visualization}.
-We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec.
-2) and on the details of the bridge technologies.
 
@@
 \end{python}
+\vspace{-15px}
 \caption{Working example of testing in \textit{NeuronUnit}}
 \label{fig:neuronunit_example}
-\vspace{-15px}
+
 \end{figure}

### 2013-11-30 NeurounitFrontiers/Paper.tex
Added ipython reference and fixed one sentence

@@
 To create a \emph{particular} spike count test, we instantiate this class with particular experimental observations. 
-For example, given observations from CA1 cells (not shown), we can instantiate a test as follows\todo{use iPython style In[0] notation?}:
+For example, given observations from CA1 cells (not shown), we can instantiate a test as follows:
 \begin{ipy}
@@
 A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools.
-For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \todo{reference to ipython nb docs/paper?} (Fig.
+For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \citep{perez_ipython_2007} (Fig.
 \ref{fig:scidash_matrix}).
@@
 \textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, parameterized by a path to a NeuroML model.  
-NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that are time-integrable point neurons (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}).
+NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that are time-integrable neurons with membrane potentials (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}).
 It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig.
@@
 (2) simulates it using NeuroConstruct; 
-(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTestDynamic}; \todo{Update this with current examples.py content}
+(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTestDynamic}; \todo{Update this with current examples.py content, and changed to ipython notebook notation}
 and (4) computes and prints a test score (Figure~\ref{fig:neuronunit_example}).

### 2013-11-30 NeurounitFrontiers/Paper.tex
Revised example script and added reference to bib

@@
 \usepackage{lineno}
+\usepackage{upquote}
 %\usepackage{natbib}
@@
 \begin{python}
-# Interface with neuroelectro.org to search for spike widths of CA1 Pyramidal cells. 
-reference_data = neuroelectro.NeuroElectroSummary(
-  neuron = {'name':'Hippocampus CA1 pyramidal cell'}, # Neuron type.  
-  ephysprop = {'name':'Spike Width'}) # Electrophysiological property name.
+reference_data = neuroelectro.NeuroElectroSummary( # Pooled experimental data from  neuroelectro.org. 
+  neuron = {'name':'Hippocampus CA1 pyramidal cell'}, # Neuron type according to NeuroLex ontology.  
+  ephysprop = {'name':'Spike Width'}) # Electrophysiological property name in same.
 reference_data.get_values()  # Get summary data for the above. 
-model = CA1PyramidalCellModel(population_name="CG_CML_0") # Initialize the model with some parameters.
-test = SpikeWidthTestDynamic( # Initialize the test.    
-	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics from the reference data
-	model_args = {'current':40.0}, # Somatic current injection in pA.  
+model = models.OSBModel( # Initialize the model.
+        'hippocampus', # Brain area.  
+        'CA1_pyramidal_neuron', # Neuron type name in OSB.  
+        'CA1PyramidalCell') # Model name (Migliore et al, 2005).
+test = SpikeWidthTest( # Initialize the test.    
+	reference_data = {'mean':reference_data.mean, 'std':reference_data.std}, # Summary statistics.
+	model_args = {'current':40.0*pA}, # Somatic current injection in pA.  
 	comparator = ZComparator), # A comparison class that implements a Z-score.  
-result = sciunit.judge(test,model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
-result.summarize() # Summarize the result.  
+record = test.judge(model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
+record.summarize() # Summarize the result.  
 \end{python}
 \vspace{-15px}
-\caption{Working example of testing in \textit{NeuronUnit}}
+\caption{Working example of testing in \textit{NeuronUnit}. Imports excluded for clarity.}
 \label{fig:neuronunit_example}
@@
 (2) simulates it using NeuroConstruct; 
-(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTestDynamic}; \todo{Update this with current examples.py content, and changed to ipython notebook notation}
+(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTest};
 and (4) computes and prints a test score (Figure~\ref{fig:neuronunit_example}).

### 2013-11-30 NeurounitFrontiers/Paper.tex
Added line breaks to tex file

@@
 \vspace{-65px}
-\caption{Paper overview.
-NeuronUnit is set of neurophysiology-specific testing tools built upon the domain-agnostic SciUnit framework.
+\caption{Paper overview. NeuronUnit is set of neurophysiology-specific testing tools built upon the domain-agnostic SciUnit framework. 
 Scientists interested in testing neurophysiological models of particular systems, like the hippocampus, against relevant experimental data can construct test suites in a repository called \textit{hippocampus\_tests}.
@@
 As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data.
-For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec.
-\ref{sec:neuronunit}).
-Particular tests, like \verbx{CA1_sc_test}, will be derived from these families in suite repositories (e.g.
-\verbx{HippocampusTests}, as shown in Figure \ref{fig:sciunit_overview}).
+For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec. \ref{sec:neuronunit}). 
+Particular tests, like \verbx{CA1_sc_test}, will be derived from these families in suite repositories (e.g. \verbx{HippocampusTests}, as shown in Figure \ref{fig:sciunit_overview}).
 
@@
 The models must possess the union of the capabilities of the tests in a suite to be fully capable of running the suite, though partial results can also be generated. 
-When a model cannot take a test because of a missing capability, the \texttt{NotApplicable} score is used (e.g.
-point processes cannot predict subthreshold voltages).
+When a model cannot take a test because of a missing capability, the \texttt{NotApplicable} score is used (e.g. point processes cannot predict subthreshold voltages). 
 The result is a \emph{score matrix}, like the one diagrammed in Fig. \ref{fig:sciunit_overview}.
@@
 A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools.  
-For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \citep{perez_ipython_2007} (Fig.
-\ref{fig:scidash_matrix}).
+For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \citep{perez_ipython_2007} (Fig. \ref{fig:scidash_matrix}).
 
@@
 \ref{sec:visualization}.
-We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec.
-2) and on the details of the bridge technologies, below.
+We leave details of \textit{SciDash} as future work, focusing this paper on the core testing methodology (Sec. 2) and on the details of the bridge technologies, below.
 
@@
 NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that are time-integrable neurons with membrane potentials (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}).
-It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig.
-\ref{fig:ca1_model}).
+It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig. \ref{fig:ca1_model}).
 
@@
 Experimentalists may not want to write tests derived from their data.  
-We anticipate four solutions: \textbf{First}, tests require no special data formatting; only a list of required  capabilities (for selecting eligible models), optional metadata (as run-time arguments), and a statistical data summary (for scoring tests) are required.
+We anticipate four solutions: 
+\textbf{First}, tests require no special data formatting; only a list of required  capabilities (for selecting eligible models), optional metadata (as run-time arguments), and a statistical data summary (for scoring tests) are required.
 A unit test is focused and does not require arbitrary computations on data. 
@@
 A community consensus will slowly emerge in the form of commonly-accepted test suites. 
-Such a community can judge which test version is most appropriate, i.e.
-what a model \textit{should} do -- this process documented via standard moderation techiniques used e.g.
-on GitHub.
+Such a community can judge which test version is most appropriate, i.e. what a model \textit{should} do -- this process documented via standard moderation techiniques used e.g. on GitHub. 
 This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).

### 2013-11-30 NeurounitFrontiers/Paper.tex
Revisions to sec 4

@@
 \begin{ipy}
-  In [5]: CA1_suite = sciunit.TestSuite([CA1_overall_test, CA1_sc_test, CA1_sl_test, CA1_sv_test, CA1_isi_test, CA1_imi_test])
+  In [5]: CA1_suite = sciunit.TestSuite([CA1_overall_test, CA1_sc_test, CA1_sl_test, CA1_sv_test, 
+              CA1_isi_test, CA1_imi_test])
 \end{ipy}
@@
 Scientists can use this package to easily create test suites tailored to specific neuronal systems of interest. 
-For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository containing an iPython notebook called \textit{hippocampus\_tests}, parameterized by data from the hippocampus.%, parameterizing them by relevant data from \textit{NeuroElectro}.
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository containing an IPython notebook called \textit{hippocampus\_tests}, parameterized by data from the hippocampus.%, parameterizing them by relevant data from \textit{NeuroElectro}.
 %To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec. \ref{sec:neuroelectro}).
@@
 \section{Integrating With Neuroinformatics Tools and Infrastructure}\label{sec:neuronunit}
-In the examples in the previous section, tests were generated from data explicitly, and models implemented capabilities directly. 
-In many fields, however, both models and data are available from existing  repositories in standardized formats. 
-In this section, we will show how to leverage this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
+In the examples in the previous sections, tests were provided data explicitly, and models implemented capabilities directly. 
+In many fields, however, both models and data are available from existing  community resources in standardized formats. 
+In this section, we will show how to use this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
 In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
@@
 	comparator = ZComparator), # A comparison class that implements a Z-score.  
-record = test.judge(model) # (1) Check capabilities, (2) take the test, (3) generate a score and validate it, (4) bind the score to model/test combination. 
-record.summarize() # Summarize the result.  
+score = test.judge(model)
 \end{python}
@@
 Currently, up to 27 electrophysiological properties are available for 93 cell types, gathered from over 2000 single pieces of published data extracted from tables in published papers. 
-We have made it easy to parameterize \textit{NeuronUnit} tests using data extracted from the NeuroElectro API. 
+We have made it easy to parameterize the test families in \textit{Neuron\-Unit}  using data extracted from the NeuroElectro API. 
 Tests can be based upon data from single journal articles, or from ensembles of articles with a common theme (e.g. about a particular neuron type). 
-The former is illustrated in Figure \ref{fig:neuronunit_example}. 
-Associated statistics of that data (e.g mean, standard error, and sample size) are attached and enable judgement of model output according to a chosen scoring mechanism. 
-While NeuroElectro alone cannot judge all model aspects, it can serve to validate basic features of many neurophysiology models, such as resting membrane potential, action potential width, after-hyperpolarization amplitude, etc.
-As NeuroElectro is the only publicly curated source of such data, it represents a key component for \textit{NeuronUnit} test constuction.
+The latter is illustrated in Figure \ref{fig:neuronunit_example}, on lines 1-4.
+Once data has been retrieved from NeuroElectro, associated statistics (e.g.
+mean, standard error and sample size) can be extracted to parameterize tests (e.g.
+a test of spike widths on line 10).
+Data from NeuroElectro is can be used to validate a variety of basic electrophysiological features of neuron models, including spike width, resting membrane potential, after-hyperpolarization amplitude, etc.
+As NeuroElectro is the only publicly curated source of such data, it represents a key resource facilitating test construction.
 
-\subsection{Models from NeuroML}\label{sec:neuroml_models}
+\subsection{Models from NeuroML and OpenSourceBrain}\label{sec:neuroml_models}
 NeuroML is a standardized model description language for neuroscience \citep{gleeson_neuroml:_2010}. 
 It allows many neurophysiological and neuroanatomical models to be described in a simulator-independent fashion.
-Because NeuroML is an XML specification, model descriptions can be validated for correctness and queried for model properties and components.
-We use these facilities to expose capabilities automatically.
-It has proven ideal for model sharing, curation, and for answering both questions about \textit{what a model does} and \textit{how to do it} programatically.
+Some simulators, notably the popular NEURON package\todo{cite NEURON}, can seamlessly export model specifications in the NeuroML format.
+Because NeuroML is an XML specification, model descriptions can be verified for correctness and queried for model properties and components.
+We leverage the latter facilities to expose model capabilities automatically.
+%NeuroML has proven ideal for model sharing, curation, and for answering both questions about \textit{what a model does} and \textit{how to do it} programatically.
 
-NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off simulation to supported simulators. 
-\textit{NeuronUnit} offers a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel}, parameterized by a path to a NeuroML model.  
-NeuroML can describe a wide range of models, but \verbx{NeuroConstructModel} currently supports only those that are time-integrable neurons with membrane potentials (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential}).
+NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off them off to a supported simulator for execution.
+\textit{NeuronUnit} provides a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel} that takes a path to a NeuroML model as a parameter.  
+NeuroML can describe a wide range of models, but our \verbx{NeuroConstructModel} class currently supports only  time-integrable point neurons (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential} at minimum).
 It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig. \ref{fig:ca1_model}).
@@
 class CA1PyramidalCellModel(NeuroConstructModel):
-	"""CA1 Pyramidal Cell model from Open Source Brain."""
-	def __init__(self,**kwargs):
+	"""CA1 Pyramidal Cell model in the local file system."""
+	def __init__(self):
 		project_path = neuroconstruct.get_path("hippocampus","CA1_pyramidal_neuron","CA1PyramidalCell","neuroConstruct")
-		NeuroConstructModel.__init__(self,project_path,**kwargs)
+		NeuroConstructModel.__init__(self,project_path)
 \end{python}

### 2013-11-30 NeurounitFrontiers/Paper.tex
cyrus done with sec 4

@@
 Data from NeuroElectro is can be used to validate a variety of basic electrophysiological features of neuron models, including spike width, resting membrane potential, after-hyperpolarization amplitude, etc.
+\todo{write a sentence or two about its use of the NeuroLex repository}
 As NeuroElectro is the only publicly curated source of such data, it represents a key resource facilitating test construction.
@@
 It allows many neurophysiological and neuroanatomical models to be described in a simulator-independent fashion.
-Some simulators, notably the popular NEURON package\todo{cite NEURON}, can seamlessly export model specifications in the NeuroML format.
+Some simulators, notably the popular NEURON package (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), can seamlessly export model specifications as NeuroML.
 Because NeuroML is an XML specification, model descriptions can be verified for correctness and queried for model properties and components.
@@
 NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off them off to a supported simulator for execution.
+A number of popular simulators support execution of NeuroML models, including NEURON, GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}).
 \textit{NeuronUnit} provides a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel} that takes a path to a NeuroML model as a parameter.  
-NeuroML can describe a wide range of models, but our \verbx{NeuroConstructModel} class currently supports only  time-integrable point neurons (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential} at minimum).
-It can be instantiated directly or subclassed (useful if additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig. \ref{fig:ca1_model}).
+NeuroML can describe a wide range of models, but our \verbx{NeuroConstructModel} class currently supports only  time-integrable point neurons (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential} at minimum; see Sec.
+\ref{sec:neurotools}).
+It can be instantiated directly or subclassed (useful when additional capabilities need to be manually exposed, for example) to generate a model suitable for testing (Fig.
+\ref{fig:ca1_model}).
+The underlying simulator can be configured (defaulting to ??\todo{What does it default to in our code??}; not shown).
+In this example, we simply create a model based on a NeuroML model of CA1 cells downloaded from OpenSourceBrain to the local file system (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}).
 
 \textit{OSB} curates many models described in NeuroML. 
-OSB-curated projects are converted from their native format into NeuroML, and run on major neural simulators such as NEURON (\cite{carnevale_neuron_2006}, \url{http://www.neuron.yale.edu/neuron}), GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}).
-Concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files or published figures) is reported for each model. 
-Thus, OSB is an excellent source of models that, in addition to being open source, are sufficiently described to enable validation. 
-The hippocampal CA1 pyramidal cell is commonly modeled, and we implement one such model hosted on OSB (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}) by simply declaring a \verbx{CA1PyramidalCellModel} class, inheriting from \verbx{NeuroConstructModel}.
-This basic implementation simply ``wraps'' the components of the existing model, with simulator interaction taken care of by \verbx{NeuroConstructModel} methods; 
-thus, only the code shown in Fig. \ref{fig:ca1_model} is required. 
-All OSB models, and indeed any NeuroML model, can be tested similarly.
+OSB-curated projects have been converted from their native format into NeuroML.
+To ensure that the NeuroML model is faithful to the original simulation, OSB verifies concordance between model output (beginning with the NeuroML description) and reference output (from native simulator source files or published figures) for each model.
+Thus, OSB is an excellent source of models that, in addition to being open source, are known to be accurately described.
+This also highlights the distinction between \emph{verification} activities, performed by OSB to ensure that a model description operates correctly, and \emph{validation} activites, performed using SciUnit to check the model's predictions against data.
+Both are important activities.
 
-Spanning a range of scales and original development environments, all OSB models are formally described using NeuroML, as are all model components and sub-components, such as cells, ion channels, calcium stores, etc.
-These models are regularly executed on OSB servers to ensure that their output remains consistent as they are updated. 
-Therefore, OSB can confirm that they \textit{do} work, while linked journal articles, on-site wiki, and code inspection can establish \textit{how} they work. 
-However, there is no mechanism for establishing \textit{how well} they work, i.e. how well the models accord with data. 
-\textit{NeuronUnit} fills this gap by helping OSB (and the larger neuroscience community) assess models using data-driven tests. 
-\textit{SciUnit} can be applied similarly to other neuroscience (or biology) sub-disciplines using \textit{NeuronUnit} analogues written by the corresponding communities.
+To directly test a model in OSB, we can skip the step of downloading it the local file system or adding it to the test repository and simply download it from OSB directly by using the \verbx{OSBModel} class, shown on lines 5-8 of Figure \ref{fig:neuronunit_example}.
+
+%Spanning a range of scales and original development environments, all OSB models are formally described using NeuroML, as are all model components and sub-components, such as cells, ion channels, calcium stores, etc.
+%These models are regularly executed on OSB servers to ensure that their output remains consistent as they are updated. 
+%Therefore, OSB can confirm that they \textit{do} work, while linked journal articles, on-site wiki, and code inspection can establish \textit{how} they work. 
+%However, there is no mechanism for establishing \textit{how well} they work, i.e. how well the models accord with data. 
+%\textit{NeuronUnit} fills this gap by helping OSB (and the larger neuroscience community) assess models using data-driven tests. 
+%\textit{SciUnit} can be applied similarly to other neuroscience (or biology) sub-disciplines using \textit{NeuronUnit} analogues written by the corresponding communities.
 
@@
 \end{python}
-\vspace{-5px}
+\vspace{-15px}
 \caption{A model class corresponding to a CA1 Pyramidal Cell model from Open Source Brain}
 \label{fig:ca1_model}
-\vspace{-15px}
+\vspace{-10px}
 \end{figure}
 
-\subsection{Capabilities from NeuroTools}
+\subsection{Data Formats and Capabilities from NeuroTools}\label{sec:neurotools}
 NeuroTools (\url{http://neuralensemble.org/NeuroTools}) is a Python library supporting tasks associated with analysis of neural data (or model output), such as membrane potential time series, spike trains, etc.
@@
 
-We use NeuroTools to implement \textit{SciUnit} capabilities in \textit{NeuronUnit}. 
+We use NeuroTools to implement a variety of \textit{SciUnit} capabilities in \textit{NeuronUnit}. 
 For example, an \verbx{AnalogSignal} object (e.g. a membrane potential time series) from NeuroTools has a threshold detection method that returns a NeuroTools \verbx{SpikeTrain} object. 
-Meanwhile, a \textit{NeuronUnit} \verbx{HasSpikeTrain} Capability requires that the method \verbx{getSpikeTrain} be implemented. 
-\verbx{NeuroConstructModel} does so by placing the object method \verbx{AnalogSignal.threshold_detection} inside \verbx{getSpikeTrain}. 
-Many such NeuroTools objects are similarly exchanged between \verbx{NeuroConstructModel} methods. 
-This simplifies test writing, since basic model output properties are obtained trivially using the methods of NeuroTools objects, and these NeuroTools objects are easily extracted from model output, especially when the models subclass \verbx{NeuroConstructModel}.
+The \textit{NeuronUnit} capability \verbx{HasSpikeTrain}  requires that a method named \verbx{get_spike_train} be implemented, returning a \verbx{SpikeTrain} object. 
+\verbx{NeuroConstructModel} implements this by default by calling the NeuroTools method \verbx{AnalogSignal.threshold_detection}, retrieving the membrane potential by calling the \verbx{get_membrane_potential} method implemented by the \verbx{HasMembranePotential} capability that all supported NeuroML models implement.
+NeuroTools is used in this manner to implement a wide variety of capabilities for \verbx{NeuroConstructModel}s, without requiring that the model developer do so explicitly (though they can overwrite these if they wish).
+This also helps scientists by directing them to a set of common utility functions and data formats that they can use, knowing that they are accepted by the community around NeuronUnit.\todo{do you have a list of capabilities that neuroconstructmodels can automatically implement?}
 

### 2013-12-01 NeurounitFrontiers/Paper.tex
cyrus done with sec 4
updated pipeline section

@@
 	model_args = {'current':40.0*pA}, # Somatic current injection in pA.  
-	comparator = ZComparator), # A comparison class that implements a Z-score.  
+	comparator = ZComparator), # the scoring metric can be part of the test parameters 
 score = test.judge(model)
+print score.summary
 \end{python}
@@
 \vspace{-15px}
-\caption{A model class corresponding to a CA1 Pyramidal Cell model from Open Source Brain}
+\caption{A model class corresponding to a CA1 Pyramidal Cell model downloaded locally from Open Source Brain}
 \label{fig:ca1_model}
@@
 \verbx{NeuroConstructModel} implements this by default by calling the NeuroTools method \verbx{AnalogSignal.threshold_detection}, retrieving the membrane potential by calling the \verbx{get_membrane_potential} method implemented by the \verbx{HasMembranePotential} capability that all supported NeuroML models implement.
-NeuroTools is used in this manner to implement a wide variety of capabilities for \verbx{NeuroConstructModel}s, without requiring that the model developer do so explicitly (though they can overwrite these if they wish).
+NeuroTools is used in this manner to implement a wide variety of capabilities for \verbx{NeuroConstructModel}s, without requiring that the modeler do so explicitly (though they can overwrite these if they wish).
 This also helps scientists by directing them to a set of common utility functions and data formats that they can use, knowing that they are accepted by the community around NeuronUnit.\todo{do you have a list of capabilities that neuroconstructmodels can automatically implement?}
@@
 \ref{sec:neuronunit} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal.
-In the \textit{NeuronUnit} repository (\url{http://github.com/scidash/neuronunit}) is a runnable script (\textit{examples.py}) demonstrating a complete testing pipeline. 
-It (1) selects an OSB model; 
-(2) simulates it using NeuroConstruct; 
-(3) tests the widths of the resulting action potentials, extracted and computed using NeuroTools, against NeuroElectro data downloaded on-the-fly, using a \textit{NeuronUnit} test class called \verbx{SpikeWidthTest};
-and (4) computes and prints a test score (Figure~\ref{fig:neuronunit_example}).
+In the \textit{hippocampus\_tests} repository (\url{http://github.com/scidash/hippocampus\_tests}) is an IPython notebook (\textit{ca1\_suite.ipynb}) demonstrating a complete test suite similar to the \emph{ad hoc} suite used by the QSNMC.
+Our tests are parameterized by data drawn both from NeuroElectro and entered manually, as well as models drawn both from OSB and implemented manually.
+New tests, data and models can be added by contributing to these resources and/or submitting pull requests; we anticipate handing control over merging these requests to prominent members of the hippocampal modeling community once our interface stabilizes and this paper is published.
+This repository represents a template that other groups of systems neuroscientists can use for their system of interest, and a starting point for other research areas in neuroscience, and science more broadly.
 

### 2013-12-01 NeurounitFrontiers/Paper.tex
Updated participation sections

@@
 Our tests are parameterized by data drawn both from NeuroElectro and entered manually, as well as models drawn both from OSB and implemented manually.
-New tests, data and models can be added by contributing to these resources and/or submitting pull requests; we anticipate handing control over merging these requests to prominent members of the hippocampal modeling community once our interface stabilizes and this paper is published.
+New tests, data and models can be added by contributing to these community resources and/or submitting pull requests; we anticipate handing control over merging these requests to members of the hippocampal modeling community once our interface stabilizes and this paper is published.
 This repository represents a template that other groups of systems neuroscientists can use for their system of interest, and a starting point for other research areas in neuroscience, and science more broadly.
 
-\subsection{Creating New Models, Capabilities, and Tests}
+\subsection{Manually Creating New Models, Capabilities, and Tests}
 \textit{NeuronUnit} provides base classes to enable rapid generation of models, capabilities, and tests for neurophysiology data. 
@@
 a Test could be initialized using empirical spike rates collected in the lab.  
-While this does not meet our idealized vision of development and testing, in practice this may be a common scenario.
+While this does not meet our idealized vision of collaborative development and testing, in practice this may be a common scenario.
 
 \subsection{Participation from Modeling Communities}
-Modelers may not want to expose model capabilities, a requirement of test-taking.  
-We anticipate four solutions: \textbf{First}, interfacing a model to \textit{SciUnit} requires only implementing selected model capabilities. 
-Often this means identifying native model procedures that satisfy a capability, and wrapping their functionality. 
-This can require as little as one line of code. 
-Importantly, the modeler is not required to expose or rewrite any model flow control. 
-\textbf{Second}, we support multiple environments automatically by using NeuroML \citep{gleeson_neuroml:_2010}, and other simulator-independent model descriptions are possible for other domains. 
-Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator (\cite{carnevale_neuron_2006}), this functionality is already implemented in use.
+Modelers may not want to expose their models to tests via capabilities, a requirement for test-taking.  
+We anticipate four solutions: \textbf{First}, we will emphasize to the community that wrapping existing model code that satisfy a capability is quite simple, requiring as little as one line of code. 
+Importantly, the modeler is not required to expose or rewrite any internal model flow control in almost all cases. 
+\textbf{Second}, we support multiple simulation environments automatically by using NeuroML \citep{gleeson_neuroml:_2010}, and other simulator-independent model descriptions are possible for other domains.
+Automated generation of NeuroML from native model source code is in development (Gleeson, personal communication); for the popular NEURON simulator (\cite{carnevale_neuron_2006}), this functionality is already implemented and in use.
 This minimizes modeler effort for a large (at least 1000, \url{http://www.neuron.yale.edu/neuron/node/69}) and growing number of neuronal models. 
 \textbf{Third}, modelers have an incentive to demonstrate publicly their models' validity. 
-Participation in public modeling competitions demonstrates this incentive. 
-\textbf{Fourth}, modelers have an incentive to use \textit{SciUnit} during development (see TDD, above) to ensure that ongoing development preserves correspondence between model and data. 
-A popular test suite can represent a ``gold standard'' by which progress during development is judged.
+Participation in public modeling competitions demonstrates that this incentive can draw several participants.
+We plan to assist with such competitions by advocating for use of SciUnit as the underlying technical substrate in the future.
+\textbf{Fourth}, modelers have an incentive to use \textit{SciUnit} during development (see TDD, Sec.
+\ref{sec:introduction}) to ensure that ongoing development preserves correspondence between model and data.
+A popular test suite can represent a ``gold standard'' by which progress during development is judged, even within a single project.
 
@@
 We anticipate four solutions: 
-\textbf{First}, tests require no special data formatting; only a list of required  capabilities (for selecting eligible models), optional metadata (as run-time arguments), and a statistical data summary (for scoring tests) are required.
-A unit test is focused and does not require arbitrary computations on data. 
-For example, suppose intracellular current injection evokes 100 action potentials, the width of which is of interest. 
-Writing the test consists of selecting \verbx{ReceivesCurrent} and \verbx{ProducesActionPotentialShape} capabilities (one line of code each), computing the mean and variance of action potential widths (one line of code), specifying current injection parameters, e.g.
-amplitude and duration (two lines of code), and selecting a scoring mechanism from \verbx{sciunit.scores}, e.g.
-(colloquially) ``Must be $<$ 1 standard deviation of the mean'' (one line of code).
-This example can be found in \verbx{NeuronUnit.tests.SpikeWidthTest}; heavy-lifting is done by the interface.
-\textbf{Second}, data-sharing is becoming accepted, and test-writing can be distributed across scientists, including non-experimentalists with other aims such as analysis or modeling. 
-\textbf{Third}, many tests can be automatically generated using NeuronUnit, and the continued emergence of data-aggregation initiatives such as NeuroElectro will expand these possibilities. 
-\textbf{Fourth}, an incentive to write tests for one's data exists: the ability to identify models that give the data clear context and impact.
+\textbf{First}, we will emphasize that tests do not require releasing entire datasets; a test consists only of a list of required  capabilities (for selecting eligible models), and sufficient statistics suitable for executing the scoring logic.
+This can simply be means and standard deviations in many cases, such as the examples in this paper.
+Most scoring logic will consist of a few calls to capability methods followed by a standard statistical test, which can be implemented once in \textit{SciUnit} or a discipline-specific repository like \textit{NeuronUnit}.
+\textbf{Second}, data-sharing is becoming accepted.
+If data is available from a community repository, as many granting agencies are increasingly requiring, then tests can often be generated automatically using bridges developed collaboratively by the community.
+\textbf{Third}, an incentive to write tests for one's data exists: the ability to identify models that give the data clear context and impact.
+If a new piece of data invalidates a widely-accepted model, this can be cited in publications.
+\textbf{Fourth}, one can compare new data against existing data by simply creating a \emph{data-derived model} that directly generates ``predictions'' by draws from the new dataset directly.
+Thus the model validation procedures described in this paper can also be used to perform data validation -- that is, check the goodness-of-fit of new data with old data.
 

### 2013-12-01 NeurounitFrontiers/Paper.tex
Updated 5.5

@@
 The diversity of topics in biology is vast. 
-\textbf{First}, we address this by providing an interface allowing modelers to express specific capabilities.  
-This capability set determines the range of eligible tests.  Scale hierarchies are embedded in capability inheritance. 
-For example, \verbx{HasActionPotentials} inherits from \verbx{HasNeurons}, and \verbx{HodgkinHuxley} inherits from \verbx{VoltageGated}. 
-Thus, incompatibility of a test-requiring-action-potentials for a model-lacking-neurons is known without explicit tagging. 
+\textbf{First}, we address this by providing an interface allowing modelers to flexibly express precisely how a model should be interfaced with using  capabilities.
+Capabilities can inherit from and call into each other.
+This is more flexible than the fixed interfaces used in existing modeling competitions or domains like machine learning where only a few interfaces are of interest (e.g.
+classifiers).
 \textbf{Second}, NeuroML naturally addresses diversity of scales because it is organized hierarchically, in ``levels.''  
@@
 \textbf{Third}, cross-level testing can use ``Representional Similarity Analysis'' (RSA) \citep{kriegeskorte_representational_2008}, requiring only that a model respond to defined inputs (e.g.
-stimuli).
+stimuli)\todo{I have no idea what this means}.
 A ``similarity matrix'' for input responses defines a unique model signature, and can serve as intermediate test output. 

### 2013-12-01 NeurounitFrontiers/Paper.tex
Updated through sec 5

@@
 
-\verbx{judge} is a stock \verbx{sciunit.Test} method that proceeds by first checking that the provided model implements all required capabilities. 
+\verbx{judge} is a built-in method of \verbx{sciunit.Test} that proceeds by first checking that the provided model implements all required capabilities. 
 It then calls the test's author-implemented \verbx{_judge} method (note leading underscore) to produce a score.
+A score is an instance of \verbx{sciunit.Score} and must implement an ordering, to facilitate sorting of scores (e.g.
+in tabular form, described below).
 A reference to the test and model are added to the score for convenience (accessible via the \verbx{test} and \verbx{model} attributes, respectively), before it is returned.
@@
 \begin{figure}%[18]{r}{1\textwidth}
+\vspace{-5px}
 \centering
@@
 \label{fig:scidash_matrix}
-\vspace{5px}
+\vspace{-5px}
 \end{figure}
@@
 
-Statisticians interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community.
+Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and 
+identification and correction of flawed methodology is becoming increasingly common (\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010}).
+Statisticians and other scientists interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community.
 Rather than attempting to convince a large number of scientists socially that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community.
@@
 
-\subsection{Arbitrary Scoring Criteria for Tests}
-A test first assesses goodness-of-fit, and applies a normalization (e.g. pass/fail, 0.0-1.0) to generate a score. 
-Arbitrary choices at both stages may benefit some models over others. 
-\textbf{First}, however, rank-ordering is constant across many goodness-of-fit metrics, meaning that choice of metric will rarely cause an otherwise passing model to fail and vice versa. 
-For example, given a data mean and variance, ordering model output by Z-score or p-value will yield the same relative ranking of models. 
-Indeed, rank ordering of models may prove more valuable than test scores themselves. 
-\textbf{Second}, suite repositories should be open, so tests can be cloned and new statistical choices implemented. 
-Statistics as applied to neuroscience have been notoriously ``fast and loose''; 
-identification and correction of flawed methodology is becoming increasingly common (\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010}, \url{http://prefrontal.org/files/posters/Bennett-Salmon-2009.jpg}), and is accelerated by an open framework.
-The validation criteria is made explicit in the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model. 
-Validation criteria are subject to debate (indeed, the QSNMC criteria changed between 2007 and 2008 due to such debates), and neuroscientists who wish to promote different criteria need only derive alternative tests.
-A community consensus will slowly emerge in the form of commonly-accepted test suites. 
-Such a community can judge which test version is most appropriate, i.e. what a model \textit{should} do -- this process documented via standard moderation techiniques used e.g. on GitHub. 
-This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).
+%\subsection{Arbitrary Scoring Criteria for Tests}
+%A test first assesses goodness-of-fit, and applies a normalization (e.g. pass/fail, 0.0-1.0) to generate a score. 
+%Arbitrary choices at both stages may benefit some models over others. 
+%\textbf{First}, however, rank-ordering is constant across many goodness-of-fit metrics, meaning that choice of metric will rarely cause an otherwise passing model to fail and vice versa. 
+%For example, given a data mean and variance, ordering model output by Z-score or p-value will yield the same relative ranking of models. 
+%Indeed, rank ordering of models may prove more valuable than test scores themselves. 
+%\textbf{Second}, suite repositories should be open, so tests can be cloned and new statistical choices implemented. 
+%Statistics as applied to neuroscience have been notoriously ``fast and loose''; 
+%identification and correction of flawed methodology is becoming increasingly common (\cite{button_power_2013,kriegeskorte_circular_2009,galbraith_study_2010}, \url{http://prefrontal.org/files/posters/Bennett-Salmon-2009.jpg}), and is accelerated by an open framework.
+%The validation criteria is made explicit in the specification of a test, so modelers need not guess which criteria are being used to validate or invalidate their model.  
+%A community consensus will slowly emerge in the form of commonly-accepted test suites. 
+%Such a community can judge which test version is most appropriate, i.e. what a model \textit{should} do -- this process documented via standard moderation techiniques used e.g. on GitHub. 
+%This process can be made even more visible by storing the output of test runs using Sage or IPython worksheets, or through optional database backends such as in the Sumatra lab notebook for simulation and analysis (\cite{sumatra_davison_2012}, \url{http://neuralensemble.org/sumatra}).
 
-\subsection{Reliability of Data Underlying Tests}
-Unreliable data can undermine model validation. 
-\textbf{First}, the community must evaluate experimental design and methods, discounting data produced using questionable techniques. 
-Open source version control services such as GitHub support community moderation, permitting users to comment on tests, indicating their concerns. 
-Suite repository popularity can reflect consensus. 
-Experimental metadata also constrain a test's relevance, so test writers should select data with metadata appropriate to the system being modeled, and attach the metadata to resulting test scores. 
-Using the NeuroElectro API, for example, it is possible to select only data corresponding to specific experimental conditions, for example recording electrode type.  
-Metadata can also be expressed as Capabilities, e.g. \verbx{At37Degrees} or \verbx{Calcium3mM}; and tests can require that models express them. 
-Such capabilities require no implementation, so the model definition must only inherit them. 
-\textbf{Second}, models cannot perfectly reproduce data that is itself a random draw from a ``true'' distribution. 
-Uncertainty in data must be made explicit, by asking how well a data set validates its own experimental replications \citep{kriegeskorte_representational_2008}. 
-The degree of such ``self-validation'' represents the upper limit of what a model can be expected to achieve, and should represent a ``perfect'' score.
+%\subsection{Reliability of Data Underlying Tests}
+%Unreliable data can undermine model validation. 
+%\textbf{First}, the community must evaluate experimental design and methods, discounting data produced using questionable techniques. 
+%Open source version control services such as GitHub support community moderation, permitting users to comment on tests, indicating their concerns. 
+%Suite repository popularity can reflect consensus. 
+%Experimental metadata also constrain a test's relevance, so test writers should select data with metadata appropriate to the system being modeled, and attach the metadata to resulting test scores. 
+%Using the NeuroElectro API, for example, it is possible to select only data corresponding to specific experimental conditions, for example recording electrode type.  
+%Metadata can also be expressed as Capabilities, e.g. \verbx{At37Degrees} or \verbx{Calcium3mM}; and tests can require that models express them. 
+%Such capabilities require no implementation, so the model definition must only inherit them. 
+%\textbf{Second}, models cannot perfectly reproduce data that is itself a random draw from a ``true'' distribution. 
+%Uncertainty in data must be made explicit, by asking how well a data set validates its own experimental replications \citep{kriegeskorte_representational_2008}. 
+%The degree of such ``self-validation'' represents the upper limit of what a model can be expected to achieve, and should represent a ``perfect'' score.
 
@@
 All things being equal, simpler models are better. 
-Model complexity has many definitions \citep{mccabe_complexity_1976}, including: 
+Model complexity, though fundamentally a subjective measure, has many correlates \citep{mccabe_complexity_1976}, including: 
 1) model length; 2) memory use; 3) CPU load; 4) \# of capabilities. 
-Future \textit{SciUnit} tools will report the model validity vs complexity tradeoff in tabular form (e.g.
-Figure \ref{fig:scidash_matrix}), and in a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot.
+Future \textit{SciUnit} tools will analyze these factors, and may include tools for gathering community ratings about subjective factors like complexity.
+As a result of these enhancements, scientists will be able to visualize the model validity vs complexity tradeoff in tabular form (e.g.
+as a column in Figure \ref{fig:scidash_matrix}), or as a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot.
 The set of models which \textit{dominate} all others, i.e.
-that have the highest validity for a given complexity, can be represented as a ``frontier'' in such a scatter plot, a visualization familiar from the symbolic regression package Eureqa \citep{schmidt_distilling_2009}.
+that have the highest validity for a given complexity, can be represented as a ``frontier'' in such a scatter plot (e.g.
+as used in the symbolic regression package Eureqa \citep{schmidt_distilling_2009}).
 

### 2013-12-01 NeurounitFrontiers/Paper.tex
Nearly final revisions

@@
 \def\Address{$^{1}$School of Life Sciences, Arizona State University, Tempe, AZ, USA \\
-$^{2}$Dept. of Computer Science, Carnegie Mellon University, Pittsburgh, PA, USA  }
+$^{2}$Dept. of Computer Science, Carnegie Mellon University, Pittsburgh, PA, USA \\
+The authors contributed equally. }
 % The Corresponding Author should be marked with an asterisk
@@
 \label{sec:introduction}
+\subsection{The problem: what do models do and how well do they do it?}
 Neuroscientists construct quantitative models to coherently explain experimental observations of neurons, circuits, brain regions and behavior. 
@@
 
+\subsection{The solution: unit testing for models}
 Professional software developers face similar issues \citep{omar_sciunit_2013}. 
@@
 
+\subsection{The implementation: SciUnit and NeuronUnit}
 Each of these examples has leveraged \emph{ad hoc} infrastructure to support model validation. 
@@
   parameters:
-    inputs: list of numpy arrays containing input currents (nA)
+    inputs: list of numpy arrays containing input currents (pA)
     means, stds: lists of observed means and standard deviations, one per input
@@
     return sciunit.PValue(pooled_p, related_data={
-      "inputs": inputs, "counts": counts, "obs_means": means, "obs_stds": stds
+      "inputs": inputs, "counts": counts, "empirical_means": means, "empirical_stds": stds
       })
@@
 We emphasize the crucial distinction between the \textit{class} \verbx{SpikeCountTest}, which defines a \emph{parameterized family} of validation tests, and the particular \textit{instance} \verbx{CA1_sc_test}, which is an individual validation test because the necessary parameters, derived from data, have been provided.
-As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience so that test generation for a particular system of interest will often require simply instantiating a previously-developed family with particular experimental parameters and data.
+As we will describe below, we expect communities to build repositories of such families capturing the criteria used in their subfields of neuroscience. 
+Test generation for a particular system of interest will then often require simply instantiating a previously-developed family with particular experimental parameters and data. 
 For single-neuron test families like \verbx{SpikeCountTest}, we have developed such a library, called \textit{NeuronUnit} (\url{http://github.com/scidash/neuronunit}) (Sec. \ref{sec:neuronunit}). 
-Particular tests, like \verbx{CA1_sc_test}, will be derived from these families in suite repositories (e.g. \verbx{HippocampusTests}, as shown in Figure \ref{fig:sciunit_overview}).
+Particular tests, like \verbx{CA1_sc_test}, will be derived from these families in suite repositories (e.g. \verbx{hippocampus_tests}, as shown in Figure \ref{fig:sciunit_overview}).
 
@@
 
-The remainder of the \verbx{_judge} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.PValue}, a subclass of \verbx{sciunit.Score} that is included with \textit{SciUnit}.
+The remainder of the \verbx{_judge} method implements the goodness-of-fit metric described above, returning an instance of \verbx{sciunit.scores.PValue}, a subclass of \verbx{sciunit.Score} that is included with \textit{SciUnit}.
 In addition to the $p$-value itself, the returned score object also contains metadata, via the \verbx{related_data} parameter, for scientists who may wish to examine the result in more detail later. 
-In this case we save the input currents, the model outputs and the observed means and standard deviations (line 24).
+In this case we save the input currents, the model outputs and the empirical (experimental) means and standard deviations (line 24).
 
@@
 Fig. \ref{fig:rate_test} does not include a training phase. 
-If training data is externally available, models that nevertheless are capable of being automatically trained (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
+If training data is externally available, models capable of being automatically trained (like \verb|LinearModel|) can simply be trained explicitly by calling the capability method just like any other Python method:
 \begin{ipy}
@@
 \subsection{Test Suites and Score Matrices}\label{sec:visualization} A collection of tests intended to be run on the same model can be put together to form a test suite.
-The following test suite could be used for a simplified version of the QSNMC, as described in Sec. \ref{sec:example}:  
+The following test suite could be used for a simplified version of the QSNMC, as described in sec. \ref{sec:example}:  
 \begin{ipy}
@@
 Scientists can use this package to easily create test suites tailored to specific neuronal systems of interest. 
-For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository containing an IPython notebook called \textit{hippocampus\_tests}, parameterized by data from the hippocampus.%, parameterizing them by relevant data from \textit{NeuroElectro}.
+For example, scientists interested specifically in testing models of cells in the hippocampus would use \textit{NeuronUnit} to create tests in a GitHub repository called \textit{hippocampus\_tests}, containing an IPython notebook and parameterized by empirical data from the hippocampus.%, parameterizing them by relevant data from \textit{NeuroElectro}.
 %To make this easy, \textit{NeuronUnit} contains \emph{bridge functions} for retrieving data and generating tests from \textit{NeuroElectro} directly (Sec. \ref{sec:neuroelectro}).
@@
 Statisticians and other scientists interested in improving how goodness-of-fit is measured can simply fork the \textit{NeuronUnit} repository, modify the logic in the relevant test families and submit a \emph{pull request} for evaluation by the community.
-Rather than attempting to convince a large number of scientists socially that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community.
+Rather than attempting to persuade a large number of scientists that the methods used in canonical papers need to be changed, statisticians need only propagate a change to the testing logic used by the community.
 Once the testing logic has been changed, all models can be immediately evaluated against the new metrics. 
-Scientists wishing to determine statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.
+Scientists wishing to identify statistical best-practices for measuring goodness-of-fit need only refer to the tests in these repositories.
 
@@
 Using these common repositories, smaller groups of scientists interested in particular systems of interest will develop tests and models in test repositories like \textit{hippocampus\_tests}. 
-Each research community can develop suitable quality standards and processes for merging these pull requests.
+Each research community can develop suitable quality standards and processes for merging pull requests.
 
-The end result of these efforts will be tables, like the one shown in Figure \ref{fig:scidash_matrix}, that allow scientists to understand, precisely, the state-of-the-art in their field. 
+The most visible result of these efforts will be tables, like the one shown in Figure \ref{fig:scidash_matrix}, that allow scientists to understand, precisely, the state-of-the-art in their field. 
 We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \citep{omar_sciunit_2013}.
@@
 In many fields, however, both models and data are available from existing  community resources in standardized formats. 
-In this section, we will show how to use this existing infrastructure to make parameterizing tests with published data and generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
-In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models written in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
+In this section, we will show how to use this existing infrastructure to make 1) parameterizing tests with published data and 2) generating \textit{SciUnit} models from models implemented in some other manner (even in a language other than Python) nearly automatic.
+In particular, we will continue to focus on neurophysiology as our initial case study, using machine-readable models described in \textit{NeuroML} available from OpenSourceBrain (\textit{OSB}), and machine-readable data from \textit{NeuroElectro}.
 
@@
 The latter is illustrated in Figure \ref{fig:neuronunit_example}, on lines 1-4. 
-Once data has been retrieved from NeuroElectro, associated statistics (e.g.
-mean, standard error and sample size) can be extracted to parameterize tests (e.g.
-a test of spike widths on line 10).
-Data from NeuroElectro is can be used to validate a variety of basic electrophysiological features of neuron models, including spike width, resting membrane potential, after-hyperpolarization amplitude, etc.
+Once data has been retrieved from NeuroElectro, associated statistics (e.g. mean, standard error and sample size) can be extracted to parameterize tests (e.g. a test of spike widths on line 10). 
+Data from NeuroElectro can be used to validate a variety of basic electrophysiological features of neuron models, including spike width, resting membrane potential, after-hyperpolarization amplitude, etc.
 \todo{write a sentence or two about its use of the NeuroLex repository}
-As NeuroElectro is the only publicly curated source of such data, it represents a key resource facilitating test construction.
+As NeuroElectro is the only public, curated source of such data, it represents a key resource facilitating test construction.
 
@@
 Because NeuroML is an XML specification, model descriptions can be verified for correctness and queried for model properties and components.
-We leverage the latter facilities to expose model capabilities automatically.
+We are working on leveraging the latter facilities to expose model capabilities automatically.
 %NeuroML has proven ideal for model sharing, curation, and for answering both questions about \textit{what a model does} and \textit{how to do it} programatically.
 
-NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands off them off to a supported simulator for execution.
+NeuroConstruct (\cite{gleeson_neuroconstruct:_2007}, \url{http://www.neuroconstruct.org}) is a simulation manager that takes NeuroML models and hands them off to a supported simulator for execution.
 A number of popular simulators support execution of NeuroML models, including NEURON, GENESIS (\cite{bower_genesis_2007}, \url{http://genesis-sim.org}), NEST (\cite{gewaltig_nest_2007}, \url{http://www.nest-initiative.org}), and MOOSE (\cite{ray_moose_2008}, \url{http://moose.ncbs.res.in}).
 \textit{NeuronUnit} provides a \verbx{sciunit.Model} subclass called \verbx{NeuroConstructModel} that takes a path to a NeuroML model as a parameter.  
-NeuroML can describe a wide range of models, but our \verbx{NeuroConstructModel} class currently supports only  time-integrable point neurons (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential} at minimum; see Sec.
+NeuroML can describe a wide range of models, but our \verbx{NeuroConstructModel} class currently supports only time-integrable neuron models with membrane potentials (exposing capabilities \verbx{TimeIntegrable} and \verbx{HasMembranePotential} at minimum; see Sec.
 \ref{sec:neurotools}).
@@
 The underlying simulator can be configured (defaulting to ??\todo{What does it default to in our code??}; not shown).
-In this example, we simply create a model based on a NeuroML model of CA1 cells downloaded from OpenSourceBrain to the local file system (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}).
+In this example, we simply create a model based on a NeuroML model of CA1 cells downloaded from OpenSourceBrain to the local file system (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}).\todo{Migliore ref.}\todo{Should OSB models be transiently downloaded as part of the instantiation of OSBModel?}
 
@@
 The \textit{NeuronUnit} capability \verbx{HasSpikeTrain}  requires that a method named \verbx{get_spike_train} be implemented, returning a \verbx{SpikeTrain} object. 
-\verbx{NeuroConstructModel} implements this by default by calling the NeuroTools method \verbx{AnalogSignal.threshold_detection}, retrieving the membrane potential by calling the \verbx{get_membrane_potential} method implemented by the \verbx{HasMembranePotential} capability that all supported NeuroML models implement.
-NeuroTools is used in this manner to implement a wide variety of capabilities for \verbx{NeuroConstructModel}s, without requiring that the modeler do so explicitly (though they can overwrite these if they wish).
-This also helps scientists by directing them to a set of common utility functions and data formats that they can use, knowing that they are accepted by the community around NeuronUnit.\todo{do you have a list of capabilities that neuroconstructmodels can automatically implement?}
+\verbx{NeuroConstructModel} implements this by default by calling the NeuroTools method \verbx{AnalogSignal.threshold_detection}, retrieving the membrane potential by calling the \verbx{get_membrane_potential} method implemented by the \verbx{HasMembranePotential} capability.
+This capability is implemented by the OSBModel class that supports all current OSB models.
+NeuroTools is used in this manner to implement a wide variety of capabilities for \verbx{NeuroConstructModel}s, without requiring that the modeler do so explicitly (though they can override these if they wish).
+This also helps scientists by directing them to a set of common utility functions and data object types that they can use, knowing that they are accepted by the community around NeuronUnit.\todo{do you have a list of capabilities that neuroconstructmodels can automatically implement?}
 
@@
 Our tests are parameterized by data drawn both from NeuroElectro and entered manually, as well as models drawn both from OSB and implemented manually. 
-New tests, data and models can be added by contributing to these community resources and/or submitting pull requests; we anticipate handing control over merging these requests to members of the hippocampal modeling community once our interface stabilizes and this paper is published.
+New tests, data and models can be added by contributing to these community resources and/or submitting pull requests; 
+we anticipate handing control over merging these requests to members of the hippocampal modeling community once our interface stabilizes and this paper is published. 
 This repository represents a template that other groups of systems neuroscientists can use for their system of interest, and a starting point for other research areas in neuroscience, and science more broadly.
@@
 \textit{NeuronUnit} provides base classes to enable rapid generation of models, capabilities, and tests for neurophysiology data. 
-However these objects can also be created from scratch, requiring only adherence to the \textit{SciUnit} interface. 
-For example, a Model could implement an \verbx{integrate} capability method by wrapping execution of a MATLAB script and a \verbx{get_spikes} capability method by parsing a .csv file on disk; 
+However these objects can also be created from scratch, requiring only adherence to the \textit{SciUnit} interface as exemplified in sec. \ref{sec:sciunit}. 
+For example, a Model could implement an \verbx{integrate} capability method by wrapping execution of a MATLAB script and a \verbx{get_spikes} capability method by parsing a resulting .csv file on disk;
 a Test could be initialized using empirical spike rates collected in the lab.  
@@
 \subsection{Participation from Modeling Communities}
-Modelers may not want to expose their models to tests via capabilities, a requirement for test-taking.  
+Modelers may not want to formally expose their models to tests via capabilities, a requirement for test-taking.  
 We anticipate four solutions: \textbf{First}, we will emphasize to the community that wrapping existing model code that satisfy a capability is quite simple, requiring as little as one line of code. 
@@
 If a new piece of data invalidates a widely-accepted model, this can be cited in publications.
-\textbf{Fourth}, one can compare new data against existing data by simply creating a \emph{data-derived model} that directly generates ``predictions'' by draws from the new dataset directly.
+\textbf{Fourth}, one can compare new data against existing data by simply creating a \emph{data-derived model} that directly generates ``predictions'' by draws from the existing dataset directly.
 Thus the model validation procedures described in this paper can also be used to perform data validation -- that is, check the goodness-of-fit of new data with old data.
@@
 The diversity of topics in biology is vast. 
-\textbf{First}, we address this by providing an interface allowing modelers to flexibly express precisely how a model should be interfaced with using  capabilities.
+\textbf{First}, we address this by providing an interface allowing modelers to flexibly express precisely how a model should be interfaced using capabilities. 
 Capabilities can inherit from and call into each other. 
-This is more flexible than the fixed interfaces used in existing modeling competitions or domains like machine learning where only a few interfaces are of interest (e.g.
-classifiers).
+This is more flexible than the fixed interfaces used in existing modeling competitions or domains like machine learning where only a few interfaces are of interest (e.g. classifiers). 
 \textbf{Second}, NeuroML naturally addresses diversity of scales because it is organized hierarchically, in ``levels.''  

### 2014-01-16 databases/databases_chapter.tex
Update encyclopedia chapters to include required definitions and section headings

@@
 
+\section*{Neuroscience Databases}
+
+\subsection*{Synonyms}
+Data repositories
+
+\subsection*{Definition}
+Neuroscience databases are curated collections of data from neuroscience experiments that can be used to test models or compare with the results of novel experiments.
+They are often but not always relational, and are frequently free and public to maximize their utility to other researchers.
+
+\subsection*{Detailed Description}
+
 Computational neuroscience produces models that can help to explain empirical data. 
@@
 
+\subsubsection*{Computational Models}
 First, there are databases of computational models and model parts.  
@@
 
+\subsubsection*{Neuron Properties}
 Second, there are databases containing structured information specific to neurons and their properties. 
@@
 
+\subsubsection*{Anatomical Reference}
 Third, there are databases focusing on the anatomical organization of the brain.  
@@
 
+\subsubsection*{Integration}
 In addition to these neuroscience domain-specific databases are uber-databases that provide linking facilities for cross-resource data integration. 
@@
 
-\bibliographystyle{plainnat}
-\nobibliography{shreejoy}
+\subsection*{Cross-References/Related Terms}
+None
+
+\bibliographystyle{abbrv}
+\bibliography{shreejoy}
 

### 2014-01-16 databases/neuroelectro_chapter.tex
Update encyclopedia chapters to include required definitions and section headings

@@
 
+\section*{The NeuroElectro Project}
+
+\subsection*{Synonyms}
+neuroelectro, neuroelectro.org
+
+\subsection*{Definition}
+The NeuroElectro Project is an effort to curate data about the electrophysiological properties
+of neurons.  It contains experimental data extracted from the literature about dozens of
+basic properties (such as resting membrane potential, action potential width, etc.) for hundreds of distinct types of neurons.  It can be browsed online at http://neuroelectro.org.
+
+\subsection*{Detailed Description}
 Computational neuroscientists have argued that the electrophysiological properties of neurons determine their computational roles.
@@
 
+\subsubsection*{Implementation}
 This database is populated primarily using automated text extraction from tables of journal articles using Python.
@@
 
+\subsubsection*{Data provenance}
 While NeuroElectro contains information about 27 distinct electrophysiological properties, those most heavily represented include resting membrane potential, input resistance, action potential height and width, etc.
@@
 
+\subsubsection*{Participation}
 The NeuroElectro web interface (\url{http://neuroelectro.org} also invites users to contribute to the database’s content.
 For example, users can suggest relevant articles on a specific neuron type as well as validate content that has been extracted via the automated algorithms.
-Furthermore, users can elect to become ``content-experts” on a specific neuron type and can then modify the database’s content directly.
+Furthermore, users can elect to become ``content-experts" on a specific neuron type and can then modify the database’s content directly.
 
+\subsubsection*{Scientific Goals}
 NeuroElectro also contains analyses of the resulting database yielding novel relationships on the electrophysiological similarity of different neuron types throughout the brain.
@@
 
-\bibliographystyle{plainnat}
-\nobibliography{shreejoy}
+\subsection*{Cross-References/Related Terms}
+None
+
+\bibliographystyle{abbrv}
+\bibliography{shreejoy}
 \end{document}

### 2014-03-17 neuroelectro_frontiers/main.tex
Initial submission of NeuroElectro methods paper

\documentclass{template/frontiersSCNS} % for Science articles

\usepackage{url,lineno}
\usepackage{todonotes}

\linenumbers

\copyrightyear{}
\pubyear{}

\newcommand{\INS}[1]{{{\color{red}#1}}}

\def\journal{Neuroinformatics}
\def\DOI{}
\def\articleType{Research Article}
\def\keyFont{\fontsize{8}{11}\helveticabold }
\def\firstAuthorLast{Tripathy {et~al.}}
\def\Authors{Shreejoy J. Tripathy\,$^{1,2,3,4,*}$, Judith Savitskaya\,$^{1,6}$, Shawn D. Burton$^{1,2}$, Nathaniel N. Urban$^{1,2}$, and Richard C. Gerkin\,$^{1,2,5,*}$}
\def\Address{$^{1}$Department of Biological Sciences, Carnegie Mellon University, Pittsburgh, PA, USA \\
$^{2}$Center for the Neural Basis of Cognition, Pittsburgh, PA, USA \\
$^{3}$Present Address: Centre for High-Throughput Biology, University of British Columbia, BC, Canada \\
$^{4}$Present Address: Department of Psychiatry, University of British Columbia, BC, Canada \\
$^{5}$Present Address: School of Life Sciences, Arizona State University, Tempe, AZ, USA \\
$^{6}$Present Address: Graduate Program in Bioengineering, University of California, Berkeley and University of California, San Francisco, CA, USA }
\def\corrAuthor{Shreejoy J Tripathy}
\def\corrAddress{177 Michael Smith Laboratories, 2185 East Mall,
University of British Columbia, BC, Canada, V6T 1Z4} 
\def\corrEmail{stripat3@gmail.com}

\begin{document}
\onecolumn
\firstpage{1}

\title[NeuroElectro.org: text-mining neurophysiology data]{NeuroElectro: A Window to the World's Neurophysiology Data}
\author[\firstAuthorLast ]{\Authors}
\address{}
\correspondance{}

\extraAuth{Richard C Gerkin\\ School of Life Sciences
PO Box 874501
Arizona State University, Tempe, AZ, 85287-4501, rgerkin@asu.edu}
\topic{Neuroinformatics Infrastructure}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% SDB: neurophysiology and electrophysiology can be used somewhat interchangeably. You use neurophysiology in your title - you should then use that somewhat consistently throughout your article. Right now, the only place you say Neurophysiology is in the title.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

\begin{abstract}

The behavior of neural circuits is determined largely by the electrophysiological properties of the neurons they contain.  Understanding the relationships of these properties requires the ability to first identify and catalog each property.  However, information about such properties is largely locked away in decades of closed-access journal articles with heterogeneous conventions for reporting results, making it difficult to utilize the underlying data.  We solve this problem through the NeuroElectro project: a Python library, RESTful API, and web application (at \url{http://neuroelectro.org}) for the extraction, visualization, and summarization of published data on neurons' electrophysiological properties.  Information is organized both by neuron type (using neuron definitions provided by NeuroLex) and by electrophysiological property (using a newly developed ontology).  We describe the techniques and challenges associated with the automated extraction of tabular electrophysiological data and methodological metadata from journal articles.  We further discuss strategies for how to best combine, normalize and organize data across these heterogeneous sources.  NeuroElectro is a valuable resource for experimental physiologists looking to supplement their own data, for computational modelers looking to constrain their model parameters, and for theoreticians searching for undiscovered relationships among neurons and their properties. 
\tiny
 \keyFont{ \section{Keywords:} neuroinformatics, electrophysiology, database, text-mining, metadata, API, machine learning, natural language processing} 
 %All article types: you may provide up to 8 keywords; at least 5 are mandatory.
\end{abstract}

\section{Introduction}

Brains achieve efficient function through implementing a division of labor, in which different types of neurons serve distinct functional and computational roles.  One striking way in which neuron types differ is in their electrophysiology properties. Though the electrophysiology of many neuron types has been previously characterized and documented across decades of research, these data exist across thousands of journal articles, making cross-study neuron-to-neuron comparisons difficult.

Neurophysiology lacks a centralized resource where consensus data on basic physiological measurements  from many neuron types and studies are accessible for reference and subsequent meta-analyses. For example, though it is common for neurophysiologists to measure and report neuronal measurements such as resting membrane potential and input resistance, there is not a public database which compiles this information. In other domains of neuroscience such efforts have made more progress.  In the domain of neuroanatomical connectivity, information on connectivity between different brain regions is being compiled by experts at the Brain Architecture Management System project (BAMS) across hundreds of publications \citep{bota_brain_2005}.  Parallel to this effort is the WhiteText Project, which addresses a complementary goal by algorithmically mining brain region connectivity statements from journal abstracts using biomedical natural language processing (bioNLP) methods \citep{french_automated_2009,french_application_2012}.  Similarly, in the domain of neuroimaging, the NeuroSynth Project has mined fMRI-based brain activation maps from published {x,y,z} coordinate data tables from thousands of neuroimaging publications \citep{yarkoni_large-scale_2011}.  These literature-based methods can be contrasted with projects such as NeuroMorpho.org \citep{parekh_neuronal_2013} and ModelDB \citep{migliore_modeldb_2003,hines_modeldb:_2004}, which index neuron morphological reconstructions and computational models for simulating neuron activity by obtaining this information directly from investigators.

Success among these projects can be defined according to different criteria.  Such criteria include completeness and comprehensiveness; for example, what percentage of relevant connectivity studies are indexed within BAMS? How many different neuron types are contained within the NeuroMorpho database?  Alternatively, success can be defined in terms of the utility of these databases in driving subsequent research, like the use of BAMS as a resource for discovering relationships between brain region connectivity and gene expression \citep{french_relationships_2011} or the use of NeuroMorpho to discover general scaling relationships among the morphology of neuron types \citep{teeter_general_2011}. Similarly, NeuroSynth is widely used by cognitive scientists as a starting point for designing functional imaging studies.  Thus while these projects are not yet comprehensive and likely contain data records of varying quality, these resources may nevertheless be employed to draw novel inferences.

These projects are logically divided according to their methods for obtaining the source data: through the use of manual methods like expert curation or user contributions versus automated methods such as text-mining.  Notably, these approaches differ in their scale and accuracy; while algorithmic methods can ``scale-up'' and be applied to arbitrary numbers of publications, they typically have a lower accuracy relative to human-curated content \citep{french_automated_2009}.  This lower accuracy is often attributed to the rich lexical complexity of biomedical texts which often require considerable context and background knowledge to understand and parse \citep{dickman_tough_2003,ambert_text-mining_2012}.  The competing constraints of scale versus accuracy pose a challenge for large-scale compilation of neuroscientific data.

Here, we built a custom infrastructure framework for extracting electrophysiological measurements for specific neuron types from published neurophysiology articles.  These measurements included properties such as input resistance and resting membrane potential, as well as associated metadata (i.e., article-specific methodological details).  Our methods combine algorithmic literature text-mining, drawing from the approach used by NeuroSynth \citep{yarkoni_large-scale_2011} where neurophysiological measurements are primarily extracted from data tables, as well as manual curation, leveraging the background knowledge of domain experts.  The resulting neurophysiology database, named NeuroElectro, can be interactively viewed and explored through a public web interface at \url{http://neuroelectro.org}.

\section{Materials, Methods, \& Results}

\subsection{Overview}

We describe and validate our semi-automated methodology for obtaining neuronal biophysical measurements directly from published reports in the literature (summarized in Fig. \ref{text_mining_workflow}).  After obtaining full article texts from publishers, we then used text-mining algorithms to identify concepts specific to electrophysiology and neuron types, which we then validated manually.

\begin{figure*}[htbp]
\centering
\includegraphics[scale = .8]{figures/SMeth2_text_mining_workflow_v2.jpg}
\caption{Illustration of workflow for obtaining electrophysiological information from the research literature.}
\label{text_mining_workflow}
\end{figure*}
%SDB: in this figure and subsequent figures, you include very coarse tables, rather than what might appear in the final publication. This might be a  point of confusion for pure experimentalists that only focus on the formatted tables in articles. That is, it seems like you are just making up this table as an example. What if you replace the coarse tables currently in your figure with an example of a  formatted table from a paper and the underlying html code that generates that table?

\subsection{Article identification}
We obtained electrophysiological data from 10 neuroscience specific journals (Table \ref{tab:journal_listing}), which include: \emph{Journal of Neuroscience, Journal of Neurophysiology,} and \emph{Journal of Physiology} (among others). We selected these journals because they often devote a significant fraction of an article's main text, tables, and figures to detailed characterizations and summaries of intrinsic neuronal biophysical properties.

\begin{table}[!t]
\textbf{\refstepcounter{table}\label{tab:journal_listing} Table \arabic{table}.}
{Statistics of journals represented in the NeuroElectro database. Listing of journals and counts of articles downloaded (articles obtained), articles with published data tables containing neurophysiological information which has been manually validated by an expert curator (validated), and articles which likely contain information in a data table which has not yet been manually curated (not validated). Not validated articles are those which have at least 4 algorithmically assigned electrophysiological concepts within a data table.}
\processtable{}
{\begin{tabular}{rrrr}
    \toprule
    Journal & Articles obtained & Validated & Not validated \\
    \midrule
    J. Neurosci. & 19002 & 104   & 560 \\
    J. Neurophysiol. & 12078 & 94    & 555 \\
    J. Physiol. (Lond.) & 10543 & 44    & 235 \\
    Neuroscience & 3035  & 14    & 205 \\
    Eur. J. Neurosci. & 2495  & 7     & 117 \\
    Brain Res. & 3017  & 7     & 146 \\
    Neuron & 1657  & 4     & 43 \\
    Epilepsia & 463   & 2     & 23 \\
    Neurosci. Lett. & 1468  & 2     & 34 \\
    Hippocampus & 208   & 2     & 10 \\
    \botrule
    \end{tabular}}[]
\end{table}

We obtained tens of thousands of potentially relevant full article texts directly from publisher websites.  We first identified potential articles that were likely to contain information relevant to neuron biophysics using the native search functions provided within the journal websites and only downloaded articles containing a specific list of terms including ``input resistance'' and ``resting membrane potential'' (Fig. \ref{text_mining_workflow}).  This pre-selection step allowed us to identify and download only articles that contained data relevant to our project.  Upon identifying candidate articles, we then downloaded the full text of each potentially-relevant article as HTML; articles downloaded from the publisher Elsevier (e.g., \emph{Neuron and Brain Research}) were downloaded as XML using the provided text-mining API and subsequently converted to HTML.  We chose to work with HTML (as opposed to PDF or XML) because HTML provides a machine-readable markup of the article's content, allowing us to easily identify relevant elements within the article -- such as data tables and the methods section -- using publicly available HTML-parsing tools (here we used the Beautiful Soup HTML-processing library implemented in Python: \url{http://www.crummy.com/software/BeautifulSoup/bs4/doc/}).  Furthermore, because HTML is a single semi-structured standard used across publishers, we could write relatively generic HTML-processing algorithms applicable to content published across journals.  However, our focus on using HTML limits us to relatively newer articles -- typically those published after 1997 -- because most publications before this time are only available as scanned PDF files.

We stored the HTML-enhanced full text of each article in our database and associated each article with its corresponding PubMed ID (\url{http://www.ncbi.nlm.nih.gov}).  These 8-digit IDs serve as publisher-independent unique identifiers for each article, and allow us to use PubMed-specific tools, such as a powerful API (i.e., PubMed eutils, \url{http://www.ncbi.nlm.nih.gov/books/NBK25500/}).  For example, this API provides the ability to query each article's MeSH terms (MEdical Subject Headings) and returns basic methodological information such as animal species and strain.

\subsection{Electrophysiological property identification}

\subsubsection{Rationale for focusing on electrophysiological property extraction from data tables.}
In order to algorithmically extract information on neuron electrophysiology from these articles, we needed to first specify the data types of interest.  Our preference was to obtain as much detailed information about neuron electrophysiological properties as possible: ideally, this would include raw data corresponding to recorded electrophysiological traces. In mining information from articles, we were presented with multiple options (illustrated in Fig. \ref{content_types}), including extraction from: 1) the text of the article including figure captions, 2) the figures of the article, or 3) data tables presented within the article.  In addition to these, authors often submit supplemental materials and figures which also contain neurophysiological data.

\begin{figure*}
\centering
\includegraphics[scale = .8]{./figures/SMeth1_extraction_content_example.jpg}
\caption{\textit{Illustration of the sources within an article containing information relevant to neuron electrophysiological properties.}  Data on neuronal electrophysiological properties are presented within article figures and raw traces, sentences within the article text, and formatted data tables.  The raw traces and references are from \citet{van_brederode_gad67-gfp+_2011} and the data table is a constructed example.  Colored text indicates electrophysiological concepts (red), neuron concepts (pink), or neurophysiological data (yellow).}.
\label{content_types}
\end{figure*}

Given the challenges in mining raw electrophysiological traces from figure images, we instead focused on obtaining information about basic neuronal electrophysiological properties, such as input resistances and resting membrane potentials.  Though this information is often presented within the text of the article, it is usually presented in complex sentence structures that are difficult to accurately parse algorithmically.  Published data tables, on the other hand, present a unique opportunity for electrophysiological data extraction, since common techniques exist for extracting information from structured tables \citep{yarkoni_large-scale_2011}.  Moreover, because tables succinctly summarize multiple attributes of a collected dataset, the effort of an expert curator can be put to best use when validating tables relative to validating content mined from article sentences or figure panels.  While we estimate that only 5-10\% of electrophysiology articles contain data tables, there is sufficient redundancy within the field (i.e., multiple investigators often publish articles on the same neuron type) that focusing on data tables nevertheless yields substantial coverage of electrophysiological properties across nearly all major neuron types.

\subsubsection{Extracting information on electrophysiological properties.}
\label{sec:ephys_extraction}
In extracting electrophysiological data, we took advantage of the fact that certain measurements are commonly made during intracellular recordings.  For example, such recordings are commonly used to: 1) measure a neuron's resting membrane potential, 2) to apply hyperpolarizing current injections for measurement of input resistance and membrane time constant, and 3) to apply depolarizing current steps to evoke action potentials (spikes) and enable measurement of characteristics such as spike threshold, width, and amplitude.

We developed an electrophysiological lexicon comprising 28 measurements that we found to be commonly reported in the literature, largely based on previously published definitions \citep{toledo-rodriguez_correlation_2004,ascoli_petilla_2008}.  To account for subtle differences in terminology that authors use to refer to the same electrophysiological concept (e.g., resting membrane potential is often referred to as ``rmp'' and ``V$_{rest}$''), we also identified a common list of synonyms to map to each concept.  Together, these electrophysiological concepts and their synonyms define a preliminary ontology for electrophysiological concepts (included in Supplemental Materials).  Moreover, this physiological measurement ontology can serve as a scaffolding for a more in-depth ontology of electrophysiological investigations (e.g., Ontology for Experimental Neurophysiology, \citet{bruha_ontology_2013}). The terms in our preliminary ontology are also indexed and defined within NeuroLex (\url{http://neurolex.org}, \citep{larson_neurolex.org:_2013}).

To identify data corresponding to electrophysiological properties reported within a data table, we developed algorithms to search data table header elements and assess whether these elements corresponded to any of the electrophysiological concept synonyms in our ontology.  We first identified table header elements by searching for table elements composed primarily of non-numeric characters.  For each putative header element, we then used fuzzy string matching algorithms (implemented using the fuzzywuzzy library in Python: \url{https://github.com/seatgeek/fuzzywuzzy}), to assess the textual match between the header element and each of the electrophysiological synonyms.  These fuzzy matching algorithms combine a number of string match metrics into a single ``match value", including whether a pair of strings completely match, contain matching substrings, or contain matching but misordered substrings.  If the table header and electrophysiological synonym match value exceeded a specified threshold, the table header and corresponding row or column of numeric values were automatically mapped to the electrophysiological concept.  Similarly, we mapped whole rows or columns to specific neuron types recorded during normotypic or ``wild-type" conditions.

We then manually corrected cases where these algorithms misassigned an electrophysiological concept.  For example, a common algorithmic mis-assignment was the case when an author used the string ``EPSP amplitude'' to refer to the electrophysiological concept excitatory post-synaptic potential amplitude.  In these cases, our algorithms incorrectly mapped this string to ``spike amplitude'' because the former concept is not in our current ontology.  In a test sample of 279 articles that were manually curated, we found that 78\% of concept-matchings (901/1152) were identified correctly with no supervision, with the remainder manually corrected.

\begin{figure*}
\centering
\includegraphics[scale = 1]{figures/example_data_table_v2.jpg}
\caption{\textit{Example data table illustrating mark-up and annotation of entities.}  A. Example published data table containing neurophysiological information.  Data table from \citet{pasquale_increased_1997}.  B. Same as A, but semantically marked up with algorithmic and manually curated annotations.  Markups in red and pink indicate electrophysiological and neuron type concepts and yellow indicates extracted data measurements.  Note that here the textual string ``+/+'' and ``stg/stg'' refers to the normotypic and manipulated condition, respectively.}
\label{data_table}
\end{figure*}

\subsubsection{Accounting for differences in electrophysiological definitions across investigators.}
By focusing on textually matching the electrophysiological terms in each table to a list of electrophysiological concepts, we are implicitly assuming that electrophysiological properties are measured in the same way by investigators across different articles.  For example, the most common method that electrophysiologists use to measure a neuron's spike properties is to record from the neuron in current-clamp mode and apply peri-threshold depolarizing currents to evoke 1-2 spikes over several hundred milliseconds or more.  The neuron's spike amplitude is then commonly measured by calculating the difference between the neuron's voltage at spike threshold and spike peak for the first evoked spike (e.g. \citep{connors_electrophysiological_1982,toledo-rodriguez_correlation_2004}).  However, experimental differences exist between how investigators measure and compute these properties; we divide these differences into roughly 3 categories: \textit{protocol}, \textit{calculation}, and \textit{condition} differences.  For example, investigators can use different experimental protocols to measure the spike amplitude, like evoking spikes using current steps much greater than rheobase current required to elicit a single spike (\textit{protocol differences}).  Additionally, the spike amplitude itself can be calculated in different ways, such as using the neuron's resting membrane potential as the baseline instead of the spike threshold (\textit{calculation differences}).  Furthermore, the value of spike amplitude that an investigator reports will also be affected by specific experimental conditions such as the animal species or age and recording solution temperature or contents (\textit{condition differences}).

When manually curating the text-mined content for the most commonly reported electrophysiological properties (resting membrane potential, input resistance, membrane time constant, spike half-width, spike amplitude, and spike threshold), we took care to account for and remove cases where the investigator had calculated an electrophysiological measurement using an inconsistent methodology (e.g., protocol or calculation differences).  However we note that we could not identify all of these cases (in particular: spike amplitude, input resistance, and membrane time constant), in part because investigators did not always explicitly define how these measurements were calculated within their article.  We note that in cases where we pool measurements which are measured using inconsistent protocols or calculations, this will tend to add unexplained variance to our data set.  Given these measurement inconsistencies, we provide our recommendations for how these electrophysiological properties should be reported in future investigations via our electrophysiology ontology (see Supplemental Materials).

\subsection{Neuron type identification}

\subsubsection{Using neuron types defined by NeuroLex.}
To extract physiological information specific to individual neuron types, we had to identify which neuron types were reported in each article.  However, in many cases uniquely identifying the neuron type(s) reported in any given study and mapping these to a canonical ``neuron type'' is difficult.  This difficulty arises in part because investigators use different criteria for classifying neurons, including electrophysiological, morphological, or molecular characteristics \citep{ascoli_petilla_2008,huang_genetic_2013,fishell_neuron_2013}.

To define canonical neuron types, we chose to use an existing list of approximately 250 neuron types and definitions provided by NeuroLex, a community-sourced, expert-defined collection of neuron types (\url{http://neurolex.org}; \citet{shepherd_synaptic_2003,hamilton_ontological_2012,larson_neurolex.org:_2013}).  Moreover, we chose to use NeuroLex to keep our database consistent with existing resources and to enable future researchers to combine these resources seamlessly.  NeuroLex also provides synonyms for each neuron type, which we utilized to identify the neuron type(s) in each article.  In cases where a neuron type was investigated in the literature across multiple articles but not indexed within NeuroLex (e.g. cerebellar nucleus neurons), we manually added this neuron type to our database's listing and provided this neuron type to the NeuroLex neuron curators for incorporation (Gordon Shepherd, personal communication).  Our specific criteria for identifying each of the neuron types reflected in the database are given in the Supplemental Materials.

\subsubsection{Identifying specific neuron types within an article.}
Because of the complexity in unambiguously identifying neuron types, we used a mixed text-mining and manual approach to map the neuron types studied in each article to canonical NeuroLex neuron types.  First, we used text-mining algorithms to provide an initial ``best guess'' of the most likely neuron type.  Specifically, we used a bag-of-words approach \citep{aldous_exchangeability_1985} on the full article text.  This approach ignores the serial structure of the words in the document and utilizes only the frequency of occurrence of each word within the document. We next compared the article's word-frequency histogram to the listing of neuron synonyms provided by NeuroLex, ranking all neuron types by their likelihood of being actually studied within that article.  In comparison to articles that we manually curated, we found that this automated approach accurately identified the neurons studied in each article with an accuracy of 30\% (120 of 399 total) and up to 55\% when defining success as the studied neuron appearing as one of the top three neuron types suggested by the bag-of-words method.  Because of the relatively low accuracy of an automated-only approach, we added a manual curation step where a curator identified the recorded neuron type using HTML drop down menus enriched by the bag-of-words search (e.g., Fig. \ref{human_validation}).  As previously described, we mapped individual data table elements and corresponding rows or columns to specific neuron types recorded under normotypic conditions.  We note that currently we only identify data from normotypic or ``control" neurons represented in tables, but plan to identify data from additional conditions in future work (e.g. from pharmacologically manipulated or genetically modified animals).

\subsection{Extraction of electrophysiological data values}
After identifying specific electrophysiological properties and neuron types reported in a data table (corresponding to row or column table headers), we then algorithmically extracted the data corresponding to the table intersection of these (Fig. \ref{data_table}).  We developed custom string regular expressions \citep{thompson_programming_1968} to parse the string corresponding to the numeric data.  Specifically, we found that data strings were often of the form: ``XX $\pm$ YY (ZZ)'', where XX, YY, and ZZ refer to the mean, error term, and sample size (i.e. the ``n''), respectively.  Often the number of replicates or error measurement were not reported or were reported in alternative ways within the table.  Presently, the error term is not resolved as either a standard deviation or standard error measurement in the current version of NeuroElectro, but could easily be resolved in future iterations.

When designing our processing algorithms, we parsed data strings from right to left: first searching for data entities contained within parentheses, then for entities contained to the right of the $\pm$ term, and finally the remaining term which we assumed to refer to the mean term.  We found that occasionally data were reported as ``XX (LL - HH)'' -- where LL and HH indicate the lower and upper limits of a data range -- and accounted for these cases similarly.  We used regular expressions to identify entities such as digits, decimal signs, parentheses, and $\pm$ signs.  We then converted the individual data elements which were encoded as textual strings of digits to double precision decimal entities before storing these into our database.  Our focus here was primarily on parsing the data record mean value (i.e., summarizing the properties of a number of recorded neurons), but also extracted and stored the error term and sample size where possible.  Using these methods, we were able to extract 2176 electrophysiological values for 93 distinct neuron types within 279 articles.

\subsection{Manual validation of automated data extraction}
Following these automated concept identification and data extraction steps, we manually validated associated concepts and fixed incorrect concept mappings as necessary.  We developed custom-HTML and javascript code to allow human curators to graphically interact with downloaded HTML data tables and ``mark-up'' entities within the table (Fig. \ref{human_validation}).  This code allows for textual based elements of the HTML table to be semantically annotated using drop down menus and text fields.  Moreover, because annotation is implemented via user interfaces composed of interactive web pages and drop down menus, these user interfaces are simple enough to be utilized by other expert curators with little formal instruction. 
% do I need to say more here? 
%SDB: Perhaps include a before and after version of the table in Figure 4 to drive home the point that you are able to use this mark-up tool to change/correct values/concepts. Also, maybe give an example in this figure of changing a neuron type and of changing a value.

\begin{table}[!t]
\textbf{\refstepcounter{table}\label{tab:metadata_id} Table \arabic{table}.}
{A partial listing of metadata attributes and extraction methodology.  Metadata attributes are extracted through combining PubMed Medical Subject Heading terms (MeSH Terms) and custom regular expressions (Regex).  Regular expression column (or MeSH Term column) indicates specific regular expressions (or MeSH terms) used for identifying metadata concept entities.}
\processtable{}
{\begin{tabular}{rrrrrr}
    \toprule
    Metadata Concept & Values & Extraction method & Regular Expresssion & MeSH Term \\
    \midrule
    Species &       & MeSH Term only &       &       \\
          & Rats         &       & & Rats  \\
          & Mice         &       & & Mice  \\
          & Guinea Pigs        &       & & Guinea Pigs \\
    Electrode Type &        & MeSH Term + Regex &       &       \\
          & Patch-clamp &        & "whole cell" or "patch clamp" & Patch-Clamp Techniques  \\
          & sharp &        & "sharp electrode" &        \\
    Animal Strain &        & MeSH Term only &       &       \\
          & Fischer 344 &              & & Rats, Inbred F344 \\
          & Long-Evans &             & & Rats, Long-Evans \\
          & Sprague-Dawley &              & & Rats, Sprague-Dawley \\
          & Wistar &             & & Rats, Wistar \\
          & C57BL &              & & Mice, Inbred C57BL \\
          & BALB C &              & & Mice, Inbred BALB C \\
    Prep Type &       & MeSH Term+Regex &       &       \\
          & in vitro &        &"slice" or "in vitro" &       \\
          & in vivo &        &"in vivo" &       \\
          & cell culture &        &"culture" & Cell Culture Techniques \\
          & model &       &"model" & Computer Simulation \\
    Jxn Potential &        & Regex &       &       \\
          & Not Corrected &        &"not… junction potential"   &       \\
          & Corrected &        &"junction potential" &       \\
          &       &              &   &    \\
    Rec Temperature &        & Regex &       &       \\
          & Continuous value &        & "record ... °C" or "experiment … °C" &       \\
          & Room temperature &       & "record… room temperature"  &       \\
          &       &       &        &     \\
    Animal Age &        & Regex &       &       \\
          & Continuous value &        & Find digits near: "P\#-\#" or "P\#-P\#"&       \\
    \botrule
    \end{tabular}}
{}
\end{table}

\begin{figure*}
\centering
\includegraphics[scale = 1]{figures/human_validation_example.jpg}
\caption{\textit{Example of human validation of algorithmically assigned content.}  All textual elements of a table are enhanced using HTML and javascript to allow for assignment of neuron or electrophysiological concepts using drop down menus.  Example data table from \citet{pasquale_increased_1997}.}
\label{human_validation}
\end{figure*}

\subsection{Metadata identification}
Given the strong relationships between experimental conditions, such as animal species or recording temperature, and electrophysiological measurements (e.g., input resistances are known to decrease when measured in neurons from older animals \citep{zhu_maturation_2000,okaty_transcriptional_2009,kinnischtzke_postnatal_2012}), we also identified information on article-specific experimental conditions by extracting this information primarily from each article's methods section.  For each article, we found the methods section by developing custom HTML tag filters for each journal (e.g., common publisher-defined HTML tags for methods sections are ``Methods" or ``Experimental procedures").  For each metadata entity that we focused on (species, animal strain, electrode type, preparation type, liquid junction potential correction, animal age, recording temperature), we devised custom automated text searching methods to identify these based on combining regular expressions \citep{thompson_programming_1968} with PubMed MeSH terms (Table \ref{tab:metadata_id}).  In other words, rather than taking a machine-learning based approach and training classifiers \citep{mccallum_mallet:_2002}, we took a rule-based approach and developed custom rules for identifying metadata entities.  For example, to identify whether the recording electrode's liquid junction potential was corrected for in the study \citep{neher_[6]_1992}, we searched for whether the character string ``junction potential'' was mentioned within the methods section and, if so, whether the sentence or phrase containing the term was explicitly negated (indicating that the junction potential was not corrected for).  Here, we identified and parsed distinct sentences within the methods section using tools provided within the Natural Language Tool Kit in Python \citep{bird_natural_2009}.

\begin{figure*}[htbp!]
\centering
\includegraphics[scale = 1]{figures/metadata_assignment_accuracy.jpg}
\caption{\textit{Accuracy of metadata assignment using automated methods alone.} }
\label{metadata_robot_accuracy_robot}
\end{figure*}

Following automated identification of article metadata, we then manually checked each article to ascertain that algorithmically-tagged metadata was identified correctly and, as before, we corrected misidentified content as necessary through the use of custom HTML forms.  We found that the mean accuracy of algorithmic metadata assignment was approximately 50\% (Fig. \ref{metadata_robot_accuracy_robot}) and was typically lower for identifying continuous-valued metadata (e.g. animal age or recording temperature) relative to nominal metadata such as species and electrode type.

\subsection{Object models and relational database}
We stored extracted data and metadata using a relational database implemented in MySQL (\url{http://dev.mysql.com/doc/refman/5.6/en/}) built from a Python Django object model (\url{https://www.djangoproject.com/}).  The object model contains classes for a number of fields, such as full article texts, electrophysiological properties, neuron types, synonyms, electrophysiological data values, and experimental metadata (Fig. \ref{db_schema}).  A useful feature of the relational nature of the database is that it enables linking between classes (e.g., linking between neuron types and electrophysiological properties reported by a single investigator across multiple articles). This linking feature facilitates efficient and arbitrary querying of data; for example, querying for known electrophysiological data on olfactory bulb mitral cells recorded \emph{in vitro} and published between the dates 2000 and 2004.  For example, such a feature could be used to assess whether the properties of olfactory bulb mitral cells have changed as a function of time or are dependent upon whether the data are collected \emph{in vitro} or \emph{in vivo}.

\subsection{Web application}
The primary results of NeuroElectro are viewable at \url{http://www.neuroelectro.org} where the data can be interactively explored.

\subsubsection{Human interface}
The web interface is organized around neuron types and electrophysiological properties.  For example, each neuron type has its own webpage where extracted data corresponding to specific electrophysiological properties is graphically and interactively displayed (graphical plot interactivity implemented using the jqPlot javascript toolbox, \url{http://www.jqplot.com/}).  Users can thus visualize the mean and variability of electrophysiological values across papers, view references plus experimental metadata, and easily navigate to primary data from specific papers.  Furthermore, users can view electrophysiological data across all of the neuron types in the database - putting phenotypic properties of a given neuron type into the larger context of other neuron types located throughout the nervous system.

The web application also contains preliminary features to allow website visitors to contribute to the NeuroElectro resource.  For example, users can suggest articles which contain electrophysiological data which are not already in the database.  We also invite visitors to become ``expert curators'' for neurons of interest.  In the future, we plan to build functionality that will allow investigators to upload raw and summary data, such as recorded voltage and current traces.  In addition, we plan to continue mining the literature and adding neurophysiological measurements as they are published.

\subsubsection{API}
An initial API (application programmer interface) providing public access to the electrophysiological data is described at \url{http://neuroelectro.org/api/docs/}.  This RESTful API allows contents of the NeuroElectro database to be dynamically retrieved in JSON or XML format to utilize this data within external applications.  For example, using the current API, a developer could build an application which dynamically queries NeuroElectro for all data corresponding to layer 2/3 neocortical pyramidal cells and then uses this data to constrain parameters for a Hodgkin-Huxley type neuron model \citep{hodgkin_quantitative_1952}.  Example use cases of the current API (version 1) include:

\begin{itemize}
\item \url{http://neuroelectro.org/api/1/n/} : Returns a list of all neurons with electrophysiological data indexed in NeuroElectro.
\item \url{http://neuroelectro.org/api/1/nedm/?nlex=sao830368389} : Returns a list of all indexed data on CA1 pyramidal cells (queried using the NeuroLex identifier for CA1 pyramidal cells, \emph{sao830368389}).  
\item \url{http://neuroelectro.org/api/1/nes/?e\_\_name=Input\%20Resistance\&n\_\_name=Cerebellum\%20Purkinje\%20Cell} : Returns a data record composed of the mean, standard deviation, and n, summarizing input resistance measurements from cerebellar Purkinje cells based on all indexed articles in NeuroElectro database.  Here the database query is performed using the textual strings for the electrophysiological and neuron type concepts.
\end{itemize}

Our future plans are to work with domain ontologists to further develop the existing API into a formal relational data format (RDF) specification, allowing further querying and extending of NeuroElectro into additional resources.

\section{Discussion}

We have developed, applied, and validated a methodology and pipeline for extracting -- from existing literature on cellular neurophysiology -- measurements of basic biophysical properties from diverse neuron types throughout the nervous system.  Currently, the NeuroElectro database contains 2344 manually curated electrophysiological measurements from 98 neuron types from 335 publications.  Of these electrophysiological measurements, 2176 (93\%) were obtained from 279 (83\%) publications using the semi-automated approach described here.  In addition, we machine-extracted and manually validated 1667 methodological conditions (metadata) from these publications.  This represents the single largest collection of neurophysiological data ever compiled and represents a potentially valuable tool for scientific discovery.

\subsection{Specific benefits provided by the semi-automated approach}
One of the key advantages of the approach described here is that the automated pipeline identifies publications which are likely to contain content relevant to our domain area (i.e., measurements of neuronal biophysics).  Thus a human needs only to manually curate the content first identified by the algorithms as being likely relevant, instead of having to identify the relevant content \emph{de novo}.  Moreover, the automated identification of neuron types in articles allows us to target manual curation efforts to publications likely to contain data from specific neuron types, such as neurons that are currently underrepresented in the database.

Given our laboratory's focus on olfactory circuits, we conducted a natural experiment to compare the efficacy of biophysical property extraction using these semi-automated methods versus traditional methods which do not make use of algorithmic text-mining as a pre-processing step.  In a seven-hour curation session, a senior graduate student in our laboratory identified 91 electrophysiological measurements (focusing on resting membrane potential, input resistance, membrane time constant, spike amplitude, spike width, and spike threshold) from 35 articles for 7 olfactory bulb neuron types using only prior knowledge of which articles and investigators were likely to have reported such electrophysiological data.  In a comparable seven-hour curation session using our semi-automated methods, a single curator (with similar expertise to the first curator) identified 551 electrophysiological measurements from 70 articles across 40 neuron types throughout the nervous system.  Moreover, this comparison would likely tilt even more in favor of the semi-automated methods had the curators been less familiar with the primary literature.

\subsection{Scalability of current approach}
We note that multiple steps in our approach require manual intervention by an expert curator in order for electrophysiological measurements to be extracted with an acceptably low error rate.  Namely, an expert curator needs to specify which neuron types are recorded from in each article and where data from the normotypic or ``control'' states of these neurons are textually referenced within a data table.  Moreover, given the current accuracy of the unsurpervised algorithmic assignment of electrophysiological concepts and experimental metadata (78\% and 50\%, respectively), these also need to be manually validated and corrected as required by an expert.  Given the necessity of these manual steps, the scalability of our current approach is limited by our ability to manually curate this information or by our ability to improve the error rate of the automated methods.  Despite this limitation, our current pipeline is still much faster than a purely manual one.  The methodology could be further improved by addressing falsely matching entities (such as EPSP amplitude in section \ref{sec:ephys_extraction}) by either auto-suggesting alternative matches returned by string-similarity algorithms or by simply adding these concepts to the electrophysiolgical ontology.  Moreover, these improvements would facilitate formally computing the sensitivity and specificity of these entity recognition methods.

\subsection{Extensions and improvements to the current semi-automated algorithms}
Currently, neuron type identification is a critical bottleneck in our approach.  One potential improvement would be to replace the nonspecific bag-of-words approach we are currently using in favor of a bioNLP classifier-based approach \citep{mccallum_mallet:_2002}.  Specifically, we propose adapting the named entity recognition methodology used by the WhiteText project for tagging brain regions mentioned in literature \citep{french_automated_2009,french_using_2012} and first identifying spans of text likely to pertain to a neuron type before mapping these textual spans to a individual neuron type within the neuron ontology.  Moreover, such an approach could easily incorporate common neuron type acronyms and abbreviations \citep{okazaki_building_2006}.

The approach described here is highly effective for extracting biophysical measurements presented within machine-readable data tables published within journal articles.  However, the current requirement that these data tables exist in a machine parseable format, such as HTML or XML, limits this approach from being directly applied to older manuscripts, which are only available as scanned images.  Existing approaches, such as optical character recognition technology (OCR; e.g. \citep{ramakrishnan_layout-aware_2012}) may be applied toward this problem in the future. 
%[Imagine that Neuroscience journals replace and CAPTCHA validation with NeuroCaptcha - to validate data from papers]

Given the relatively low accuracy of the automated approach to identifying neuron types, there may be several avenues through which this process can be improved. For example, we note the automated approach was particularly ineffective when the neuron type investigated within an article was not already described in NeuroLex or when the neuron had an insufficient list of synonyms associated with it.  The current implementation of NeuroElectro also does not consider common neuron type acronyms (e.g., that olfactory bulb mitral cells are commonly referred to as ``MCs'').  Adding acronym identification to future iterations will thus likely improve the automated approach \citep{okazaki_building_2006,french_using_2012}.  Moreover, our current implementation of the bag-of-words algorithm would likely be improved via minor improvements, such as only identifying neurons using the text of the abstract or results and discarding text from the introduction or discussion. As neuron identification forms the major bottleneck in the scalability of NeuroElectro due to the requirement for manual curation, we plan to address this bottleneck in future revisions.

\subsection{Future methods for data extraction}
A more pressing issue with the current approach is its focus on extraction from data tables.  We estimate that only 5-10\% of published electrophysiological data is contained within tables, while the remaining 90-95\% is presented within article text or figure images.  Given our preference to obtain data in their most raw form, we initially considered extraction of data from figures, e.g. voltage traces of neuronal activity.  However, digitizing article figures (presented by publishers as images) into a form that can be further analyzed presents multiple challenges.  Though techniques and tools exist to digitize figures, substantial amounts of manual effort are required to employ them correctly, making this figure-based approach difficult to scale to increasing numbers of articles without also employing a large team of human curators.  While automatically extracting measurements from figure images will likely prove challenging, our methods can likely be adapted to operate on article text, perhaps by making use of bioNLP methodologies currently used for relationship extraction in the identification of connected brain regions \citep{french_application_2012} or interacting pairs of proteins \citep{kim_classifying_2011}.

However, more widespread inclusion of fundamental electrophysiological measurements in data tables in future publications will strongly facilitate data-sharing and meta-analysis initiatives such as NeuroElectro.  We believe that, if successful, the use of NeuroElectro will influence the practices of scientists writing papers and reporting results.  Specifically we believe (and hope) that it will result in scientists reporting more basic physiological data overall as well as reporting more data in machine-parsable tables.  This change would make it easier for scientists to find and make use of data collected by others.  Moreover, such a culture shift has the potential to make science function more effectively and efficiently to facilitate discovery.

\section*{Disclosure/Conflict-of-Interest Statement}
The authors declare that the research was conducted in the absence of any commercial or financial relationships that could be construed as a potential conflict of interest.

\section*{Acknowledgement}
We thank William Cohen, Gordon Shepherd, and Renaud Richardet for discussions and comments on the manuscript. We are especially grateful to all of the investigators whose collected data are represented within the NeuroElectro database.  We thank the academic journal publishers (in particular, Elsevier and Wiley and Highwire) for allowing us access to their full-texts for text-mining.  We are especially grateful to all of the investigators whose collected data are represented within the NeuroElectro database.

\paragraph{Funding\textcolon} This work was supported by a National Science Foundation Graduate Research Fellowship and a R. K. Mellon Foundation Fellowship (to S.J.T.), an Achievement Rewards for College Scientists Foundation Fellowship and NIDCD NRSA F31DC013490 (to S.D.B.), NIDCD award F32DC010535 and NIMH award R01MH081905 (in support of R.C.G.), and NIDCD award R01DC005798 (to N.N.U.).

\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
\bibliography{references}

\section*{Supplemental Data}
\begin{figure*}[htbp]
\centering
\includegraphics[scale = .4, angle =90]{figures/django_models_v2.jpg}
\caption{Illustration of NeuroElectro relational database schema}
\label{db_schema}
\end{figure*}
%SDB: anyway you can increase the font on at least some of these pathways? Or split into multiple figures showing subsections of the relations? As is, it is very difficult to look at this and take anything away from it.

\end{document}

### 2014-03-17 neuroelectro_frontiers/main.tex
Added tex line breaks for easy diffability
Revisions for reviewers

@@
 
-\title[NeuroElectro.org: text-mining neurophysiology data]{NeuroElectro: A Window to the World's Neurophysiology Data}
+\title[NeuroElectro.org: text-mining neurophysiology data]{NeuroElectro: A Window to the World's Neuron Electrophysiology Data}
 \author[\firstAuthorLast ]{\Authors}
@@
 Success among these projects can be defined according to different criteria.  
-Such criteria include completeness and comprehensiveness; for example, what percentage of relevant connectivity studies are indexed within BAMS?
+Such criteria include completeness and comprehensiveness; 
+for example, what percentage of relevant connectivity studies are indexed within BAMS? 
 How many different neuron types are contained within the NeuroMorpho database?  
@@
 This pre-selection step allowed us to identify and download only articles that contained data relevant to our project.  
-Upon identifying candidate articles, we then downloaded the full text of each potentially-relevant article as HTML; articles downloaded from the publisher Elsevier (e.g., \emph{Neuron and Brain Research}) were downloaded as XML using the provided text-mining API and subsequently converted to HTML.
+Upon identifying candidate articles, we then downloaded the full text of each potentially-relevant article as HTML; 
+articles downloaded from the publisher Elsevier (e.g., \emph{Neuron and Brain Research}) were downloaded as XML using the provided text-mining API and subsequently converted to HTML.  
 We chose to work with HTML (as opposed to PDF or XML) because HTML provides a machine-readable markup of the article's content, allowing us to easily identify relevant elements within the article -- such as data tables and the methods section -- using publicly available HTML-parsing tools (here we used the Beautiful Soup HTML-processing library implemented in Python: \url{http://www.crummy.com/software/BeautifulSoup/bs4/doc/}).
 Furthermore, because HTML is a single semi-structured standard used across publishers, we could write relatively generic HTML-processing algorithms applicable to content published across journals.  
-However, our focus on using HTML limits us to relatively newer articles -- typically those published after 1997 -- because most publications before this time are only available as scanned PDF files.
+Our focus on using HTML limits us to relatively newer articles - typically those published after 1996 - because before this time most publications are only available as scanned PDF files.  
+However, because the rate of publication across the field has grown exponentially, this HTML-available subset constitutes the vast majority of neuroscience articles ever published.
 
@@
 In order to algorithmically extract information on neuron electrophysiology from these articles, we needed to first specify the data types of interest.  
-Our preference was to obtain as much detailed information about neuron electrophysiological properties as possible: ideally, this would include raw data corresponding to recorded electrophysiological traces.
-In mining information from articles, we were presented with multiple options (illustrated in Fig.
-\ref{content_types}), including extraction from: 1) the text of the article including figure captions, 2) the figures of the article, or 3) data tables presented within the article.
+Our preference was to obtain as much detailed information about neuron electrophysiological properties as possible: 
+ideally, this would include raw data corresponding to recorded electrophysiological traces. 
+In mining information from articles, we were presented with multiple options (illustrated in Fig. \ref{content_types}), including extraction from: 
+1) the text of the article including figure captions, 
+2) the figures of the article, or 
+3) data tables presented within the article.  
 In addition to these, authors often submit supplemental materials and figures which also contain neurophysiological data.
@@
 \includegraphics[scale = .8]{./figures/SMeth1_extraction_content_example.jpg}
-\caption{\textit{Illustration of the sources within an article containing information relevant to neuron electrophysiological properties.}  Data on neuronal electrophysiological properties are presented within article figures and raw traces, sentences within the article text, and formatted data tables.
+\caption{\textit{Illustration of the sources within an article containing information relevant to neuron electrophysiological properties.}  
+Data on neuronal electrophysiological properties are presented within article figures and raw traces, sentences within the article text, and formatted data tables.  
 The raw traces and references are from \citet{van_brederode_gad67-gfp+_2011} and the data table is a constructed example.  
@@
 In extracting electrophysiological data, we took advantage of the fact that certain measurements are commonly made during intracellular recordings.  
-For example, such recordings are commonly used to: 1) measure a neuron's resting membrane potential, 2) to apply hyperpolarizing current injections for measurement of input resistance and membrane time constant, and 3) to apply depolarizing current steps to evoke action potentials (spikes) and enable measurement of characteristics such as spike threshold, width, and amplitude.
+For example, such recordings are commonly used to: 
+1) measure a neuron's resting membrane potential, 
+2) to apply hyperpolarizing current injections for measurement of input resistance and membrane time constant, and 
+3) to apply depolarizing current steps to evoke action potentials (spikes) and enable measurement of characteristics such as spike threshold, width, and amplitude.
 
@@
 \includegraphics[scale = 1]{figures/example_data_table_v2.jpg}
-\caption{\textit{Example data table illustrating mark-up and annotation of entities.}  A.
-Example published data table containing neurophysiological information.
-Data table from \citet{pasquale_increased_1997}.
-B.
-Same as A, but semantically marked up with algorithmic and manually curated annotations.
+\caption{\textit{Example data table illustrating mark-up and annotation of entities.}  
+A. Example published data table containing neurophysiological information.  Data table from \citet{pasquale_increased_1997}.  
+B. Same as A, but semantically marked up with algorithmic and manually curated annotations.  
 Markups in red and pink indicate electrophysiological and neuron type concepts and yellow indicates extracted data measurements.  
@@
 \citep{connors_electrophysiological_1982,toledo-rodriguez_correlation_2004}).
-However, experimental differences exist between how investigators measure and compute these properties; we divide these differences into roughly 3 categories: \textit{protocol}, \textit{calculation}, and \textit{condition} differences.
+However, experimental differences exist between how investigators measure and compute these properties; 
+we divide these differences into roughly 3 categories: \textit{protocol}, \textit{calculation}, and \textit{condition} differences.  
 For example, investigators can use different experimental protocols to measure the spike amplitude, like evoking spikes using current steps much greater than rheobase current required to elicit a single spike (\textit{protocol differences}).
@@
 We developed custom string regular expressions \citep{thompson_programming_1968} to parse the string corresponding to the numeric data.  
-Specifically, we found that data strings were often of the form: ``XX $\pm$ YY (ZZ)'', where XX, YY, and ZZ refer to the mean, error term, and sample size (i.e.
-the ``n''), respectively.
+Specifically, we found that data strings were often of the form: ``XX $\pm$ YY (ZZ)'', where XX, YY, and ZZ refer to the mean, error term, and sample size (i.e. the ``n''), respectively.  
 Often the number of replicates or error measurement were not reported or were reported in alternative ways within the table.  
@@
 
-When designing our processing algorithms, we parsed data strings from right to left: first searching for data entities contained within parentheses, then for entities contained to the right of the $\pm$ term, and finally the remaining term which we assumed to refer to the mean term.
+When designing our processing algorithms, we parsed data strings from right to left: 
+first searching for data entities contained within parentheses, then for entities contained to the right of the $\pm$ term, and finally the remaining term which we assumed to refer to the mean term.  
 We found that occasionally data were reported as ``XX (LL - HH)'' -- where LL and HH indicate the lower and upper limits of a data range -- and accounted for these cases similarly.  
@@
 Following these automated concept identification and data extraction steps, we manually validated associated concepts and fixed incorrect concept mappings as necessary.  
-We developed custom-HTML and javascript code to allow human curators to graphically interact with downloaded HTML data tables and ``mark-up'' entities within the table (Fig.
-\ref{human_validation}).
+We developed custom-HTML and javascript code to allow human curators to graphically interact with downloaded HTML data tables and ``mark-up'' entities within the table (Fig. \ref{human_validation}).  
 This code allows for textual based elements of the HTML table to be semantically annotated using drop down menus and text fields.  
@@
 \includegraphics[scale = 1]{figures/human_validation_example.jpg}
-\caption{\textit{Example of human validation of algorithmically assigned content.}  All textual elements of a table are enhanced using HTML and javascript to allow for assignment of neuron or electrophysiological concepts using drop down menus.
+\caption{\textit{Example of human validation of algorithmically assigned content.}  
+All textual elements of a table are enhanced using HTML and javascript to allow for assignment of neuron or electrophysiological concepts using drop down menus.  
 Example data table from \citet{pasquale_increased_1997}.}
@@
 A useful feature of the relational nature of the database is that it enables linking between classes (e.g., linking between neuron types and electrophysiological properties reported by a single investigator across multiple articles).
-This linking feature facilitates efficient and arbitrary querying of data; for example, querying for known electrophysiological data on olfactory bulb mitral cells recorded \emph{in vitro} and published between the dates 2000 and 2004.
+This linking feature facilitates efficient and arbitrary querying of data; 
+for example, querying for known electrophysiological data on olfactory bulb mitral cells recorded \emph{in vitro} and published between the dates 2000 and 2004.  
 For example, such a feature could be used to assess whether the properties of olfactory bulb mitral cells have changed as a function of time or are dependent upon whether the data are collected \emph{in vitro} or \emph{in vivo}.
@@
 
+\subsection{Preliminary use of NeuroElectro in scientific work}
+The NeuroElectro project is intended to facilitate scientific investigation by providing easy access to large quantities of data about neurons.  
+Because the data is machine-readable, we have already begun to conduct several analyses that would not be possible without this resource.  
+First, we have begun an investigation of the relationships between neurons defined by the similarity of their electrophysiological properties.  
+This information can be used to make predictions about as yet unmeasured properties.  
+Second, we have begun to explore the relationship between patterns of gene expression (using both the Allen Brain Atlas and single cell qPCR approaches) and electrophysiological properties of neurons.
+Third, we have begun automated testing of quantitative neuron models, under the reasonable assumption that these models should be constrained by the available experimental data.  
+These projects are described in manuscripts currently in preparation.
+
 \subsection{Extensions and improvements to the current semi-automated algorithms}
@@
 However, the current requirement that these data tables exist in a machine parseable format, such as HTML or XML, limits this approach from being directly applied to older manuscripts, which are only available as scanned images.
-Existing approaches, such as optical character recognition technology (OCR; e.g.
-\citep{ramakrishnan_layout-aware_2012}) may be applied toward this problem in the future.
+Existing approaches, such as optical character recognition technology (OCR; e.g. \citep{ramakrishnan_layout-aware_2012}) may be applied toward this problem in the future. 
 %[Imagine that Neuroscience journals replace and CAPTCHA validation with NeuroCaptcha - to validate data from papers]
@@
 We estimate that only 5-10\% of published electrophysiological data is contained within tables, while the remaining 90-95\% is presented within article text or figure images.  
-Given our preference to obtain data in their most raw form, we initially considered extraction of data from figures, e.g.
-voltage traces of neuronal activity.
+Given our preference to obtain data in their most raw form, we initially considered extraction of data from figures, e.g. voltage traces of neuronal activity.  
 However, digitizing article figures (presented by publishers as images) into a form that can be further analyzed presents multiple challenges.  
@@
 While automatically extracting measurements from figure images will likely prove challenging, our methods can likely be adapted to operate on article text, perhaps by making use of bioNLP methodologies currently used for relationship extraction in the identification of connected brain regions \citep{french_application_2012} or interacting pairs of proteins \citep{kim_classifying_2011}.
+
+Future developments in machine extraction of data from the scientific literature will be of great benefit.  
+These should include better semantic understanding of context, ranging from relatively unambiguous notations such as units, to syntax-parsing that relates objects of study to their reported properties in free-form prose.
+Much progress has been made by computer scientists in some of these areas, and more future engagement with their research should enable vastly more data to be extracted from the literature.  
+In the mean time, experimentalists who would like their data to be easily curated should strongly consider using data tables in future publications.
 

### 2014-03-17 neuroelectro_frontiers/main.tex
updated main.tex and updated figures

@@
 \centering
-\includegraphics[scale = 1]{figures/metadata_assignment_accuracy.jpg}
+\includegraphics[scale = 1]{figures/metadata_assignment_accuracy_v2.jpg}
 \caption{\textit{Accuracy of metadata assignment using automated methods alone.} }
@@
 Much progress has been made by computer scientists in some of these areas, and more future engagement with their research should enable vastly more data to be extracted from the literature.
-In the mean time, experimentalists who would like their data to be easily curated should strongly consider using data tables in future publications.
+
+To facilitate further data integration efforts, we advocate small shifts in how investigators analyze and report neurophysiological data.  
+Specifically, we recommend the usage of common standards and definitions for basic physiological measurements\citep{toledo-rodriguez_correlation_2004} and neuron types\citep{ascoli_petilla_2008,larson_neurolex.org:_2013}.
+We also ask that physiologists report more basic physiological information within articles and, if possible, publish such data using machine-readable formats like data tables.  
+Similarly, relevant experimental details should be clearly stated within the methods section (e.g., liquid junction potential correction).  
+These recommendations could be made informally by journals (in particular, requested by reviewers during manuscript review) as well as by funding agencies.
 

### 2014-03-17 neuroelectro_frontiers/main.tex
made changes to main.tex to respond to reviewer comments

@@
     \botrule
-    \end{tabular}}[]
+    \end{tabular}}
+   {}
 \end{table}
@@
 Our focus on using HTML limits us to relatively newer articles - typically those published after 1996 - because before this time most publications are only available as scanned PDF files.  
-However, because the rate of publication across the field has grown exponentially, this HTML-available subset constitutes the vast majority of neuroscience articles ever published.
+However, because the rate of publication across the field has grown exponentially, this HTML-available subset constitutes the majority of published neuroscience articles.
 
@@
 Moreover, because tables succinctly summarize multiple attributes of a collected dataset, the effort of an expert curator can be put to best use when validating tables relative to validating content mined from article sentences or figure panels.
-While we estimate that only 5-10\% of electrophysiology articles contain data tables, there is sufficient redundancy within the field (i.e., multiple investigators often publish articles on the same neuron type) that focusing on data tables nevertheless yields substantial coverage of electrophysiological properties across nearly all major neuron types.
+While we estimate that only 5-10\% of electrophysiology articles contain data tables, there is sufficient redundancy within the field (i.e., multiple investigators often publish articles on the same neuron type) that focusing on data tables nevertheless yields substantial coverage of electrophysiological properties across many major neuron types.
 
@@
 
-When manually curating the text-mined content for the most commonly reported electrophysiological properties (resting membrane potential, input resistance, membrane time constant, spike half-width, spike amplitude, and spike threshold), we took care to account for and remove cases where the investigator had calculated an electrophysiological measurement using an inconsistent methodology (e.g., protocol or calculation differences).
+When manually curating the text-mined content for the most commonly reported electrophysiological properties (resting membrane potential, input resistance, membrane time constant, spike half-width, spike amplitude, and spike threshold), we took care to account for where the investigator had calculated an electrophysiological measurement using an inconsistent methodology (e.g., protocol or calculation differences) by normalizing such measurements to a common reference definition or removing such data when normalization was not possible.
 However we note that we could not identify all of these cases (in particular: spike amplitude, input resistance, and membrane time constant), in part because investigators did not always explicitly define how these measurements were calculated within their article.
@@
 \centering
-\includegraphics[scale = 1]{figures/metadata_assignment_accuracy_v2.jpg}
-\caption{\textit{Accuracy of metadata assignment using automated methods alone.} }
+\includegraphics[scale = .25]{figures/metadata_assignment_accuracy_v2.jpg}
+\caption{\textit{Accuracy of metadata assignment using automated methods alone. Error indicate 95\% binomial confidence intervals.} }
 \label{metadata_robot_accuracy_robot}
@@
 Namely, an expert curator needs to specify which neuron types are recorded from in each article and where data from the normotypic or ``control'' states of these neurons are textually referenced within a data table.
-Moreover, given the current accuracy of the unsurpervised algorithmic assignment of electrophysiological concepts and experimental metadata (78\% and 50\%, respectively), these also need to be manually validated and corrected as required by an expert.
+Moreover, given the current accuracy of the unsurpervised algorithmic assignment of electrophysiological concepts and experimental metadata (78\% and 50\%, respectively), these also need to be manually validated and corrected and normalized as required by an expert.
 Given the necessity of these manual steps, the scalability of our current approach is limited by our ability to manually curate this information or by our ability to improve the error rate of the automated methods.
@@
 
-To facilitate further data integration efforts, we advocate small shifts in how investigators analyze and report neurophysiological data.  
-Specifically, we recommend the usage of common standards and definitions for basic physiological measurements\citep{toledo-rodriguez_correlation_2004} and neuron types\citep{ascoli_petilla_2008,larson_neurolex.org:_2013}.
-We also ask that physiologists report more basic physiological information within articles and, if possible, publish such data using machine-readable formats like data tables.  
-Similarly, relevant experimental details should be clearly stated within the methods section (e.g., liquid junction potential correction).  
-These recommendations could be made informally by journals (in particular, requested by reviewers during manuscript review) as well as by funding agencies.
-
 However, more widespread inclusion of fundamental electrophysiological measurements in data tables in future publications will strongly facilitate data-sharing and meta-analysis initiatives such as NeuroElectro.
 We believe that, if successful, the use of NeuroElectro will influence the practices of scientists writing papers and reporting results.  
-Specifically we believe (and hope) that it will result in scientists reporting more basic physiological data overall as well as reporting more data in machine-parsable tables.  
+Specifically, we recommend the usage of common standards and definitions for basic physiological measurements\citep{toledo-rodriguez_correlation_2004} and neuron types\citep{ascoli_petilla_2008,larson_neurolex.org:_2013}.
+Moreover, we advocate that, where possible, scientists report more basic physiological data overall and report such data using machine-parsable data tables.  
+These recommendations could be made informally by journals (in particular, requested by reviewers during manuscript review) as well as by funding agencies.
 This change would make it easier for scientists to find and make use of data collected by others.  

### 2014-03-18 neuroelectro_frontiers/main.tex
Asdf
Added bibliography format file

@@
 This change would make it easier for scientists to find and make use of data collected by others.  
-Moreover, such a culture shift has the potential to make science function more effectively and efficiently to facilitate discovery.
+Such a culture shift has the potential to make science function more effectively and efficiently to facilitate discovery.
 
@@
 
-\bibliographystyle{frontiersinSCNS&ENG} % for Science and Engineering articles
+\bibliographystyle{template/frontiersinSCNS&ENG} % for Science and Engineering articles
 \bibliography{references}
-
+\
 \section*{Supplemental Data}  

### 2014-03-18 neuroelectro_frontiers/main.tex
Added url for repository
Added sciunit reference

@@
 
-\usepackage{url,lineno}
-\usepackage{todonotes}
+\usepackage{template/url}
+\usepackage{template/lineno}
 
@@
 Our future plans are to work with domain ontologists to further develop the existing API into a formal relational data format (RDF) specification, allowing further querying and extending of NeuroElectro into additional resources.
+All code used in the project and the website is available at \url{http://bitbucket.org/rgerkin/neuroelectro_org}.
 
@@
 Second, we have begun to explore the relationship between patterns of gene expression (using both the Allen Brain Atlas and single cell qPCR approaches) and electrophysiological properties of neurons.
-Third, we have begun automated testing of quantitative neuron models, under the reasonable assumption that these models should be constrained by the available experimental data.  
+Third, we have begun automated testing of quantitative neuron models in concert with SciUnit \citep{omar_sciunit_2014}, under the reasonable assumption that these models should be constrained by the available experimental data.
 These projects are described in manuscripts currently in preparation.

### 2014-03-18 neuroelectro_frontiers/main.tex
added ref to ABA

@@
 This information can be used to make predictions about as yet unmeasured properties.  
-Second, we have begun to explore the relationship between patterns of gene expression (using both the Allen Brain Atlas and single cell qPCR approaches) and electrophysiological properties of neurons.
+Second, we have begun to explore the relationship between patterns of gene expression (using both the Allen Brain Atlas \citep{lein_genome-wide_2007} and single cell qPCR approaches) and electrophysiological properties of neurons.
 Third, we have begun automated testing of quantitative neuron models in concert with SciUnit \citep{omar_sciunit_2014}, under the reasonable assumption that these models should be constrained by the available experimental data.

### 2014-03-18 neuroelectro_frontiers/main.tex
minor spacing changes

@@
 We believe that, if successful, the use of NeuroElectro will influence the practices of scientists writing papers and reporting results.  
-Specifically, we recommend the usage of common standards and definitions for basic physiological measurements\citep{toledo-rodriguez_correlation_2004} and neuron types\citep{ascoli_petilla_2008,larson_neurolex.org:_2013}.
+Specifically, we recommend the usage of common standards and definitions for basic physiological measurements \citep{toledo-rodriguez_correlation_2004} and neuron types \citep{ascoli_petilla_2008,larson_neurolex.org:_2013}.
 Moreover, we advocate that, where possible, scientists report more basic physiological data overall and report such data using machine-parsable data tables.  

### 2014-03-18 neuroelectro_frontiers/main.tex
Minor changes befoire resubmission

@@
 Listing of journals and counts of articles downloaded (articles obtained), articles with published data tables containing neurophysiological information which has been manually validated by an expert curator (validated), and articles which likely contain information in a data table which has not yet been manually curated (not validated).
-Not validated articles are those which have at least 4 algorithmically assigned electrophysiological concepts within a data table.}
+Not validated articles are those which have at least 4 algorithmically assigned electrophysiological concepts within data tables.}
 \processtable{}
@@
 We obtained tens of thousands of potentially relevant full article texts directly from publisher websites.  
-We first identified potential articles that were likely to contain information relevant to neuron biophysics using the native search functions provided within the journal websites and only downloaded articles containing a specific list of terms including ``input resistance'' and ``resting membrane potential'' (Fig.
+We first identified potential articles that were likely to contain information relevant to neuron biophysics using the native search functions provided within the journal websites and only downloaded articles containing in their full text any of a specific list of terms including ``input resistance'' and ``resting membrane potential'' (Fig.
 \ref{text_mining_workflow}).
@@
 We then converted the individual data elements which were encoded as textual strings of digits to double precision decimal entities before storing these into our database.  
-Our focus here was primarily on parsing the data record mean value (i.e., summarizing the properties of a number of recorded neurons), but also extracted and stored the error term and sample size where possible.
+Our focus here was primarily on parsing the mean value from a data record (i.e., summarizing the properties of a number of recorded neurons), but also extracted and stored the error term and sample size where possible.
 Using these methods, we were able to extract 2176 electrophysiological values for 93 distinct neuron types within 279 articles.
@@
 The object model contains classes for a number of fields, such as full article texts, electrophysiological properties, neuron types, synonyms, electrophysiological data values, and experimental metadata (Fig.
-\ref{db_schema}).
+S1).
 A useful feature of the relational nature of the database is that it enables linking between classes (e.g., linking between neuron types and electrophysiological properties reported by a single investigator across multiple articles).
@@
 for example, querying for known electrophysiological data on olfactory bulb mitral cells recorded \emph{in vitro} and published between the dates 2000 and 2004.  
-For example, such a feature could be used to assess whether the properties of olfactory bulb mitral cells have changed as a function of time or are dependent upon whether the data are collected \emph{in vitro} or \emph{in vivo}.
+For example, such a feature could be used to assess whether measurements of olfactory bulb mitral cells have changed as a function of time or are dependent upon whether the data are collected \emph{in vitro} or \emph{in vivo}.
 
@@
 \item \url{http://neuroelectro.org/api/1/nedm/?nlex=sao830368389} : Returns a list of all indexed data on CA1 pyramidal cells (queried using the NeuroLex identifier for CA1 pyramidal cells, \emph{sao830368389}).
-\item \url{http://neuroelectro.org/api/1/nes/?e\_\_name=Input\%20Resistance\&n\_\_name=Cerebellum\%20Purkinje\%20Cell} : Returns a data record composed of the mean, standard deviation, and n, summarizing input resistance measurements from cerebellar Purkinje cells based on all indexed articles in NeuroElectro database.
+\item \url{http://neuroelectro.org/api/1/nes/?e__name=Input%20Resistance&n__name=Cerebellum%20Purkinje%20Cell} : Returns a data record composed of the mean, standard deviation, and sample size n, summarizing input resistance measurements from cerebellar Purkinje cells based on all indexed articles in NeuroElectro database.
 Here the database query is performed using the textual strings for the electrophysiological and neuron type concepts.
@@
 Given our laboratory's focus on olfactory circuits, we conducted a natural experiment to compare the efficacy of biophysical property extraction using these semi-automated methods versus traditional methods which do not make use of algorithmic text-mining as a pre-processing step.
-In a seven-hour curation session, a senior graduate student in our laboratory identified 91 electrophysiological measurements (focusing on resting membrane potential, input resistance, membrane time constant, spike amplitude, spike width, and spike threshold) from 35 articles for 7 olfactory bulb neuron types using only prior knowledge of which articles and investigators were likely to have reported such electrophysiological data.
+In a seven-hour curation session (evoking the classic American parable of John Henry versus the steam-powered hammer), a senior graduate student in our laboratory identified 91 electrophysiological measurements (focusing on resting membrane potential, input resistance, membrane time constant, spike amplitude, spike width, and spike threshold) from 35 articles for 7 olfactory bulb neuron types using only prior knowledge of which articles and investigators were likely to have reported such electrophysiological data.
 In a comparable seven-hour curation session using our semi-automated methods, a single curator (with similar expertise to the first curator) identified 551 electrophysiological measurements from 70 articles across 40 neuron types throughout the nervous system.
@@
 We note that multiple steps in our approach require manual intervention by an expert curator in order for electrophysiological measurements to be extracted with an acceptably low error rate.  
-Namely, an expert curator needs to specify which neuron types are recorded from in each article and where data from the normotypic or ``control'' states of these neurons are textually referenced within a data table.
+Namely, an expert curator needs to confirm which of the machine-identified candidate neuron types are recorded from in each article and where data from the normotypic or ``control'' states of these neurons are textually referenced within a data table.
 Moreover, given the current accuracy of the unsurpervised algorithmic assignment of electrophysiological concepts and experimental metadata (78\% and 50\%, respectively), these also need to be manually validated and corrected and normalized as required by an expert.
@@
 Because the data is machine-readable, we have already begun to conduct several analyses that would not be possible without this resource.  
-First, we have begun an investigation of the relationships between neurons defined by the similarity of their electrophysiological properties.  
+First, we have begun an investigation of the relationships between neurons as defined by the similarity of their electrophysiological properties.  
 This information can be used to make predictions about as yet unmeasured properties.  
@@
 Specifically, we propose adapting the named entity recognition methodology used by the WhiteText project for tagging brain regions mentioned in literature \citep{french_automated_2009,french_using_2012} and first identifying spans of text likely to pertain to a neuron type before mapping these textual spans to a individual neuron type within the neuron ontology.
-Moreover, such an approach could easily incorporate common neuron type acronyms and abbreviations \citep{okazaki_building_2006}.
 
@@
 The current implementation of NeuroElectro also does not consider common neuron type acronyms (e.g., that olfactory bulb mitral cells are commonly referred to as ``MCs'').  
-Adding acronym identification to future iterations will thus likely improve the automated approach \citep{okazaki_building_2006,french_using_2012}.  
-Moreover, our current implementation of the bag-of-words algorithm would likely be improved via minor improvements, such as only identifying neurons using the text of the abstract or results and discarding text from the introduction or discussion.
+Adding acronym and abbreviation identification to future iterations will thus likely improve the automated approach \citep{okazaki_building_2006,french_using_2012}.  
+Moreover, our current implementation of the bag-of-words algorithm would likely be enhanced via minor improvements, such as only identifying neurons using the text of the abstract or results and discarding text from the introduction or discussion.
 As neuron identification forms the major bottleneck in the scalability of NeuroElectro due to the requirement for manual curation, we plan to address this bottleneck in future revisions.
@@
 Future developments in machine extraction of data from the scientific literature will be of great benefit.  
-These should include better semantic understanding of context, ranging from relatively unambiguous notations such as units, to syntax-parsing that relates objects of study to their reported properties in free-form prose.
+These should include better semantic understanding of context, ranging from relatively unambiguous notations such as units, to syntax-parsing of free-form prose that relates objects of study to their reported properties.
 Much progress has been made by computer scientists in some of these areas, and more future engagement with their research should enable vastly more data to be extracted from the literature.
 
-However, more widespread inclusion of fundamental electrophysiological measurements in data tables in future publications will strongly facilitate data-sharing and meta-analysis initiatives such as NeuroElectro.
 We believe that, if successful, the use of NeuroElectro will influence the practices of scientists writing papers and reporting results.  
@@
 \centering
-\includegraphics[scale = .4, angle =90]{figures/django_models_v2.jpg}
-\caption{Illustration of NeuroElectro relational database schema}
-\label{db_schema}
+\includegraphics[scale = .38, angle =90]{figures/django_models_v2.jpg}
+
+Fig. S1: Illustration of NeuroElectro relational database schema
+%\label{db_schema}
 \end{figure*}

### 2014-03-21 neurounit_frontiers/Paper.tex
Changed NeurounitFrontiers to neurounit_frontiers

--- 2013-12-01 NeurounitFrontiers/Paper.tex
@@
 \vspace{-15px}
-\caption{\texttt{[neuronunit.SpikeCountTest]} An example single neuron spike count test class implemented using \textit{SciUnit}.
+\caption{\texttt{[SpikeCountTest]} An example single neuron spike count test class implemented using \textit{SciUnit}.
 Because this implementation contains logic common to many different systems, \textit{NeuronUnit} was developed to provide a simpler means to deliver it (see Sec.
@@
 \vspace{-15px}
-\caption{\texttt{[neuronunit.SpikeCountFromCurrent]} An example capability specifying a single required method (used by the test in Figure \ref{fig:rate_test}).}
+\caption{\texttt{[SpikeCountFromCurrent]} An example capability specifying a single required method (used by the test in Figure \ref{fig:rate_test}).}
 \label{fig:capability}
@@
 \vspace{-15px}
-\caption{\texttt{[neuronunit.TrainSpikeCountFromCurrent]} Another capability specifying a training protocol (not used by the test in Figure \ref{fig:rate_test}).}
+\caption{\texttt{[TrainSpikeCountFromCurrent]} Another capability specifying a training protocol (not used by the test in Figure \ref{fig:rate_test}).}
 \label{fig:training}
@@
 \vspace{-15px}
-\caption{\texttt{[neuronunit.LinearModel]} A model that returns a spike count by applying a linear transformation to the mean input current.
+\caption{\texttt{[LinearModel]} A model that returns a spike count by applying a linear transformation to the mean input current.
 The parameters can be provided manually or learned from data provided by a test or user (see text).}
@@
 Currently, up to 27 electrophysiological properties are available for 93 cell types, gathered from over 2000 single pieces of published data extracted from tables in published papers. 
+NeuroElectro uses the NeuroLex.org ontology \cite{larson_neurolex_2013} to identify specific neuron types and specific electrophysiological properties, and indexes corresponding data values from the literature.
 We have made it easy to parameterize the test families in \textit{Neuron\-Unit}  using data extracted from the NeuroElectro API. 
@@
 Data from NeuroElectro can be used to validate a variety of basic electrophysiological features of neuron models, including spike width, resting membrane potential, after-hyperpolarization amplitude, etc.
-\todo{write a sentence or two about its use of the NeuroLex repository}
 As NeuroElectro is the only public, curated source of such data, it represents a key resource facilitating test construction.
@@
 \ref{fig:ca1_model}).
-The underlying simulator can be configured (defaulting to ??\todo{What does it default to in our code??}; not shown).
-In this example, we simply create a model based on a NeuroML model of CA1 cells downloaded from OpenSourceBrain to the local file system (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}).\todo{Migliore ref.}\todo{Should OSB models be transiently downloaded as part of the instantiation of OSBModel?}
+The underlying simulator can be configured (defaulting to NEURON; not shown).
+In this example, we simply create a model based on a NeuroML model of CA1 cells \cite{migliore_ca1_2005} downloaded from OpenSourceBrain to the local file system upon instantiation (\url{http://opensourcebrain.org/projects/ca1pyramidalcell}).
 
@@
 
-To directly test a model in OSB, we can skip the step of downloading it the local file system or adding it to the test repository and simply download it from OSB directly by using the \verbx{OSBModel} class, shown on lines 5-8 of Figure \ref{fig:neuronunit_example}.
+To directly test a model in OSB, we can skip the step of adding it to the test repository and simply download it from OSB directly by using the \verbx{OSBModel} class, which is a subclass of  \verbx{NeuroConstructModel}, shown on lines 5-8 of Figure \ref{fig:neuronunit_example}.
 
@@
 \vspace{-15px}
-\caption{A model class corresponding to a CA1 Pyramidal Cell model downloaded locally from Open Source Brain}
+\caption{A model class corresponding to a CA1 Pyramidal Cell model (Migliore et al, 2005) downloaded locally from Open Source Brain}
 \label{fig:ca1_model}
@@
 \verbx{NeuroConstructModel} implements this by default by calling the NeuroTools method \verbx{AnalogSignal.threshold_detection}, retrieving the membrane potential by calling the \verbx{get_membrane_potential} method implemented by the \verbx{HasMembranePotential} capability.
-This capability is implemented by the OSBModel class that supports all current OSB models.
+This capability is implemented by the \verbx{NeuroConstructModel} class which supports all current OSB models and implicitly supports all NeuroML models with somatic membrane potentials.
 NeuroTools is used in this manner to implement a wide variety of capabilities for \verbx{NeuroConstructModel}s, without requiring that the modeler do so explicitly (though they can override these if they wish).
-This also helps scientists by directing them to a set of common utility functions and data object types that they can use, knowing that they are accepted by the community around NeuronUnit.\todo{do you have a list of capabilities that neuroconstructmodels can automatically implement?}
+This also helps scientists by directing them to a set of common utility functions and data object types that they can use, knowing that they are accepted by the community around NeuronUnit.
 
@@
 \ref{sec:neuronunit} do not exhaust the possible sources of models, capabilities, and test data, they provide an immediate point of entry into the neurophysiology community and a powerful demonstration of our proposal.
-In the \textit{hippocampus\_tests} repository (\url{http://github.com/scidash/hippocampus\_tests}) is an IPython notebook (\textit{ca1\_suite.ipynb}) demonstrating a complete test suite similar to the \emph{ad hoc} suite used by the QSNMC.
-Our tests are parameterized by data drawn both from NeuroElectro and entered manually, as well as models drawn both from OSB and implemented manually. 
+In the \textit{hippocampus\_tests} repository (\url{http://github.com/scidash/hippocampus\_tests}) we are currently developing a complete test suite similar to the \emph{ad hoc} suite used by the QSNMC, demonstrated by an IPython notebook (\textit{ca1\_suite.ipynb}).
+These tests will be parameterized by data drawn both from NeuroElectro and entered manually, as well as models drawn both from OSB and implemented manually. 
 New tests, data and models can be added by contributing to these community resources and/or submitting pull requests; 
@@
 \textbf{Third}, cross-level testing can use ``Representional Similarity Analysis'' (RSA) \citep{kriegeskorte_representational_2008}, requiring only that a model respond to defined inputs (e.g.
-stimuli)\todo{I have no idea what this means}.
-A ``similarity matrix'' for input responses defines a unique model signature, and can serve as intermediate test output. 
+stimuli).
+In RSA, a ``similarity matrix'' for input responses defines a unique model signature, and can serve as intermediate test output. 
 Goodness-of-fit between similarity matrices for model and experiment determines test scores; 

### 2014-03-27 neuronunit_frontiers/Paper.tex
Revisions for Frontiers

--- 2014-03-21 neurounit_frontiers/Paper.tex
@@
 These tests generate and statistically validate predictions from a specified class of scientific models against one relevant empirical observation to produce a score indicating agreement between the model and the data.
-Suites of such validation tests, collaboratively developed by a scientific community in common repositories, produce up-to-date statistical summaries of the state of the field.
+Suites of such validation tests, collaboratively developed by a scientific community in common repositories, can produce up-to-date statistical summaries of the state of the field.
 In this paper, we aim to detail this test-driven workflow and introduce it to the neuroscience community.
@@
 The scientists tasked with reviewing the paper are responsible for evaluating these claims, discovering competing models and relevant data the paper did not adequately consider, and ensuring that goodness-of-fit was measured in a statistically sound manner, drawing on their knowledge of prior literature.
-Once a modeling paper is published, it is frozen and cited as-is in perpetuity.
+Often, there are no means for verifying even the basic results \citep{Donoho0815years}.
+And once a modeling paper is published, it is frozen and cited as-is in perpetuity.
 
@@
 A simple summary of the scores in a score matrix can be printed to the console or visualized by other tools.  
-For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \citep{perez_ipython_2007} (Fig. \ref{fig:scidash_matrix}).
+For example, the score matrix can be visualized as a hyperlinked table inside an IPython notebook \citep{perez_ipython_2007} (Fig.
+\ref{fig:scidash_matrix}).
+The code for generating such visualizations is available in the main SciUnit repository (\url{http://github.com/scidash/sciunit}), and for generating this particular visualization is available at \url{Cyrus put a URL here}.
 
@@
 
-The most visible result of these efforts will be tables, like the one shown in Figure \ref{fig:scidash_matrix}, that allow scientists to understand, precisely, the state-of-the-art in their field. 
+The most visible result of these efforts will be tables, like the one shown in Figure \ref{fig:scidash_matrix}, that allow scientists to represent, formally, the state of model development in their field, as judged against corresponding experimental data.
 We are developing a lightweight portal, \textit{SciDash}, that directs scientists to the canonical test repositories in their field in order to prevent fragmentation and encourage community participation \citep{omar_sciunit_2013}.
@@
 As NeuroElectro is the only public, curated source of such data, it represents a key resource facilitating test construction.  
+However, in selecting data from NeuroElectro (either averaged data across all reports, or data from selected reports) for test construction, one is implicitly assuming that it represents the kind data that ought to be binding in model development.
+For some models, data obtained in this way is ought not to guide model development, and other data sources will need to be identified and used for test construction.
 
@@
 We plan to assist with such competitions by advocating for use of SciUnit as the underlying technical substrate in the future.
+Currently, we are in discussion with field specialists to organize competitions for spiking neuron models (a sequel to the QSNMC), spike-sorting algorithms, calcium imaging spike time reconstruction, brain-computer interfaces, neural network function prediction, and seizure prediction.
 \textbf{Fourth}, modelers have an incentive to use \textit{SciUnit} during development (see TDD, Sec.
@@
 as a column in Figure \ref{fig:scidash_matrix}), or as a scatter plot, with the ``best'' models being in the high validity / low complexity corner of the plot.
+Validity may be equated to cross-validation accuracy, or the inverse of some loss function.
 The set of models which \textit{dominate} all others, i.e.
@@
 elegans.
+
+\subsection{Project Development}
+Gewaltig and Cannon describe the maturity of a computational software project \citep{gewaltig_current_2014} as ``review ready'', ``research ready'', or ``user ready''.  
+The development of the underlying SciUnit framework is complete \citep{omar_sciunit_2014}, and it provides the full interface necessary for continued development of domain-specific unit-testing frameworks -- it is research ready.
+NeuronUnit is ``review ready'' -- we invite others to participate in building it out to satisfy the use cases they encounter.
+Corresponding test suite repositories on GitHub, containing NeuronUnit-based tests, do not even reach this stage.
+With the exception of the repositories in development for the QSNMC, and for the Open Source Brain pipeline describe in Section 4, they are non-existent.
+We plan to continue creating such repositories; more importantly we invite interested parties to create their own, either to guide in-house model development or to assess larger pools of established models.
 

### 2014-03-27 neuroelectro_frontiers/main.tex
Minor changes for reviewer 1

@@
 We further discuss strategies for how to best combine, normalize and organize data across these heterogeneous sources.  
-NeuroElectro is a valuable resource for experimental physiologists looking to supplement their own data, for computational modelers looking to constrain their model parameters, and for theoreticians searching for undiscovered relationships among neurons and their properties.
+NeuroElectro is a valuable resource for experimental physiologists attempting to supplement their own data, for computational modelers looking to constrain their model parameters, and for theoreticians searching for undiscovered relationships among neurons and their properties.
 \tiny
@@
 How many different neuron types are contained within the NeuroMorpho database?  
-Alternatively, success can be defined in terms of the utility of these databases in driving subsequent research, like the use of BAMS as a resource for discovering relationships between brain region connectivity and gene expression \citep{french_relationships_2011} or the use of NeuroMorpho to discover general scaling relationships among the morphology of neuron types \citep{teeter_general_2011}.
+Alternatively, success can be defined in terms of the utility of these databases in driving subsequent research, like the use of BAMS as a resource for discovering relationships between brain region connectivity and gene expression \citep{french_relationships_2011} or the use of NeuroMorpho to discover general scaling relationships among the morphologies of neuron types \citep{teeter_general_2011}.
 Similarly, NeuroSynth is widely used by cognitive scientists as a starting point for designing functional imaging studies.  
@@
 articles downloaded from the publisher Elsevier (e.g., \emph{Neuron and Brain Research}) were downloaded as XML using the provided text-mining API and subsequently converted to HTML.  
-We chose to work with HTML (as opposed to PDF or XML) because HTML provides a machine-readable markup of the article's content, allowing us to easily identify relevant elements within the article -- such as data tables and the methods section -- using publicly available HTML-parsing tools (here we used the Beautiful Soup HTML-processing library implemented in Python: \url{http://www.crummy.com/software/BeautifulSoup/bs4/doc/}).
+We chose to work with HTML (as opposed to PDF or XML) because HTML provides a machine-readable markup of the article's content, allowing us easily to identify relevant elements within the article -- such as data tables and the methods section -- using publicly available HTML-parsing tools (here we used the Beautiful Soup HTML-processing library implemented in Python: \url{http://www.crummy.com/software/BeautifulSoup/bs4/doc/}).
 Furthermore, because HTML is a single semi-structured standard used across publishers, we could write relatively generic HTML-processing algorithms applicable to content published across journals.  
@@
 1) measure a neuron's resting membrane potential, 
-2) to apply hyperpolarizing current injections for measurement of input resistance and membrane time constant, and 
-3) to apply depolarizing current steps to evoke action potentials (spikes) and enable measurement of characteristics such as spike threshold, width, and amplitude.
+2) apply hyperpolarizing current injections for measurement of input resistance and membrane time constant, and 
+3) apply depolarizing current steps to evoke action potentials (spikes) and enable measurement of characteristics such as spike threshold, width, and amplitude.
 
@@
 
-When manually curating the text-mined content for the most commonly reported electrophysiological properties (resting membrane potential, input resistance, membrane time constant, spike half-width, spike amplitude, and spike threshold), we took care to account for where the investigator had calculated an electrophysiological measurement using an inconsistent methodology (e.g., protocol or calculation differences) by normalizing such measurements to a common reference definition or removing such data when normalization was not possible.
+When manually curating the text-mined content for some of the most commonly reported electrophysiological properties, we accounted for an investigator's calculation of an electrophysiological measurement using an inconsistent methodology (e.g., protocol or calculation differences).
+We did so by normalizing such measurements to a common reference definition or removing such data when normalization was not possible.
 However we note that we could not identify all of these cases (in particular: spike amplitude, input resistance, and membrane time constant), in part because investigators did not always explicitly define how these measurements were calculated within their article.
@@
 We then converted the individual data elements which were encoded as textual strings of digits to double precision decimal entities before storing these into our database.  
-Our focus here was primarily on parsing the mean value from a data record (i.e., summarizing the properties of a number of recorded neurons), but also extracted and stored the error term and sample size where possible.
+Our focus here was primarily on parsing the mean value from a data record (i.e., summarizing the properties of a number of recorded neurons), but we also extracted and stored the error term and sample size where possible.
 Using these methods, we were able to extract 2176 electrophysiological values for 93 distinct neuron types within 279 articles.
@@
 \subsection{Manual validation of automated data extraction}
-Following these automated concept identification and data extraction steps, we manually validated associated concepts and fixed incorrect concept mappings as necessary.  
+Following these automated concept identification and data extraction steps, we manually validated associated concepts and corrected incorrect concept mappings as necessary.  
 We developed custom-HTML and javascript code to allow human curators to graphically interact with downloaded HTML data tables and ``mark-up'' entities within the table (Fig. \ref{human_validation}).  
@@
 Despite this limitation, our current pipeline is still much faster than a purely manual one.
-The methodology could be further improved by addressing falsely matching entities (such as EPSP amplitude in section \ref{sec:ephys_extraction}) by either auto-suggesting alternative matches returned by string-similarity algorithms or by simply adding these concepts to the electrophysiolgical ontology.
+The methodology could be further improved by correcting falsely matching entities (such as EPSP amplitude in section \ref{sec:ephys_extraction}).
+These could be corrected by simply adding these valid concepts to the electrophysiolgical ontology.  
 Moreover, these improvements would facilitate formally computing the sensitivity and specificity of these entity recognition methods.
@@
 Given the relatively low accuracy of the automated approach to identifying neuron types, there may be several avenues through which this process can be improved. 
-For example, we note the automated approach was particularly ineffective when the neuron type investigated within an article was not already described in NeuroLex or when the neuron had an insufficient list of synonyms associated with it.
+For example, we note that the automated approach was particularly ineffective when the neuron type investigated within an article was not already described in NeuroLex or when the neuron had an insufficient list of synonyms associated with it.
 The current implementation of NeuroElectro also does not consider common neuron type acronyms (e.g., that olfactory bulb mitral cells are commonly referred to as ``MCs'').  
